### 2017-04-23 main.tex
Paper outline and key points

\documentclass{article}

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{standalone}
\usepackage{fancyvrb}

\usepackage{tikz}
\usetikzlibrary{calc, shapes, patterns}

\usepackage[backend=biber, firstinits=false, backref=false, url=true,
            isbn=true, style=numeric]{biblatex}
\addbibresource{bibliography.bib}

% Title
\title{IPD Strategies created with Reinforcement Learning}
\author{Marc Harper \and Vincent Knight} % TODO Authors?
\date{}

\begin{document}

\maketitle

Key points:
* We trained several different strategies and they all are tournament
winners
* works for standard, noisy, and moran
* Complex strategies can fare well
* the best strategies are cooperative yet punitive
* handshakes evolved naturally (ref art of war paper)
* copious references to W. and D. Ashlock

Todo:
* better title

Optional Todos:
* train lookerup that doesn't use first rounds
* train score diff mem-one -- is it ZD?

\begin{abstract}
    We present several powerful strategies for the Iterated
    Prisoner's Dilemma created using reinforcement learning techniques
    (evolutionary and particle swarm algorithms). These strategies are
    trained to perform well against a corpus of over 100 distinct
    opponents from the literature and all the trained strategies
    win standard tournaments against the total collection of other opponents.
    The best of these strategies use features derived from the history
    of play beyond the last round. We also trained variants to win
    noisy tournaments and the Moran process.
\end{abstract}

\section{Introduction}\label{sec:introduction}

* Update on Axelrod Library
Description of strategy space and tournament capabilities
Includes many prior tournament winners (OmegaTFT, ZDGTFT2)
Some original strategies but mostly from the literature

\section{The Strategy Archetypes}

Lookup Table: LookerUp
* Uses first two rounds of opponent's play (first impressions matter)
and last two trailing rounds

PSO Gambler
* Stocastic variant of Lookup Table
* Trained using particle swarm algorithm
* ``mostly deterministic'' and performs a bit better

Memory one strategies are a special case of PSO Gambler
* Trained a memory one variant it does well but not the best
* Not a ZD strategy

ANN
* Uses a collection of history derived features
* One hidden layer of 5-10 nodes
* Cite Ashlock as prior work

FSM
* Finite state machines (Ashlock et al)
* deterministic, moves depend on the state and the last round of play
* easy to encode TFT, WSLS, and handshake behaviors
* quick to train and execute
* represents a large portion of strategy space
* The library contains several FSMs from Ashlock et al

HMM
* Stochastic version of FSM
* Mimics a Hidden Markov Model

Meta*
* Mimics ensemble methods from ML
* Initially good strategies but not as good as trained strategies

\section{Results}

Standard Tournament run
Noisy Tournament run

Moran process fixations

\section{Methods}

Training Parameters
Objectives:
* total score
* total moran wins (fixation)
* score differece (unused, maybe leads to ZD?)

\section{Discussion}

Discussion:
* ML better at creating strategies
* possible to train an NN for predicting next move very accurate
but not straightforward to turn into a useful strategy
since some strategies grudge

Future work:
* spatial tournaments and other variants
* Additional strategy archetypes by the Ashlocks, e.g. function stacks
* further refine features and training parameters

\section{Conclusion}\label{sec:conclusion}

\section*{Acknowledgements}

This work was performed using the computational facilities of the Advanced
Research Computing @ Cardiff (ARCCA) Division, Cardiff University.

\printbibliography

### 2017-05-17 main.tex
Fill out the basic content for the paper

@@
 % Title
-\title{IPD Strategies created with Reinforcement Learning}
+\title{Reinforcement Learning Produces Dominant Strategies for the
+Iterated Prisoner's Dilemma}
 \author{Marc Harper \and Vincent Knight} % TODO Authors?
@@
 * the best strategies are cooperative yet punitive
-* handshakes evolved naturally (ref art of war paper)
 * copious references to W. and D. Ashlock
@@
 * better title
-
-Optional Todos:
-* train lookerup that doesn't use first rounds
-* train score diff mem-one -- is it ZD?
 
@@
     trained to perform well against a corpus of over 100 distinct
-    opponents from the literature and all the trained strategies
-    win standard tournaments against the total collection of other opponents.
-    The best of these strategies use features derived from the history
-    of play beyond the last round. We also trained variants to win
-    noisy tournaments and the Moran process.
+    opponents, including many well-known strategies from the literature, and all
+    the trained strategies win standard tournaments against the total collection
+    of other opponents. We also trained variants to win noisy tournaments.
 \end{abstract}
@@
 
+% TODO: cite earlier tournaments
+
 \section{The Strategy Archetypes}
 
-Lookup Table: LookerUp
-* Uses first two rounds of opponent's play (first impressions matter)
-and last two trailing rounds
+The Axelrod library now contains many strategies based on machine learning
+methods. Most are deterministic, use many rounds of memory, and perform
+extremely well in tournaments.
 
-PSO Gambler
-* Stocastic variant of Lookup Table
-* Trained using particle swarm algorithm
-* ``mostly deterministic'' and performs a bit better
+\subsection{LookerUp}
 
-Memory one strategies are a special case of PSO Gambler
-* Trained a memory one variant it does well but not the best
-* Not a ZD strategy
+The first strategy trained with reinforcement learning in the library is based
+on lookup tables. The strategy encodes a set of deterministic responses
+based on the opponent's first $n_1$ moves, the opponent's last $m_1$ moves, and
+the players last $m_2$ moves. If $n_1 > 0$ then the player has infinite memory
+depth, otherwise it has depth $\max{m_1, m_2}$. Although we tried various
+combinations of $n_1, m_1,$ and $m_2$, the best performance at the time of
+training was obtained for $n_1 = m_1 = m_2 = 2$ and generally for $n_1 > 0$. 
+First impressions matter in the IPD. The library includes a strategy
+called EvolvedLookerUp2_2_2 which is among the top strategies in the library.
 
-ANN
-* Uses a collection of history derived features
-* One hidden layer of 5-10 nodes
-* Cite Ashlock as prior work
+This archetype can be used to train memory-$n$ strategies with the parameters
+$n_1=0$ and $m_1=m_2=n$. For $n=1$, the result is WSLS.
+% TODO: doublecheck that it is WSLS
 
-FSM
-* Finite state machines (Ashlock et al)
-* deterministic, moves depend on the state and the last round of play
-* easy to encode TFT, WSLS, and handshake behaviors
-* quick to train and execute
-* represents a large portion of strategy space
-* The library contains several FSMs from Ashlock et al
+\subsection{PSO Gambler}
 
-HMM
-* Stochastic version of FSM
-* Mimics a Hidden Markov Model
+PSO Gambler is a stochastic variant of LookerUp. Instead of deterministically
+encoded moves the lookup table emits probabilities which are
+used to choose cooperation or defection. The library includes a player trained
+with $n_1 = m_1 = m_2 = 2$ that is \emph{mostly deterministic}, with most of the
+probabilities being 0 or 1. At one time this strategy outperformed
+EvolvedLookerUp2_2_2.
 
-Meta*
-* Mimics ensemble methods from ML
-* Initially good strategies but not as good as trained strategies
+This strategy type can be used to train arbitrary memory-$n$ strategies and a
+memory one strategy was trained and is called PSO Gambler Mem 1, with
+probabilities $\ldots$. Though it performs well in deterministic tournaments
+it is not as good as the longer memory strategies, and is bested by a similar
+strategy that also uses the first round of play.
+
+% TODO: quantify how stochastic
+% TODO: include memory one four vector
+
+\subsection{ANN}
+
+Strategies based on artificial neural networks can also be trained with an
+evolutionary algorithm. A variety of features are computed from the history
+of play such as the opponents trailing moves, the total number of cooperations
+of the player and the opponent, and several others, which are then input
+into a feed forward neural network with one layer and user-supplied width.
+An inner layer with just five nodes performs quite well in both deterministic and
+noisy tournaments. The output of the ANN used in this work is deterministic and
+a stochastic variant that outputs probabilities rather than exact moves could
+be easily created.
+
+% TODO: Cite earlier ANN papers including Ashlock
+% TODO: list features
+
+\subsection{Finite State Machines}
+
+We used strategies based on finite state machines to create a number of
+strategies. These strategies are deterministic and are efficient computational.
+At each state the machine transitions to a new state and plays a specified move
+depending on the opponent's last action. These strategies can encode a variety
+of other strategies, including classic strategies like TitForTat, encode
+handshakes, and gruding strategies that always defect after an opponent
+defection.
+
+% TODO: Cite Ashlock FSM papers
+% TODO: One or more diagrams
+
+\subsection{Hidden Markov Models}
+
+We also trained stochastic versions of finite state machine players called
+hidden Markov model players or HMMs. These strategies also encode an internal
+state with probabilistic transitions to other states and cooperate or defect
+with various probabilities at each state. These are the best performing
+stochastic strategies in the library but take longer to train due to their
+stochasticity.
+
+\subsection{Meta Strategies}
+
+Last but not least there are several strategies based on ensemble methods that
+are common in machine learning called Meta strategies. These strategies are
+composed of a team of other strategies and each is polled for its desired next
+move. The ensemble then selects the next move based on some rule, such as the
+consensus vote in the case of MetaMajority or the best individual performance
+in the case of MetaWinner. These strategies were among the best in the library
+before the inclusion of those trained by reinforcement learning.
 
@@
 
-Standard Tournament run
-Noisy Tournament run
+\subsection{Standard Tournament}
 
-Moran process fixations
+We conducted a tournament with all strategies in the Axelrod library. The top
+11 performing strategies by mean payoff are all strategies trained to maximize
+total payoff against a subset of the strategies (Figure \ref{}). The next strategy is 
+Desired Belief Strategy (DBS) which actively analyzes the opponent and responds
+accordingly. The next two strategies are Winner12, based on a lookup table, and
+Fool Me Once, a strategy that defects indefinitely on the second defection.
+
+Pairwise payoff results are given as a heatmap (Figure \ref{}) which
+shows that the many strategies achieve mutual cooperation with each other and
+that the top performing strategies never defect first but are able to exploit
+weaker strategies that attempt to defect.
+
+The strategies that win the most matches are Defector, Aggrevater, and then a
+series of ensemble strategies called MetaWinner, that combine the strategies
+of many other strategies and take a consensus vote for each move. These are
+followed by handshaking and zero determinant strategies.
+
+% Table of best strategies
+% \includegraphics{strategies_std_boxplot.svg}
+% \includegraphics{strategies_std_payoff.svg}
+% \includegraphics{strategies_std_winplot.svg}
+
+\subsection{Noisy Tournament}
+
+We also ran noisy tournaments in which there is a 5\% chance that an action
+is flipped. The best performing strategies in mean payoff are DBS, designed
+to correct for noise, followed by two finite state machine strategies trained
+in the presence of noise, and OmegaTFT (also designed to handle noise). The
+strategies trained in the presence of noise are also among the best performers
+in the absence of noise.
+
+The cluster of mutually cooperative strategies is broken by the noise at 5\%. A
+similar collection of players excels at winning matches but again they have
+a poor total payoff.
+
+% Table of best strategies
+% \includegraphics{strategies_noisy_boxplot.svg}
+% \includegraphics{strategies_noisy_payoff.svg}
+% \includegraphics{strategies_noisy_winplot.svg}
 
@@
 
-Training Parameters
-Objectives:
-* total score
-* total moran wins (fixation)
-* score differece (unused, maybe leads to ZD?)
+We trained a variety of strategies using evolutionary algorithms, and in the
+case of PSO Gambler particle swarm algorithms. The evolutionary algorithms
+used standard techniques, varying strategies by mutation and crossover, and
+evaluating the performance against each opponent for many repetitions. The
+best performing strategies in each generation are persisted, variants created,
+and objective functions computed again. This process continues for approxaimtely
+200 generations or until strategies no longer improve significantly.
+
+% Diagram with ANN training performance
+
+All training code is available on github. The are objective functions for
+* total payoff
+* total payoff difference
+* total Moran process wins (fixation probability)
+
+New strategies can be easily trained with variations including noise, spatial
+structure, and probabilistically ending matches.
 
@@
 
-Discussion:
-* ML better at creating strategies
-* possible to train an NN for predicting next move very accurate
-but not straightforward to turn into a useful strategy
-since some strategies grudge
+The tournament results indicate that pretrained strategies are generally better
+than human designed strategies at maximizing payoff against a diverse set of
+opponents. A simple evolutionary algorithm produces strategies based on multiple
+standard machine learning techniques that are able to achieve a higher mean
+score than any other known opponent. All of the trained strategies use many
+rounds of the history of play (some using all of it) and outperform memory-one
+strategies.
+
+Directly designing an effective strategy is no easy task. Of all the actively
+learning strategies in the library, only DBS performs well. The authors trained
+a neural network to predict opponents' next moves with high accuracy but basing
+a strategy on the predictions proved difficult -- it is necessary to consider
+the downstream consequences of a defection and direct training of strategy
+outputs generally performed better.
+
+These results suggest that, in opposition to historical tournament results
+and community folklore, that complex strategies can be very effective for the
+IPD. It is not the complexity of strategies that is disadvantageous, rather it
+is apparently too difficult for humans to design complex yet effective
+strategies, DBS being a notable exception.
+
+Furthermore, dealing with noise is difficult for most strategies. Two strategies
+designed specifically to account for noise, DBS and OmegaTFT, perform well and
+only DBS performs better than directly trained finite state machine strategies.
+
+Of all the strategies trained to maximize their mean score all are generally
+cooperative, not defecting until the opponent defects. Maximizing for individual
+performance across a collection of opponents leads to mutual cooperation despite
+the fact that mutual cooperation is an unstable equilibrium for the prisoner's
+dilemma. Specifically we note that the reinforcement learning process does not
+lead to exploitative zero determinant strategies, which may be a result of the
+collection of training strategies, many of which retailate harshly.
+
+Finally, we note that as the library grows, the top performing strategies
+sometimes shuffle, and are not retrained regularly. The precise parameters
+that are optimal will depend on the pool of opponents. Moreover we have not
+extensively trained strategies to determine the minimum parameters that are
+sufficient -- neural networks with fewer nodes and features and finite state
+machines with fewer states may suffice.
+% TODO: Cite Ashlock paper on parameter capacity for trained strategies
 
@@
 * spatial tournaments and other variants
-* Additional strategy archetypes by the Ashlocks, e.g. function stacks
+* Additional strategy archetypes by the Ashlocks, e.g. function stacks, binary
+decision players
 * further refine features and training parameters
-
-\section{Conclusion}\label{sec:conclusion}
 

### 2017-05-17 src/run_10000_noise.py
Add file for 10000 reps and 1% noise.

@@ -1,0 +1,42 @@
+import axelrod as axl
+import os
+
+turns = 200
+repetitions = 10000
+
+seed = 1
+noise = 0.01
+filename = "data/strategies_noisy_10000_interactions.csv"
+
+players = [s() for s in axl.strategies if "length"
+           not in s.classifier["makes_use_of"]]
+players.sort(key=lambda p:p.__repr__())
+
+
+def main(players=players, processes=4):
+    # Deleting the file if it exists
+    try:
+        os.remove(filename)
+    except OSError:
+        pass
+
+    axl.seed(seed)  # Setting a seed
+    assert axl.__version__ == "2.10.0"
+    print("Axelrod version", axl.__version__)
+    print(len(players), "Players")
+    print("Seed", seed)
+
+    tournament = axl.Tournament(players, turns=turns,
+                                repetitions=repetitions, noise=noise)
+
+    results = tournament.play(filename=filename, processes=processes)
+    plot = axl.Plot(results)
+    plot.save_all_plots(prefix="assets/noisy")
+    results.write_summary('assets/noisy_summary.csv')
+
+if __name__ == "__main__":
+    import sys
+    import multiprocessing
+    processes = multiprocessing.cpu_count()
+
+    main(processes=processes)

### 2017-05-18 src/run_10000_noise.py
Change run commands.

@@ -29,9 +29,11 @@ def main(players=players, processes=4):
     tournament = axl.Tournament(players, turns=turns,
                                 repetitions=repetitions, noise=noise)
 
-    results = tournament.play(filename=filename, processes=processes)
+    results = tournament.play(filename=filename, processes=processes,
+                              progress_bar=False)
     plot = axl.Plot(results)
-    plot.save_all_plots(prefix="assets/noisy")
+    plot.save_all_plots(prefix='assets/noisy', progress_bar=False,
+                        title_prefix='noisy')
     results.write_summary('assets/noisy_summary.csv')
 
 if __name__ == "__main__":

### 2017-05-19 src/run_10000_std.py
Add script for standard tournament.

@@ -1,0 +1,43 @@
+import axelrod as axl
+import os
+
+turns = 200
+repetitions = 10000
+
+seed = 1
+filename = "data/strategies_std_10000_interactions.csv"
+
+players = [s() for s in axl.strategies if "length"
+           not in s.classifier["makes_use_of"]]
+players.sort(key=lambda p:p.__repr__())
+
+
+def main(players=players, processes=4):
+    # Deleting the file if it exists
+    try:
+        os.remove(filename)
+    except OSError:
+        pass
+
+    axl.seed(seed)  # Setting a seed
+    assert axl.__version__ == "2.10.0"
+    print("Axelrod version", axl.__version__)
+    print(len(players), "Players")
+    print("Seed", seed)
+
+    tournament = axl.Tournament(players, turns=turns,
+                                repetitions=repetitions)
+
+    results = tournament.play(filename=filename, processes=processes,
+                              progress_bar=False)
+    plot = axl.Plot(results)
+    plot.save_all_plots(prefix='assets/std', progress_bar=False,
+                        title_prefix='standard')
+    results.write_summary('assets/std_summary.csv')
+
+if __name__ == "__main__":
+    import sys
+    import multiprocessing
+    processes = multiprocessing.cpu_count()
+
+    main(processes=processes)

### 2017-05-19 src/run_1000_noise.py
Correct number of reps.

@@ -2,11 +2,11 @@ import axelrod as axl
 import os
 
 turns = 200
-repetitions = 10000
+repetitions = 1000
 
 seed = 1
 noise = 0.01
-filename = "data/strategies_noisy_10000_interactions.csv"
+filename = "data/strategies_noisy_1000_interactions.csv"
 
 players = [s() for s in axl.strategies if "length"
            not in s.classifier["makes_use_of"]]

### 2017-05-19 src/run_1000_std.py

@@ -2,10 +2,10 @@ import axelrod as axl
 import os
 
 turns = 200
-repetitions = 10000
+repetitions = 1000
 
 seed = 1
-filename = "data/strategies_std_10000_interactions.csv"
+filename = "data/strategies_std_1000_interactions.csv"
 
 players = [s() for s in axl.strategies if "length"
            not in s.classifier["makes_use_of"]]

### 2017-05-19 src/run_5000_noise.py
Add scripts for 5000 repetitions.

@@ -1,0 +1,44 @@
+import axelrod as axl
+import os
+
+turns = 200
+repetitions = 5000
+
+seed = 1
+noise = 0.01
+filename = "data/strategies_noisy_1000_interactions.csv"
+
+players = [s() for s in axl.strategies if "length"
+           not in s.classifier["makes_use_of"]]
+players.sort(key=lambda p:p.__repr__())
+
+
+def main(players=players, processes=4):
+    # Deleting the file if it exists
+    try:
+        os.remove(filename)
+    except OSError:
+        pass
+
+    axl.seed(seed)  # Setting a seed
+    assert axl.__version__ == "2.10.0"
+    print("Axelrod version", axl.__version__)
+    print(len(players), "Players")
+    print("Seed", seed)
+
+    tournament = axl.Tournament(players, turns=turns,
+                                repetitions=repetitions, noise=noise)
+
+    results = tournament.play(filename=filename, processes=processes,
+                              progress_bar=False)
+    plot = axl.Plot(results)
+    plot.save_all_plots(prefix='assets/noisy_{}'.format(repetitions), progress_bar=False,
+                        title_prefix='noisy')
+    results.write_summary('assets/noisy_summary_{}.csv'.format(repetitions))
+
+if __name__ == "__main__":
+    import sys
+    import multiprocessing
+    processes = multiprocessing.cpu_count()
+
+    main(processes=processes)

### 2017-05-19 src/run_5000_std.py

@@ -1,0 +1,44 @@
+import axelrod as axl
+import os
+
+turns = 200
+repetitions = 5000
+
+seed = 1
+filename = "data/strategies_std_1000_interactions.csv"
+
+players = [s() for s in axl.strategies if "length"
+           not in s.classifier["makes_use_of"]]
+players.sort(key=lambda p:p.__repr__())
+
+
+def main(players=players, processes=4):
+    # Deleting the file if it exists
+    try:
+        os.remove(filename)
+    except OSError:
+        pass
+
+    axl.seed(seed)  # Setting a seed
+    assert axl.__version__ == "2.10.0"
+    print("Axelrod version", axl.__version__)
+    print(len(players), "Players")
+    print("Seed", seed)
+
+    tournament = axl.Tournament(players, turns=turns,
+                                repetitions=repetitions)
+
+    results = tournament.play(filename=filename, processes=processes,
+                              progress_bar=False)
+    plot = axl.Plot(results)
+    plot.save_all_plots(prefix='assets/std_{}'.format(repetitions),
+                        progress_bar=False,
+                        title_prefix='standard')
+    results.write_summary('assets/std_summary_{}.csv'.format(repetitions))
+
+if __name__ == "__main__":
+    import sys
+    import multiprocessing
+    processes = multiprocessing.cpu_count()
+
+    main(processes=processes)

### 2017-05-19 src/run_2000_noise.py
Scripts for 2000 repetitions.

@@ -1,0 +1,44 @@
+import axelrod as axl
+import os
+
+turns = 200
+repetitions = 2000
+
+seed = 1
+noise = 0.01
+filename = "data/strategies_noisy_1000_interactions.csv"
+
+players = [s() for s in axl.strategies if "length"
+           not in s.classifier["makes_use_of"]]
+players.sort(key=lambda p:p.__repr__())
+
+
+def main(players=players, processes=4):
+    # Deleting the file if it exists
+    try:
+        os.remove(filename)
+    except OSError:
+        pass
+
+    axl.seed(seed)  # Setting a seed
+    assert axl.__version__ == "2.10.0"
+    print("Axelrod version", axl.__version__)
+    print(len(players), "Players")
+    print("Seed", seed)
+
+    tournament = axl.Tournament(players, turns=turns,
+                                repetitions=repetitions, noise=noise)
+
+    results = tournament.play(filename=filename, processes=processes,
+                              progress_bar=False)
+    plot = axl.Plot(results)
+    plot.save_all_plots(prefix='assets/noisy_{}'.format(repetitions), progress_bar=False,
+                        title_prefix='noisy')
+    results.write_summary('assets/noisy_summary_{}.csv'.format(repetitions))
+
+if __name__ == "__main__":
+    import sys
+    import multiprocessing
+    processes = multiprocessing.cpu_count()
+
+    main(processes=processes)

### 2017-05-19 src/run_2000_std.py

@@ -1,0 +1,44 @@
+import axelrod as axl
+import os
+
+turns = 200
+repetitions = 2000
+
+seed = 1
+filename = "data/strategies_std_1000_interactions.csv"
+
+players = [s() for s in axl.strategies if "length"
+           not in s.classifier["makes_use_of"]]
+players.sort(key=lambda p:p.__repr__())
+
+
+def main(players=players, processes=4):
+    # Deleting the file if it exists
+    try:
+        os.remove(filename)
+    except OSError:
+        pass
+
+    axl.seed(seed)  # Setting a seed
+    assert axl.__version__ == "2.10.0"
+    print("Axelrod version", axl.__version__)
+    print(len(players), "Players")
+    print("Seed", seed)
+
+    tournament = axl.Tournament(players, turns=turns,
+                                repetitions=repetitions)
+
+    results = tournament.play(filename=filename, processes=processes,
+                              progress_bar=False)
+    plot = axl.Plot(results)
+    plot.save_all_plots(prefix='assets/std_{}'.format(repetitions),
+                        progress_bar=False,
+                        title_prefix='standard')
+    results.write_summary('assets/std_summary_{}.csv'.format(repetitions))
+
+if __name__ == "__main__":
+    import sys
+    import multiprocessing
+    processes = multiprocessing.cpu_count()
+
+    main(processes=processes)

### 2017-05-24 src/run_10000_noise.py
Change filetype for plots

@@ -33,7 +33,7 @@ def main(players=players, processes=4):
                               progress_bar=False)
     plot = axl.Plot(results)
     plot.save_all_plots(prefix='assets/noisy_{}'.format(repetitions), progress_bar=False,
-                        title_prefix='noisy')
+                        title_prefix='noisy', filetype="pdf")
     results.write_summary('assets/noisy_summary_{}.csv'.format(repetitions))
 
 if __name__ == "__main__":

### 2017-05-24 src/run_1000_std.py

@@ -32,7 +32,7 @@ def main(players=players, processes=4):
                               progress_bar=False)
     plot = axl.Plot(results)
     plot.save_all_plots(prefix='assets/std_{}'.format(repetitions), progress_bar=False,
-                        title_prefix='standard')
+                        title_prefix='standard', filetype="pdf")
     results.write_summary('assets/std_summary_{}.csv'.format(repetitions))
 
 if __name__ == "__main__":

### 2017-05-24 src/run_2000_std.py

@@ -33,7 +33,7 @@ def main(players=players, processes=4):
     plot = axl.Plot(results)
     plot.save_all_plots(prefix='assets/std_{}'.format(repetitions),
                         progress_bar=False,
-                        title_prefix='standard')
+                        title_prefix='standard', filetype="pdf")
     results.write_summary('assets/std_summary_{}.csv'.format(repetitions))
 
 if __name__ == "__main__":

### 2017-06-01 main.tex
Authors TODO
Add TODOs for the diagrams to draw.
Small set of updates

@@
 
-This archetype can be used to train memory-$n$ strategies with the parameters
-$n_1=0$ and $m_1=m_2=n$. For $n=1$, the result is WSLS.
-% TODO: doublecheck that it is WSLS
+This archetype can be used to train deterministic memory-$n$ strategies with the
+parameters $n_1=0$ and $m_1=m_2=n$. For $n=1$, the resulting strategy cooperates
+if the last round was mutual cooperation and defects otherwise.
+
+Two strategies in the library, Winner12 and Winner21, from \cite{Mathieu2015},
+are based on lookup tables for $n_1 = 0$, $m_1 = 1$, and $m_2=2$. The strategy
+Winner12 emerged in less than 10 generations of training in our framework using
+a score maximizing objective.
 
@@
 
+Because these strategies inherit many of the properties of the strategies
+on which they are based, including using the match length to defect on the last
+rounds of play, these strategies were omitted from the tournament results.
+
 \section{Results}
@@
 
-The strategies that win the most matches are Defector, Aggrevater, and then a
-series of ensemble strategies called MetaWinner, that combine the strategies
-of many other strategies and take a consensus vote for each move. These are
-followed by handshaking and zero determinant strategies.
+The strategies that win the most matches are Defector, Aggravater, followed by
+handshaking and zero determinant strategies.
 
@@
 
-All training code is available on github. The are objective functions for
+All training code is available on github. There are objective functions for
 * total payoff
@@
 
+% TODO: author contributions
+
 \section*{Acknowledgements}

### 2017-06-01 src/main.py
Refactor script to run tournaments
Also include some parametrized strategies.

@@ -1,0 +1,50 @@
+import axelrod as axl
+import multiprocessing
+import os
+
+from players import players
+
+def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
+         noise=0):
+
+    if processes is None:
+        processes = multiprocessing.cpu_count()
+
+    kind = "std" if noise == 0 else "noisy"
+    prefix = "Standard" if noise == 0 else "Noisy"
+    filename = "data/strategies_{}_{}_interactions.csv".format(kind,
+                                                               repetitions)
+    # Deleting the file if it exists
+    try:
+        os.remove(filename)
+    except OSError:
+        pass
+
+    axl.seed(seed)  # Setting a seed
+    assert axl.__version__ == "2.13.0"
+    print("Axelrod version", axl.__version__)
+    print(len(players), "Players")
+    print("Seed", seed)
+
+    tournament = axl.Tournament(players, turns=turns, repetitions=repetitions,
+                                noise=noise)
+
+    results = tournament.play(filename=filename, processes=processes,
+                              progress_bar=False)
+    plot = axl.Plot(results)
+    plot.save_all_plots(prefix='assets/{}_{}'.format(kind, repetitions),
+                        progress_bar=False,
+                        title_prefix=prefix, filetype="pdf")
+    results.write_summary('assets/{}_summary_{}.csv'.format(kind, repetitions))
+
+if __name__ == "__main__":
+    import sys
+    args = sys.argv[1:]
+
+    repetitions = int(args[0])
+    try:
+        noise = float(args[1])
+    except IndexError:
+        noise = 0
+
+    main(repetitions=repetitions, noise=noise)

### 2017-06-01 src/run_10000_noise.py

@@ -1,44 +1,0 @@
-import axelrod as axl
-import os
-
-turns = 200
-repetitions = 10000
-
-seed = 1
-noise = 0.01
-filename = "data/strategies_noisy_{}_interactions.csv".format(repetitions)
-
-players = [s() for s in axl.strategies if "length"
-           not in s.classifier["makes_use_of"]]
-players.sort(key=lambda p:p.__repr__())
-
-
-def main(players=players, processes=4):
-    # Deleting the file if it exists
-    try:
-        os.remove(filename)
-    except OSError:
-        pass
-
-    axl.seed(seed)  # Setting a seed
-    assert axl.__version__ == "2.10.0"
-    print("Axelrod version", axl.__version__)
-    print(len(players), "Players")
-    print("Seed", seed)
-
-    tournament = axl.Tournament(players, turns=turns,
-                                repetitions=repetitions, noise=noise)
-
-    results = tournament.play(filename=filename, processes=processes,
-                              progress_bar=False)
-    plot = axl.Plot(results)
-    plot.save_all_plots(prefix='assets/noisy_{}'.format(repetitions), progress_bar=False,
-                        title_prefix='noisy', filetype="pdf")
-    results.write_summary('assets/noisy_summary_{}.csv'.format(repetitions))
-
-if __name__ == "__main__":
-    import sys
-    import multiprocessing
-    processes = multiprocessing.cpu_count()
-
-    main(processes=processes)

### 2017-06-01 src/run_10000_std.py

@@ -1,44 +1,0 @@
-import axelrod as axl
-import os
-
-turns = 200
-repetitions = 10000
-
-seed = 1
-filename = "data/strategies_std_{}_interactions.csv".format(repetitions)
-
-players = [s() for s in axl.strategies if "length"
-           not in s.classifier["makes_use_of"]]
-players.sort(key=lambda p:p.__repr__())
-
-
-def main(players=players, processes=4):
-    # Deleting the file if it exists
-    try:
-        os.remove(filename)
-    except OSError:
-        pass
-
-    axl.seed(seed)  # Setting a seed
-    assert axl.__version__ == "2.10.0"
-    print("Axelrod version", axl.__version__)
-    print(len(players), "Players")
-    print("Seed", seed)
-
-    tournament = axl.Tournament(players, turns=turns,
-                                repetitions=repetitions)
-
-    results = tournament.play(filename=filename, processes=processes,
-                              progress_bar=False)
-    plot = axl.Plot(results)
-    plot.save_all_plots(prefix='assets/std_{}'.format(repetitions),
-                        progress_bar=False,
-                        title_prefix='standard', filetype="pdf")
-    results.write_summary('assets/std_summary_{}.csv'.format(repetitions))
-
-if __name__ == "__main__":
-    import sys
-    import multiprocessing
-    processes = multiprocessing.cpu_count()
-
-    main(processes=processes)

### 2017-06-01 src/run_1000_noise.py

@@ -1,44 +1,0 @@
-import axelrod as axl
-import os
-
-turns = 200
-repetitions = 1000
-
-seed = 1
-noise = 0.01
-filename = "data/strategies_noisy_{}_interactions.csv".format(repetitions)
-
-players = [s() for s in axl.strategies if "length"
-           not in s.classifier["makes_use_of"]]
-players.sort(key=lambda p:p.__repr__())
-
-
-def main(players=players, processes=4):
-    # Deleting the file if it exists
-    try:
-        os.remove(filename)
-    except OSError:
-        pass
-
-    axl.seed(seed)  # Setting a seed
-    assert axl.__version__ == "2.10.0"
-    print("Axelrod version", axl.__version__)
-    print(len(players), "Players")
-    print("Seed", seed)
-
-    tournament = axl.Tournament(players, turns=turns,
-                                repetitions=repetitions, noise=noise)
-
-    results = tournament.play(filename=filename, processes=processes,
-                              progress_bar=False)
-    plot = axl.Plot(results)
-    plot.save_all_plots(prefix='assets/noisy_{}'.format(repetitions), progress_bar=False,
-                        title_prefix='noisy', filetype="pdf")
-    results.write_summary('assets/noisy_summary_{}.csv'.format(repetitions))
-
-if __name__ == "__main__":
-    import sys
-    import multiprocessing
-    processes = multiprocessing.cpu_count()
-
-    main(processes=processes)

### 2017-06-01 src/run_1000_std.py

@@ -1,43 +1,0 @@
-import axelrod as axl
-import os
-
-turns = 200
-repetitions = 1000
-
-seed = 1
-filename = "data/strategies_std_{}_interactions.csv".format(repetitions)
-
-players = [s() for s in axl.strategies if "length"
-           not in s.classifier["makes_use_of"]]
-players.sort(key=lambda p:p.__repr__())
-
-
-def main(players=players, processes=4):
-    # Deleting the file if it exists
-    try:
-        os.remove(filename)
-    except OSError:
-        pass
-
-    axl.seed(seed)  # Setting a seed
-    assert axl.__version__ == "2.10.0"
-    print("Axelrod version", axl.__version__)
-    print(len(players), "Players")
-    print("Seed", seed)
-
-    tournament = axl.Tournament(players, turns=turns,
-                                repetitions=repetitions)
-
-    results = tournament.play(filename=filename, processes=processes,
-                              progress_bar=False)
-    plot = axl.Plot(results)
-    plot.save_all_plots(prefix='assets/std_{}'.format(repetitions), progress_bar=False,
-                        title_prefix='standard', filetype="pdf")
-    results.write_summary('assets/std_summary_{}.csv'.format(repetitions))
-
-if __name__ == "__main__":
-    import sys
-    import multiprocessing
-    processes = multiprocessing.cpu_count()
-
-    main(processes=processes)

### 2017-06-01 src/run_2000_noise.py

@@ -1,44 +1,0 @@
-import axelrod as axl
-import os
-
-turns = 200
-repetitions = 2000
-
-seed = 1
-noise = 0.01
-filename = "data/strategies_noisy_{}_interactions.csv".format(repetitions)
-
-players = [s() for s in axl.strategies if "length"
-           not in s.classifier["makes_use_of"]]
-players.sort(key=lambda p:p.__repr__())
-
-
-def main(players=players, processes=4):
-    # Deleting the file if it exists
-    try:
-        os.remove(filename)
-    except OSError:
-        pass
-
-    axl.seed(seed)  # Setting a seed
-    assert axl.__version__ == "2.10.0"
-    print("Axelrod version", axl.__version__)
-    print(len(players), "Players")
-    print("Seed", seed)
-
-    tournament = axl.Tournament(players, turns=turns,
-                                repetitions=repetitions, noise=noise)
-
-    results = tournament.play(filename=filename, processes=processes,
-                              progress_bar=False)
-    plot = axl.Plot(results)
-    plot.save_all_plots(prefix='assets/noisy_{}'.format(repetitions), progress_bar=False,
-                        title_prefix='noisy', filetype="pdf")
-    results.write_summary('assets/noisy_summary_{}.csv'.format(repetitions))
-
-if __name__ == "__main__":
-    import sys
-    import multiprocessing
-    processes = multiprocessing.cpu_count()
-
-    main(processes=processes)

### 2017-06-01 src/run_2000_std.py

@@ -1,44 +1,0 @@
-import axelrod as axl
-import os
-
-turns = 200
-repetitions = 2000
-
-seed = 1
-filename = "data/strategies_std_{}_interactions.csv".format(repetitions)
-
-players = [s() for s in axl.strategies if "length"
-           not in s.classifier["makes_use_of"]]
-players.sort(key=lambda p:p.__repr__())
-
-
-def main(players=players, processes=4):
-    # Deleting the file if it exists
-    try:
-        os.remove(filename)
-    except OSError:
-        pass
-
-    axl.seed(seed)  # Setting a seed
-    assert axl.__version__ == "2.10.0"
-    print("Axelrod version", axl.__version__)
-    print(len(players), "Players")
-    print("Seed", seed)
-
-    tournament = axl.Tournament(players, turns=turns,
-                                repetitions=repetitions)
-
-    results = tournament.play(filename=filename, processes=processes,
-                              progress_bar=False)
-    plot = axl.Plot(results)
-    plot.save_all_plots(prefix='assets/std_{}'.format(repetitions),
-                        progress_bar=False,
-                        title_prefix='standard', filetype="pdf")
-    results.write_summary('assets/std_summary_{}.csv'.format(repetitions))
-
-if __name__ == "__main__":
-    import sys
-    import multiprocessing
-    processes = multiprocessing.cpu_count()
-
-    main(processes=processes)

### 2017-06-01 src/run_5000_noise.py

@@ -1,44 +1,0 @@
-import axelrod as axl
-import os
-
-turns = 200
-repetitions = 5000
-
-seed = 1
-noise = 0.01
-filename = "data/strategies_noisy_{}_interactions.csv".format(repetitions)
-
-players = [s() for s in axl.strategies if "length"
-           not in s.classifier["makes_use_of"]]
-players.sort(key=lambda p:p.__repr__())
-
-
-def main(players=players, processes=4):
-    # Deleting the file if it exists
-    try:
-        os.remove(filename)
-    except OSError:
-        pass
-
-    axl.seed(seed)  # Setting a seed
-    assert axl.__version__ == "2.10.0"
-    print("Axelrod version", axl.__version__)
-    print(len(players), "Players")
-    print("Seed", seed)
-
-    tournament = axl.Tournament(players, turns=turns,
-                                repetitions=repetitions, noise=noise)
-
-    results = tournament.play(filename=filename, processes=processes,
-                              progress_bar=False)
-    plot = axl.Plot(results)
-    plot.save_all_plots(prefix='assets/noisy_{}'.format(repetitions), progress_bar=False,
-                        title_prefix='noisy', filetype="pdf")
-    results.write_summary('assets/noisy_summary_{}.csv'.format(repetitions))
-
-if __name__ == "__main__":
-    import sys
-    import multiprocessing
-    processes = multiprocessing.cpu_count()
-
-    main(processes=processes)

### 2017-06-01 src/run_5000_std.py

@@ -1,44 +1,0 @@
-import axelrod as axl
-import os
-
-turns = 200
-repetitions = 5000
-
-seed = 1
-filename = "data/strategies_std_{}_interactions.csv".format(repetitions)
-
-players = [s() for s in axl.strategies if "length"
-           not in s.classifier["makes_use_of"]]
-players.sort(key=lambda p:p.__repr__())
-
-
-def main(players=players, processes=4):
-    # Deleting the file if it exists
-    try:
-        os.remove(filename)
-    except OSError:
-        pass
-
-    axl.seed(seed)  # Setting a seed
-    assert axl.__version__ == "2.10.0"
-    print("Axelrod version", axl.__version__)
-    print(len(players), "Players")
-    print("Seed", seed)
-
-    tournament = axl.Tournament(players, turns=turns,
-                                repetitions=repetitions)
-
-    results = tournament.play(filename=filename, processes=processes,
-                              progress_bar=False)
-    plot = axl.Plot(results)
-    plot.save_all_plots(prefix='assets/std_{}'.format(repetitions),
-                        progress_bar=False,
-                        title_prefix='standard', filetype="pdf")
-    results.write_summary('assets/std_summary_{}.csv'.format(repetitions))
-
-if __name__ == "__main__":
-    import sys
-    import multiprocessing
-    processes = multiprocessing.cpu_count()
-
-    main(processes=processes)

### 2017-06-01 src/main.py
Add noise to title prefix

@@ -11,7 +11,7 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
         processes = multiprocessing.cpu_count()
 
     kind = "std" if noise == 0 else "noisy"
-    prefix = "Standard" if noise == 0 else "Noisy"
+    prefix = "Standard" if noise == 0 else "Noisy ({})".format(noise)
     filename = "data/strategies_{}_{}_interactions.csv".format(kind,
                                                                repetitions)
     # Deleting the file if it exists

### 2017-06-04 main.tex
Mostly citations

@@
 
-Key points:
-* We trained several different strategies and they all are tournament
-winners
-* works for standard, noisy, and moran
-* Complex strategies can fare well
-* the best strategies are cooperative yet punitive
-* copious references to W. and D. Ashlock
-
-Todo:
-* better title
-
 \begin{abstract}
@@
 * Update on Axelrod Library
-Description of strategy space and tournament capabilities
-Includes many prior tournament winners (OmegaTFT, ZDGTFT2)
-Some original strategies but mostly from the literature
+
+The Axelrod library \cite{knight2016open} now contains over 200 strategies,
+many from the scientific
+literature, including classic strategies like Win Stay Lose Shift
+\cite{nowak1993strategy} and
+previous tournament winners such as OmegaTFT \cite{slany2007some},
+ Adaptive Pavlov \cite{li2007design}, and ZDGTFT2 \cite{stewart2012extortion}.
 
 % TODO: cite earlier tournaments
+
+There are several previous publications that use evolutionary algorithms to
+evolve IPD strategies in various circumstances \cite{fogel1993evolving} \cite{ashlock2006training}
+\cite{ashlock2006changes} \cite{vassiliades2010multiagent} \cite{ashlock2014shaped}
+\cite{ashlock2014evolution} \cite{ashlock2015multiple} \cite{barlow2015varying}
+\cite{sudo2015effects}. See also \cite{gaudesi2016exploiting} for a strategy trained to win against
+a collection of well-known IPD opponents. Our results are unique in that we are
+able to train against a large collection of well-known strategies available in
+the scientific literature.
 
@@
 Winner12 emerged in less than 10 generations of training in our framework using
-a score maximizing objective.
+a score maximizing objective. Strategies nearly identical to Winner21 arise
+from training with a Moran process objective.
 
@@
 memory one strategy was trained and is called PSO Gambler Mem 1, with
-probabilities $\ldots$. Though it performs well in deterministic tournaments
+probabilities $(\text{Pr(C|CC)}, \text{Pr(C|CD)}, \text{Pr(C|DC)}, \text{Pr(C|DD)}) = (1, 0.5217, 0, 0.121)$. Though it performs well in deterministic tournaments
 it is not as good as the longer memory strategies, and is bested by a similar
@@
 
+These strategies are trained with a particle swarm algorithm rather than an
+evolutionary algorithm (though the former would suffice). Particle swarm
+algorithms have been used to trained IPD strategies previously
+\cite{franken2005particle}.
+
 % TODO: quantify how stochastic
-% TODO: include memory one four vector
 
@@
 
-% TODO: Cite earlier ANN papers including Ashlock
 % TODO: list features
@@
 of other strategies, including classic strategies like TitForTat, encode
-handshakes, and gruding strategies that always defect after an opponent
+handshakes, and grudging strategies that always defect after an opponent
 defection.
 
-% TODO: Cite Ashlock FSM papers
 % TODO: One or more diagrams
@@
 sufficient -- neural networks with fewer nodes and features and finite state
-machines with fewer states may suffice.
-% TODO: Cite Ashlock paper on parameter capacity for trained strategies
+machines with fewer states may suffice. See \cite{ashlock2013impact} for
+discussion of resource availability for IPD strategies.
 

### 2017-06-04 main.tex
More references

@@
 There are several previous publications that use evolutionary algorithms to
-evolve IPD strategies in various circumstances \cite{fogel1993evolving} \cite{ashlock2006training}
+evolve IPD strategies in various circumstances \cite{marks1989niche} \cite{fogel1993evolving} \cite{ashlock2006training}
 \cite{ashlock2006changes} \cite{vassiliades2010multiagent} \cite{ashlock2014shaped}
 \cite{ashlock2014evolution} \cite{ashlock2015multiple} \cite{barlow2015varying}
-\cite{sudo2015effects}. See also \cite{gaudesi2016exploiting} for a strategy trained to win against
-a collection of well-known IPD opponents. Our results are unique in that we are
-able to train against a large collection of well-known strategies available in
-the scientific literature.
+\cite{sudo2015effects}. See also \cite{gaudesi2016exploiting} for a strategy
+trained to win against a collection of well-known IPD opponents and see
+\cite{franken2005particle} for a prior use of particle swarm algorithms. Our
+results are unique in that we are able to train against a large collection of
+well-known strategies available in the scientific literature.
 

### 2017-06-05 src/main.py
Change script to only calculate interactions.

@@ -12,8 +12,9 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
 
     kind = "std" if noise == 0 else "noisy"
     prefix = "Standard" if noise == 0 else "Noisy ({})".format(noise)
-    filename = "data/strategies_{}_{}_interactions.csv".format(kind,
-                                                               repetitions)
+    filename = "data/strategies_{}_{}_{}_interactions.csv".format(kind,
+                                                               repetitions,
+                                                               seed)
     # Deleting the file if it exists
     try:
         os.remove(filename)
@@ -29,22 +30,19 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
     tournament = axl.Tournament(players, turns=turns, repetitions=repetitions,
                                 noise=noise)
 
-    results = tournament.play(filename=filename, processes=processes,
-                              progress_bar=False)
-    plot = axl.Plot(results)
-    plot.save_all_plots(prefix='assets/{}_{}'.format(kind, repetitions),
-                        progress_bar=False,
-                        title_prefix=prefix, filetype="pdf")
-    results.write_summary('assets/{}_summary_{}.csv'.format(kind, repetitions))
+    tournament.play(filename=filename, processes=processes,
+                    build_results=False, progress_bar=False)
 
 if __name__ == "__main__":
     import sys
     args = sys.argv[1:]
 
     repetitions = int(args[0])
+    seed = int(args[1])
+
     try:
-        noise = float(args[1])
+        noise = float(args[2])
     except IndexError:
         noise = 0
 
-    main(repetitions=repetitions, noise=noise)
+    main(repetitions=repetitions, seed=seed, noise=noise)

### 2017-06-07 src/analyse.py
Add script to analyse from files.

@@ -1,0 +1,16 @@
+import axelrod as axl
+
+def main(filename):
+
+    assert axl.__version__ == "2.13.0"
+
+    prefix = "Standard" if "standard" in filename else "Noisy"
+    results = axl.ResultSetFromFile(filename=filename, progress_bar=False)
+    plot = axl.Plot(results)
+    plot.save_all_plots(prefix="assets/{}".format(prefix), progress_bar=False,
+                        title_prefix=prefix, filetype="pdf")
+
+if __name__ == "__main__":
+    import sys
+    filename = sys.argv[1]
+    main(filename)

### 2017-06-16 src/analyse.py
Output results data.
Add output of:

- Scores
- Payoff matrix
- Payoff stdev

To compressed gz file.

@@ -1,4 +1,5 @@
 import axelrod as axl
+import numpy as np
 
 def main(filename):
 
@@ -6,10 +7,35 @@ def main(filename):
 
     prefix = "Standard" if "standard" in filename else "Noisy"
     results = axl.ResultSetFromFile(filename=filename, progress_bar=False)
-    # plot = axl.Plot(results)
-    # plot.save_all_plots(prefix="assets/{}".format(prefix), progress_bar=False,
-                        # title_prefix=prefix, filetype="pdf")
+    plot = axl.Plot(results)
+    plot.save_all_plots(prefix="assets/{}".format(prefix), progress_bar=False,
+                        title_prefix=prefix, filetype="pdf")
     results.write_summary("assets/{}_summary.csv".format(prefix))
+
+    # Write the total scores per tournament for each player to "assets/".
+    # This data is a #repetitions (rows) by #players (columns) array with
+    # X_{ij} corresponding to the TOTAL score obtained by player j in repetition
+    # i of the tournament.
+    scores_per_tournament = np.array(results.scores).transpose()
+    np.savetxt(fname="assets/{}_scores.gz".format(prefix),
+               X=scores_per_tournament)
+
+    # Write the payoff of each player against every other player to "assets/".
+    # This data is a #players (rows) by #players (rows) array with X_{ij}
+    # corresponding to the mean score of player i against player j
+    payoff_matrix = np.array(results.payoff_matrix)
+    np.savetxt(fname="assets/{}_payoff_matrix.gz".format(prefix),
+               X=payoff_matrix, delimiter=",")
+
+    # Write the stdv payoff of each player against every other player to
+    # "assets/". This data is a #players (rows) by #players (rows) array with
+    # X_{ij} corresponding to the standard deviation of the score of player i
+    # against player j
+    payoff_stdev_matrix = np.array(results.payoff_stddevs)
+    np.savetxt(fname="assets/{}_payoff_stdev_matrix.gz".format(prefix),
+               X=payoff_matrix, delimiter=",")
+
+
 
 if __name__ == "__main__":
     import sys

### 2017-06-16 src/analyse.py
Correct error.

@@ -18,7 +18,7 @@ def main(filename):
     # i of the tournament.
     scores_per_tournament = np.array(results.scores).transpose()
     np.savetxt(fname="assets/{}_scores.gz".format(prefix),
-               X=scores_per_tournament)
+               X=scores_per_tournament, delimiter=",")
 
     # Write the payoff of each player against every other player to "assets/".
     # This data is a #players (rows) by #players (rows) array with X_{ij}
@@ -33,7 +33,7 @@ def main(filename):
     # against player j
     payoff_stdev_matrix = np.array(results.payoff_stddevs)
     np.savetxt(fname="assets/{}_payoff_stdev_matrix.gz".format(prefix),
-               X=payoff_matrix, delimiter=",")
+               X=payoff_stdev_matrix, delimiter=",")
 
 
 

### 2017-06-19 main.tex
Added plots and some tables for tournament results

@@
 \usepackage{fancyvrb}
+
+\usepackage{pdflscape}
 
@@
 \begin{abstract}
-    We present several powerful strategies for the Iterated
+    We present tournament results and several powerful strategies for the Iterated
     Prisoner's Dilemma created using reinforcement learning techniques
@@
 
+% TODO: more
+
 The Axelrod library \cite{knight2016open} now contains over 200 strategies,
-many from the scientific
-literature, including classic strategies like Win Stay Lose Shift
-\cite{nowak1993strategy} and
-previous tournament winners such as OmegaTFT \cite{slany2007some},
- Adaptive Pavlov \cite{li2007design}, and ZDGTFT2 \cite{stewart2012extortion}.
+many from the scientific literature, including classic strategies like Win Stay
+Lose Shift \cite{nowak1993strategy} and previous tournament winners such as
+OmegaTFT \cite{slany2007some}, Adaptive Pavlov \cite{li2007design}, and
+ZDGTFT2 \cite{stewart2012extortion}.
 
-% TODO: cite earlier tournaments
+% TODO: discuss earlier tournaments
 
@@
 First impressions matter in the IPD. The library includes a strategy
-called EvolvedLookerUp2_2_2 which is among the top strategies in the library.
+called EvolvedLookerUp2\_2\_2 which is among the top strategies in the library.
 
@@
 probabilities being 0 or 1. At one time this strategy outperformed
-EvolvedLookerUp2_2_2.
+EvolvedLookerUp2\_2\_2.
 
@@
 
-\subsection{ANN}
+\subsection{ANN: Single Layer Artificial Neural Network}
 
@@
 
-% TODO: One or more diagrams
+% TODO: One or more FSM diagrams
 
@@
 11 performing strategies by mean payoff are all strategies trained to maximize
-total payoff against a subset of the strategies (Figure \ref{}). The next strategy is 
+total payoff against a subset of the strategies (Table \ref{tbl:standard_score}).
+The next strategy is
 Desired Belief Strategy (DBS) which actively analyzes the opponent and responds
-accordingly. The next two strategies are Winner12, based on a lookup table, and
-Fool Me Once, a strategy that defects indefinitely on the second defection.
+accordingly. The next two strategies are Winner12, based on a lookup table,
+Omega TFT, and Fool Me Once, a grudging strategy that defects indefinitely on
+the second defection. All strategies in the tournament follow a simple set of
+rules in accordance with earlier tournaments:
+\begin{itemize}
+  \item Players carry no acquired state between matches
+  \item Players cannot observe the outcome of other matches
+  \item Players cannot identify their opponent by any label or identifier
+  \item Players cannot manipulate or inspect their opponents in any way
+\end{itemize}
 
-Pairwise payoff results are given as a heatmap (Figure \ref{}) which
-shows that the many strategies achieve mutual cooperation with each other and
+Pairwise payoff results are given as a heatmap (Figure ) which
+shows that many strategies achieve mutual cooperation with each other and
 that the top performing strategies never defect first but are able to exploit
@@
 The strategies that win the most matches are Defector, Aggravater, followed by
-handshaking and zero determinant strategies.
+handshaking and zero determinant strategies. This includes two handshaking
+strategies that were the result of training to maximize Moran process fixation.
+No strategies were trained specifically to win matches. None of the top scoring
+strategies appear in the top 20 list of strategies ranked by match wins.
 
 % Table of best strategies
+\begin{table}[!hbtp]
+    \centering
+        \input{./tex/standard_scores.tex}
+        \caption{Standard Tournament: Top Ranking Strategies by Median Score in 15,000 Tournaments}
+        \label{tbl:standard_score}
+\end{table}
+
+\begin{landscape}
+    \includegraphics[width=\paperwidth]{plots/Standard_boxplot.pdf}
+\end{landscape}
+
 % \includegraphics{strategies_std_boxplot.svg}
@@
 is flipped. The best performing strategies in mean payoff are DBS, designed
-to correct for noise, followed by two finite state machine strategies trained
-in the presence of noise, and OmegaTFT (also designed to handle noise). The
-strategies trained in the presence of noise are also among the best performers
-in the absence of noise.
+to correct for noise, followed by two strategies trained
+in the presence of noise, Spiteful TFT (TFT but defects indefinitely if the
+opponent defects twice consecutively), two strategies trained without noise, then
+OmegaTFT (also designed to handle noise).
 
-The cluster of mutually cooperative strategies is broken by the noise at 5\%. A
-similar collection of players excels at winning matches but again they have
-a poor total payoff.
+The strategies trained in the presence of noise are also among the best performers
+in the absence of noise. The cluster of mutually cooperative strategies is
+broken by the noise at 5\%. A similar collection of players excels at winning
+matches but again they have a poor total payoff.
+
+The strategies tallying the most wins are somewhat similar, with Defector, the
+handshaking CollectiveStrategy, and Aggravate appearing as the top three again,
+followed by Spiteful TFT and strategies designed to be retaliatory. Players ranked
+12, 13, and 15 (TF3, Fool Me Once, and Evolved ANN 5) all appear in the top 15
+strategies by score, indicating that noise breaks the asymmetry between wins
+and scores to some extent.
 
 % Table of best strategies
-% \includegraphics{strategies_noisy_boxplot.svg}
+
+\begin{table}[!hbtp]
+    \centering
+        \input{./tex/noisy_scores.tex}
+        \caption{Noisy Tournament: Top Ranking Strategies by Median Score in a
+        15000 Tournaments with 5\% noise}
+        \label{tbl:noisy_score}
+\end{table}
+
+\begin{landscape}
+    \includegraphics[width=\paperwidth]{plots/Noisy_boxplot.pdf}
+\end{landscape}
 % \includegraphics{strategies_noisy_payoff.svg}
@@
 best performing strategies in each generation are persisted, variants created,
-and objective functions computed again. This process continues for approxaimtely
+and objective functions computed again. This process continues for approximately
 200 generations or until strategies no longer improve significantly.
 
-% Diagram with ANN training performance
+% Todo: Diagram with ANN training performance?
 
@@
 
-The tournament results indicate that pretrained strategies are generally better
+The tournament results indicate that pre-trained strategies are generally better
 than human designed strategies at maximizing payoff against a diverse set of
@@
 standard machine learning techniques that are able to achieve a higher mean
-score than any other known opponent. All of the trained strategies use many
-rounds of the history of play (some using all of it) and outperform memory-one
+score than any other known opponent in a standard tournament. Most of the trained
+strategies use multiple rounds of the history of play (some using all of it) and
+outperform memory-one strategies (though the trained memory one strategy performs
+well). The generic structure of the trained strategy did not appear to be
+critical -- strategies based on lookup tables, finite state machines, and stochastic
+variants all performed well. Single layer neural networks also performed well
+though these had some aspect of human involvement in the selection of features.
+The success of the other strategy types suggests that a deeper network that
+incorporates feature engineering would likely also perform well.
+
+In opposition to historical tournament results and community folklore,
+our results show that complex strategies can be very effective for the
+IPD. It is not the complexity of strategies that is disadvantageous; rather that directly
+designing a broadly effective strategy is no easy task. Of all the human-designed
+strategies in the library, only DBS consistently performs well, and it is
+substantially more complex than traditional tournament winners like TFT, OmegaTFT,
+and zero determinant strategies. Furthermore, dealing with noise is difficult
+for most strategies. Two strategies designed specifically to account for noise,
+DBS and OmegaTFT, perform well and only DBS performs better than our trained
 strategies.
 
-Directly designing an effective strategy is no easy task. Of all the actively
-learning strategies in the library, only DBS performs well. The authors trained
-a neural network to predict opponents' next moves with high accuracy but basing
-a strategy on the predictions proved difficult -- it is necessary to consider
-the downstream consequences of a defection and direct training of strategy
-outputs generally performed better.
-
-These results suggest that, in opposition to historical tournament results
-and community folklore, that complex strategies can be very effective for the
-IPD. It is not the complexity of strategies that is disadvantageous, rather it
-is apparently too difficult for humans to design complex yet effective
-strategies, DBS being a notable exception.
-
-Furthermore, dealing with noise is difficult for most strategies. Two strategies
-designed specifically to account for noise, DBS and OmegaTFT, perform well and
-only DBS performs better than directly trained finite state machine strategies.
-
-Of all the strategies trained to maximize their mean score all are generally
+Of the strategies trained to maximize their mean score all are generally
 cooperative, not defecting until the opponent defects. Maximizing for individual
@@
 the fact that mutual cooperation is an unstable equilibrium for the prisoner's
-dilemma. Specifically we note that the reinforcement learning process does not
+dilemma. Specifically we note that the reinforcement learning process for maximizing
+payout does not
 lead to exploitative zero determinant strategies, which may be a result of the
-collection of training strategies, many of which retailate harshly.
+collection of training strategies, many of which retaliate harshly.
 
 Finally, we note that as the library grows, the top performing strategies
-sometimes shuffle, and are not retrained regularly. The precise parameters
-that are optimal will depend on the pool of opponents. Moreover we have not
-extensively trained strategies to determine the minimum parameters that are
-sufficient -- neural networks with fewer nodes and features and finite state
-machines with fewer states may suffice. See \cite{ashlock2013impact} for
-discussion of resource availability for IPD strategies.
+sometimes shuffle, and are not retrained regularly. Most of the strategies were
+trained on an earlier version of the library (v2.2.0) that did not include DBS
+and several other opponents. The precise parameters that are optimal will depend
+on the pool of opponents. Moreover we have not extensively trained strategies to
+determine the minimum parameters that are sufficient -- neural networks with
+fewer nodes and features and finite state machines with fewer states may suffice.
+See \cite{ashlock2013impact} for discussion of resource availability for IPD strategies.
 
@@
 * further refine features and training parameters
+
+% TODO: Full strategy list
 
@@
 \printbibliography
+
+\end{document}

### 2017-06-19 main.tex
Add payoff plots
Add winplots

@@
 \begin{landscape}
+    \begin{figure}[!hbtp]
         \includegraphics[width=\paperwidth]{plots/Standard_boxplot.pdf}
+        \caption{Ranking by Median Payoff for the Standard Tournament}
+    \end{figure}
 \end{landscape}
 
-% \includegraphics{strategies_std_boxplot.svg}
-% \includegraphics{strategies_std_payoff.svg}
-% \includegraphics{strategies_std_winplot.svg}
+\begin{landscape}
+    \begin{figure}[!hbtp]
+        \includegraphics[width=\paperwidth]{plots/Standard_winplot.pdf}
+        \caption{Ranking by Total wins for the Standard Tournament}
+    \end{figure}
+\end{landscape}
+
+\begin{figure}[!hbtp]
+    \includegraphics[width=\paperwidth]{plots/Standard_payoff.pdf}
+    \caption{Pairwise Match results for the Standard Tournament}
+\end{figure}
 
@@
 \begin{landscape}
+    \begin{figure}[!hbtp]
         \includegraphics[width=\paperwidth]{plots/Noisy_boxplot.pdf}
+        \caption{Ranking by Median Payoff for the Noisy Tournament}
+    \end{figure}
 \end{landscape}
-% \includegraphics{strategies_noisy_payoff.svg}
-% \includegraphics{strategies_noisy_winplot.svg}
+
+\begin{landscape}
+    \begin{figure}[!hbtp]
+        \includegraphics[width=\paperwidth]{plots/Noisy_winplot.pdf}
+        \caption{Ranking by Total wins for the Noisy Tournament}
+    \end{figure}
+\end{landscape}
+
+\begin{figure}[!hbtp]
+    \includegraphics[width=\paperwidth]{plots/Noisy_payoff.pdf}
+    \caption{Pairwise Match results for the Noisy Tournament}
+\end{figure}
 

### 2017-06-20 main.tex
Add fingerprints

@@
 
+Using the method of fingerprinting described in \cite{ashlock2008fingerprinting}
+\cite{ashlock2009fingerprint}, we can compare
+strategies. For the top performing noisy strategies there is a striking similarity
+in the fingerprints.
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./plots/EvolvedLookerUp2_2_2.png}
+        \caption{Fingerprint for EvolvedLookerUp\_2\_2\_2}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./plots/Evolved_HMM_5.png}
+        \caption{Fingerprint for Evolved\_HMM\_5}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./plots/Evolved_FSM_16.png}
+        \caption{Fingerprint for Evolved\_FSM\_16}
+    \end{subfigure}%
+
+    \caption{Comparison of Fingerprints for Noisy Tournament Top 3}
+    \label{fig:comparison_fingerprint_noisy}
+\end{figure}
+
 \subsection{Noisy Tournament}
 
-We also ran noisy tournaments in which there is a 5\% chance that an action
+We also ran noisy tournaments in which there is a 10\% chance that an action
 is flipped. The best performing strategies in mean payoff are DBS, designed
@@
         \caption{Noisy Tournament: Top Ranking Strategies by Median Score in a
-        15000 Tournaments with 5\% noise}
+        15000 Tournaments with 10\% noise}
         \label{tbl:noisy_score}
@@
     \caption{Pairwise Match results for the Noisy Tournament}
+\end{figure}
+
+Using the method of fingerprinting described in \cite{ashlock2008fingerprinting}
+\cite{ashlock2009fingerprint}, we can compare
+strategies. For the top performing noisy strategies there is a striking similarity
+in the fingerprints.
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./plots/DBS.png}
+        \caption{Fingerprint for DBS}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./plots/Evolved_ANN_5_Noise_05.png}
+        \caption{Fingerprint for Evolved\_ANN\_5\_Noise\_05}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./plots/Evolved_FSM_16_Noise_05.png}
+        \caption{Fingerprint for Evolved\_FSM\_16\_Noise\_05}
+    \end{subfigure}%
+
+    \caption{Comparison of Fingerprints for Noisy Tournament Top 3}
+    \label{fig:comparison_fingerprint_noisy}
 \end{figure}

### 2017-06-20 src/analyse.py
Add writing of wins to analysis.

@@ -20,6 +20,14 @@ def main(filename):
     np.savetxt(fname="assets/{}_scores.gz".format(prefix),
                X=scores_per_tournament, delimiter=",")
 
+    # Write the total wins per tournament for each player to "assets/".
+    # This data is a #repetitions (rows) by #players (columns) array with
+    # X_{ij} corresponding to the TOTAL wins obtained by player j in repetition
+    # i of the tournament.
+    wins_per_tournament = np.array(results.wins).transpose()
+    np.savetxt(fname="assets/{}_wins.gz".format(prefix),
+               X=wins_per_tournament, delimiter=",")
+
     # Write the payoff of each player against every other player to "assets/".
     # This data is a #players (rows) by #players (rows) array with X_{ij}
     # corresponding to the mean score of player i against player j

### 2017-06-22 src/main.py
Write analysis back in to main.
The plan is to run smaller tournaments and amalgamate the data.

@@ -13,8 +13,8 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
     kind = "std" if noise == 0 else "noisy"
     prefix = "Standard" if noise == 0 else "Noisy ({})".format(noise)
     filename = "data/strategies_{}_{}_{}_interactions.csv".format(kind,
-                                                               repetitions,
-                                                               seed)
+                                                                  repetitions,
+                                                                  seed)
     # Deleting the file if it exists
     try:
         os.remove(filename)
@@ -26,12 +26,49 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
     print("Axelrod version", axl.__version__)
     print(len(players), "Players")
     print("Seed", seed)
+    print("Repetitions", repetitions)
+    print("Noise", noise)
 
     tournament = axl.Tournament(players, turns=turns, repetitions=repetitions,
                                 noise=noise)
 
-    tournament.play(filename=filename, processes=processes,
-                    build_results=False, progress_bar=False)
+    results = tournament.play(filename=filename, processes=processes,
+                              progress_bar=False)
+
+
+    # Write summary for each seed
+    results.write_summary("assets/{}_{}_summary.csv".format(prefix, seed))
+
+    # Write the total scores per tournament for each player to "assets/".
+    # This data is a #repetitions (rows) by #players (columns) array with
+    # X_{ij} corresponding to the TOTAL score obtained by player j in repetition
+    # i of the tournament.
+    scores_per_tournament = np.array(results.scores).transpose()
+    np.savetxt(fname="assets/{}_{}_scores.gz".format(prefix, seed),
+               X=scores_per_tournament, delimiter=",")
+
+    # Write the total wins per tournament for each player to "assets/".
+    # This data is a #repetitions (rows) by #players (columns) array with
+    # X_{ij} corresponding to the TOTAL wins obtained by player j in repetition
+    # i of the tournament.
+    wins_per_tournament = np.array(results.wins).transpose()
+    np.savetxt(fname="assets/{}_{}_wins.gz".format(prefix, seed),
+               X=wins_per_tournament, delimiter=",")
+
+    # Write the payoff of each player against every other player to "assets/".
+    # This data is a #players (rows) by #players (rows) array with X_{ij}
+    # corresponding to the mean score of player i against player j
[…]

### 2017-06-22 src/main.py
Add docstring.

@@ -1,6 +1,20 @@
+"""
+Runs a tournament and writes:
+
+    - interactions
+    - summary
+    - scores per tournament (rows) per player (columns)
+    - wins per tournament (rows) per player (columns)
+    - mean payoff matrix
+    - mean stdv payoff matrix
+
+to separate files with the prefix: `<seed>_<noise>_<repetitions>`.
+"""
+
 import axelrod as axl
 import multiprocessing
 import os
+import numpy as np
 
 from players import players
 
@@ -10,11 +24,9 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
     if processes is None:
         processes = multiprocessing.cpu_count()
 
-    kind = "std" if noise == 0 else "noisy"
-    prefix = "Standard" if noise == 0 else "Noisy ({})".format(noise)
-    filename = "data/strategies_{}_{}_{}_interactions.csv".format(kind,
-                                                                  repetitions,
-                                                                  seed)
+    prefix = "{}_{}_{}".format(seed, int(100 * noise), repetitions)
+    filename = "data/{}_interactions.csv".format(prefix)
+
     # Deleting the file if it exists
     try:
         os.remove(filename)
@@ -37,14 +49,14 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
 
 
     # Write summary for each seed
-    results.write_summary("assets/{}_{}_summary.csv".format(prefix, seed))
+    results.write_summary("assets/{}_summary.csv".format(prefix))
 
     # Write the total scores per tournament for each player to "assets/".
     # This data is a #repetitions (rows) by #players (columns) array with
     # X_{ij} corresponding to the TOTAL score obtained by player j in repetition
     # i of the tournament.
     scores_per_tournament = np.array(results.scores).transpose()
-    np.savetxt(fname="assets/{}_{}_scores.gz".format(prefix, seed),
+    np.savetxt(fname="assets/{}_scores.gz".format(prefix),
                X=scores_per_tournament, delimiter=",")
 
     # Write the total wins per tournament for each player to "assets/".
@@ -52,14 +64,14 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
     # X_{ij} corresponding to the TOTAL wins obtained by player j in repetition
     # i of the tournament.
     wins_per_tournament = np.array(results.wins).transpose()
[…]

### 2017-06-22 src/submit_ml_jobs.sh
Write script to write pbs files.

@@ -1,0 +1,20 @@
+qsub pbs_files/ml-0-5-1000.pbs
+qsub pbs_files/ml-0-0-1000.pbs
+qsub pbs_files/ml-1-5-1000.pbs
+qsub pbs_files/ml-1-0-1000.pbs
+qsub pbs_files/ml-2-5-1000.pbs
+qsub pbs_files/ml-2-0-1000.pbs
+qsub pbs_files/ml-3-5-1000.pbs
+qsub pbs_files/ml-3-0-1000.pbs
+qsub pbs_files/ml-4-5-1000.pbs
+qsub pbs_files/ml-4-0-1000.pbs
+qsub pbs_files/ml-5-5-1000.pbs
+qsub pbs_files/ml-5-0-1000.pbs
+qsub pbs_files/ml-6-5-1000.pbs
+qsub pbs_files/ml-6-0-1000.pbs
+qsub pbs_files/ml-7-5-1000.pbs
+qsub pbs_files/ml-7-0-1000.pbs
+qsub pbs_files/ml-8-5-1000.pbs
+qsub pbs_files/ml-8-0-1000.pbs
+qsub pbs_files/ml-9-5-1000.pbs
+qsub pbs_files/ml-9-0-1000.pbs

### 2017-06-22 src/write_pbs_files.py

@@ -1,0 +1,40 @@
+"""
+Write the pbs file (scheduler files for cluster) and a `./submit_ml_jobs.sh`
+script to submit them.
+"""
+min_seed = 0
+max_seed = 10  # The number of jobs is max-min
+repetitions = 1000
+noises = [0.05, 0]
+
+pbs_filenames = []
+
+for seed in range(min_seed, max_seed):
+    for noise in noises:
+        pbs_file = """#!/bin/bash
+#PBS -q workq
+#PBS -N {}-{}-{}
+#PBS -P PR350
+#PBS -o {}-{}.txt
+#PBS -e {}-{}.txt
+#PBS -l select=1:ncpus=16:mpiprocs=16
+#PBS -l place=scatter:excl
+#PBS -l walltime=70:00:00
+
+export MPLBACKEND="agg"
+# Run std
+cd /scratch/smavak/ml-paper/src
+/home/smavak/anaconda3/envs/ml-paper/bin/python main.py {} {} {}
+""".format(seed, noise, repetitions,
+           seed, noise,
+           seed, noise,
+           repetitions, seed, noise)
+        filename = "pbs_files/ml-{}-{}-{}.pbs".format(seed, int(100 * noise),
+                                                      repetitions)
+        with open(filename, "w") as f:
+            f.write(pbs_file)
+        pbs_filenames.append(filename)
+
+    with open("submit_ml_jobs.sh", "w") as f:
+        for filename in pbs_filenames:
+            f.write("qsub {}\n".format(filename))

### 2017-06-23 src/analyse.py
Remove uneeded file.

@@ -1,51 +1,0 @@
-import axelrod as axl
-import numpy as np
-
-def main(filename):
-
-    assert axl.__version__ == "2.13.0"
-
-    prefix = "Standard" if "standard" in filename else "Noisy"
-    results = axl.ResultSetFromFile(filename=filename, progress_bar=False)
-    plot = axl.Plot(results)
-    plot.save_all_plots(prefix="assets/{}".format(prefix), progress_bar=False,
-                        title_prefix=prefix, filetype="pdf")
-    results.write_summary("assets/{}_summary.csv".format(prefix))
-
-    # Write the total scores per tournament for each player to "assets/".
-    # This data is a #repetitions (rows) by #players (columns) array with
-    # X_{ij} corresponding to the TOTAL score obtained by player j in repetition
-    # i of the tournament.
-    scores_per_tournament = np.array(results.scores).transpose()
-    np.savetxt(fname="assets/{}_scores.gz".format(prefix),
-               X=scores_per_tournament, delimiter=",")
-
-    # Write the total wins per tournament for each player to "assets/".
-    # This data is a #repetitions (rows) by #players (columns) array with
-    # X_{ij} corresponding to the TOTAL wins obtained by player j in repetition
-    # i of the tournament.
-    wins_per_tournament = np.array(results.wins).transpose()
-    np.savetxt(fname="assets/{}_wins.gz".format(prefix),
-               X=wins_per_tournament, delimiter=",")
-
-    # Write the payoff of each player against every other player to "assets/".
-    # This data is a #players (rows) by #players (rows) array with X_{ij}
-    # corresponding to the mean score of player i against player j
-    payoff_matrix = np.array(results.payoff_matrix)
-    np.savetxt(fname="assets/{}_payoff_matrix.gz".format(prefix),
-               X=payoff_matrix, delimiter=",")
-
-    # Write the stdv payoff of each player against every other player to
-    # "assets/". This data is a #players (rows) by #players (rows) array with
-    # X_{ij} corresponding to the standard deviation of the score of player i
-    # against player j
-    payoff_stdev_matrix = np.array(results.payoff_stddevs)
-    np.savetxt(fname="assets/{}_payoff_stdev_matrix.gz".format(prefix),
-               X=payoff_stdev_matrix, delimiter=",")
-
-
-
-if __name__ == "__main__":
-    import sys
-    filename = sys.argv[1]
-    main(filename)

### 2017-06-23 src/submit_ml_jobs.sh
Add more pbs files.

@@ -18,3 +18,13 @@ qsub pbs_files/ml-8-5-1000.pbs
 qsub pbs_files/ml-8-0-1000.pbs
 qsub pbs_files/ml-9-5-1000.pbs
 qsub pbs_files/ml-9-0-1000.pbs
+qsub pbs_files/ml-10-5-1000.pbs
+qsub pbs_files/ml-10-0-1000.pbs
+qsub pbs_files/ml-11-5-1000.pbs
+qsub pbs_files/ml-11-0-1000.pbs
+qsub pbs_files/ml-12-5-1000.pbs
+qsub pbs_files/ml-12-0-1000.pbs
+qsub pbs_files/ml-13-5-1000.pbs
+qsub pbs_files/ml-13-0-1000.pbs
+qsub pbs_files/ml-14-5-1000.pbs
+qsub pbs_files/ml-14-0-1000.pbs

### 2017-06-23 src/write_pbs_files.py

@@ -3,8 +3,8 @@ Write the pbs file (scheduler files for cluster) and a `./submit_ml_jobs.sh`
 script to submit them.
 """
 min_seed = 0
-max_seed = 10  # The number of jobs is max-min
-repetitions = 1000
+max_seed = 15  # The number of jobs is max-min
+repetitions = 1000  # The total repetitions = max_seed * repetitions
 noises = [0.05, 0]
 
 pbs_filenames = []

### 2017-06-23 src/main.py
Change main.py to write to data dir.

@@ -49,14 +49,14 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
 
 
     # Write summary for each seed
-    results.write_summary("assets/{}_summary.csv".format(prefix))
+    results.write_summary("data/{}_summary.csv".format(prefix))
 
     # Write the total scores per tournament for each player to "assets/".
     # This data is a #repetitions (rows) by #players (columns) array with
     # X_{ij} corresponding to the TOTAL score obtained by player j in repetition
     # i of the tournament.
     scores_per_tournament = np.array(results.scores).transpose()
-    np.savetxt(fname="assets/{}_scores.gz".format(prefix),
+    np.savetxt(fname="data/{}_scores.gz".format(prefix),
                X=scores_per_tournament, delimiter=",")
 
     # Write the total wins per tournament for each player to "assets/".
@@ -64,14 +64,14 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
     # X_{ij} corresponding to the TOTAL wins obtained by player j in repetition
     # i of the tournament.
     wins_per_tournament = np.array(results.wins).transpose()
-    np.savetxt(fname="assets/{}_wins.gz".format(prefix),
+    np.savetxt(fname="data/{}_wins.gz".format(prefix),
                X=wins_per_tournament, delimiter=",")
 
     # Write the payoff of each player against every other player to "assets/".
     # This data is a #players (rows) by #players (rows) array with X_{ij}
     # corresponding to the mean score of player i against player j
     payoff_matrix = np.array(results.payoff_matrix)
-    np.savetxt(fname="assets/{}_payoff_matrix.gz".format(prefix),
+    np.savetxt(fname="data/{}_payoff_matrix.gz".format(prefix),
                X=payoff_matrix, delimiter=",")
 
     # Write the stdv payoff of each player against every other player to
@@ -79,7 +79,7 @@ def main(players=players, processes=None, seed=1, turns=200, repetitions=10000,
     # X_{ij} corresponding to the standard deviation of the score of player i
     # against player j
     payoff_stdev_matrix = np.array(results.payoff_stddevs)
-    np.savetxt(fname="assets/{}_payoff_stdev_matrix.gz".format(prefix),
+    np.savetxt(fname="data/{}_payoff_stdev_matrix.gz".format(prefix),
                X=payoff_stdev_matrix, delimiter=",")
 
 if __name__ == "__main__":

### 2017-06-23 src/submit_ml_jobs.sh
Add more pbs files.

@@ -28,3 +28,23 @@ qsub pbs_files/ml-13-5-1000.pbs
 qsub pbs_files/ml-13-0-1000.pbs
 qsub pbs_files/ml-14-5-1000.pbs
 qsub pbs_files/ml-14-0-1000.pbs
+qsub pbs_files/ml-15-5-1000.pbs
+qsub pbs_files/ml-15-0-1000.pbs
+qsub pbs_files/ml-16-5-1000.pbs
+qsub pbs_files/ml-16-0-1000.pbs
+qsub pbs_files/ml-17-5-1000.pbs
+qsub pbs_files/ml-17-0-1000.pbs
+qsub pbs_files/ml-18-5-1000.pbs
+qsub pbs_files/ml-18-0-1000.pbs
+qsub pbs_files/ml-19-5-1000.pbs
+qsub pbs_files/ml-19-0-1000.pbs
+qsub pbs_files/ml-20-5-1000.pbs
+qsub pbs_files/ml-20-0-1000.pbs
+qsub pbs_files/ml-21-5-1000.pbs
+qsub pbs_files/ml-21-0-1000.pbs
+qsub pbs_files/ml-22-5-1000.pbs
+qsub pbs_files/ml-22-0-1000.pbs
+qsub pbs_files/ml-23-5-1000.pbs
+qsub pbs_files/ml-23-0-1000.pbs
+qsub pbs_files/ml-24-5-1000.pbs
+qsub pbs_files/ml-24-0-1000.pbs

### 2017-06-23 src/write_pbs_files.py

@@ -3,7 +3,7 @@ Write the pbs file (scheduler files for cluster) and a `./submit_ml_jobs.sh`
 script to submit them.
 """
 min_seed = 0
-max_seed = 15  # The number of jobs is max-min
+max_seed = 25  # The number of jobs is max-min
 repetitions = 1000  # The total repetitions = max_seed * repetitions
 noises = [0.05, 0]
 

### 2017-06-23 src/submit_ml_jobs.sh
Submit jobs.

@@ -1,50 +1,50 @@
-qsub pbs_files/ml-0-5-1000.pbs
-qsub pbs_files/ml-0-0-1000.pbs
-qsub pbs_files/ml-1-5-1000.pbs
-qsub pbs_files/ml-1-0-1000.pbs
-qsub pbs_files/ml-2-5-1000.pbs
-qsub pbs_files/ml-2-0-1000.pbs
-qsub pbs_files/ml-3-5-1000.pbs
-qsub pbs_files/ml-3-0-1000.pbs
-qsub pbs_files/ml-4-5-1000.pbs
-qsub pbs_files/ml-4-0-1000.pbs
-qsub pbs_files/ml-5-5-1000.pbs
-qsub pbs_files/ml-5-0-1000.pbs
-qsub pbs_files/ml-6-5-1000.pbs
-qsub pbs_files/ml-6-0-1000.pbs
-qsub pbs_files/ml-7-5-1000.pbs
-qsub pbs_files/ml-7-0-1000.pbs
-qsub pbs_files/ml-8-5-1000.pbs
-qsub pbs_files/ml-8-0-1000.pbs
-qsub pbs_files/ml-9-5-1000.pbs
-qsub pbs_files/ml-9-0-1000.pbs
-qsub pbs_files/ml-10-5-1000.pbs
-qsub pbs_files/ml-10-0-1000.pbs
-qsub pbs_files/ml-11-5-1000.pbs
-qsub pbs_files/ml-11-0-1000.pbs
-qsub pbs_files/ml-12-5-1000.pbs
-qsub pbs_files/ml-12-0-1000.pbs
-qsub pbs_files/ml-13-5-1000.pbs
-qsub pbs_files/ml-13-0-1000.pbs
-qsub pbs_files/ml-14-5-1000.pbs
-qsub pbs_files/ml-14-0-1000.pbs
-qsub pbs_files/ml-15-5-1000.pbs
-qsub pbs_files/ml-15-0-1000.pbs
-qsub pbs_files/ml-16-5-1000.pbs
-qsub pbs_files/ml-16-0-1000.pbs
-qsub pbs_files/ml-17-5-1000.pbs
-qsub pbs_files/ml-17-0-1000.pbs
-qsub pbs_files/ml-18-5-1000.pbs
-qsub pbs_files/ml-18-0-1000.pbs
-qsub pbs_files/ml-19-5-1000.pbs
[…]

### 2017-06-23 src/submit_ml_jobs.sh
Submit more jobs.

@@ -45,6 +45,6 @@
 #qsub pbs_files/ml-22-5-1000.pbs
 #qsub pbs_files/ml-22-0-1000.pbs
 #qsub pbs_files/ml-23-5-1000.pbs
-qsub pbs_files/ml-23-0-1000.pbs
-qsub pbs_files/ml-24-5-1000.pbs
+#qsub pbs_files/ml-23-0-1000.pbs
+#qsub pbs_files/ml-24-5-1000.pbs
 qsub pbs_files/ml-24-0-1000.pbs

### 2017-07-04 src/submit_ml_jobs.sh
Add more jobs.

@@ -48,3 +48,53 @@
 #qsub pbs_files/ml-23-0-1000.pbs
 #qsub pbs_files/ml-24-5-1000.pbs
 qsub pbs_files/ml-24-0-1000.pbs
+qsub pbs_files/ml-25-5-1000.pbs
+qsub pbs_files/ml-25-0-1000.pbs
+qsub pbs_files/ml-26-5-1000.pbs
+qsub pbs_files/ml-26-0-1000.pbs
+qsub pbs_files/ml-27-5-1000.pbs
+qsub pbs_files/ml-27-0-1000.pbs
+qsub pbs_files/ml-28-5-1000.pbs
+qsub pbs_files/ml-28-0-1000.pbs
+qsub pbs_files/ml-29-5-1000.pbs
+qsub pbs_files/ml-29-0-1000.pbs
+qsub pbs_files/ml-30-5-1000.pbs
+qsub pbs_files/ml-30-0-1000.pbs
+qsub pbs_files/ml-31-5-1000.pbs
+qsub pbs_files/ml-31-0-1000.pbs
+qsub pbs_files/ml-32-5-1000.pbs
+qsub pbs_files/ml-32-0-1000.pbs
+qsub pbs_files/ml-33-5-1000.pbs
+qsub pbs_files/ml-33-0-1000.pbs
+qsub pbs_files/ml-34-5-1000.pbs
+qsub pbs_files/ml-34-0-1000.pbs
+qsub pbs_files/ml-35-5-1000.pbs
+qsub pbs_files/ml-35-0-1000.pbs
+qsub pbs_files/ml-36-5-1000.pbs
+qsub pbs_files/ml-36-0-1000.pbs
+qsub pbs_files/ml-37-5-1000.pbs
+qsub pbs_files/ml-37-0-1000.pbs
+qsub pbs_files/ml-38-5-1000.pbs
+qsub pbs_files/ml-38-0-1000.pbs
+qsub pbs_files/ml-39-5-1000.pbs
+qsub pbs_files/ml-39-0-1000.pbs
+qsub pbs_files/ml-40-5-1000.pbs
+qsub pbs_files/ml-40-0-1000.pbs
+qsub pbs_files/ml-41-5-1000.pbs
+qsub pbs_files/ml-41-0-1000.pbs
+qsub pbs_files/ml-42-5-1000.pbs
+qsub pbs_files/ml-42-0-1000.pbs
[…]

### 2017-07-04 src/write_pbs_files.py

@@ -3,7 +3,7 @@ Write the pbs file (scheduler files for cluster) and a `./submit_ml_jobs.sh`
 script to submit them.
 """
 min_seed = 0
-max_seed = 25  # The number of jobs is max-min
+max_seed = 50  # The number of jobs is max-min
 repetitions = 1000  # The total repetitions = max_seed * repetitions
 noises = [0.05, 0]
 

### 2017-07-04 main.tex
Add plots and tables for 15k reps.
All automatically generated from src/main.ipynb.

Includes more detailed summary tables.

Also removing unneeded plots. Everything is in assets.

@@
 
-We conducted a tournament with all strategies in the Axelrod library. The top
-11 performing strategies by mean payoff are all strategies trained to maximize
-total payoff against a subset of the strategies (Table \ref{tbl:standard_score}).
+We conducted a tournament with all strategies in the Axelrod library, including
+some parametrized strategies. These are listed in
+Appendix~\ref{app:list_of_players}.
+% TODO Add list of players
+The top
+11 performing strategies by median payoff are all strategies trained to maximize
+% TODO Potentially modify this as more repetitions are analysed.
+total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
 The next strategy is
-Desired Belief Strategy (DBS) which actively analyzes the opponent and responds
+Desired Belief Strategy (DBS)
+% TODO Add reference for DBS
+which actively analyzes the opponent and responds
 accordingly. The next two strategies are Winner12, based on a lookup table,
-Omega TFT, and Fool Me Once, a grudging strategy that defects indefinitely on
-the second defection. All strategies in the tournament follow a simple set of
+Fool Me Once, a grudging strategy that defects indefinitely on
+the second defection and Omega Tit For Tat.
+% TODO Add a reference for Omega TfT
+All strategies in the tournament follow a simple set of
 rules in accordance with earlier tournaments:
+
 \begin{itemize}
+  \item Players are unaware of the number of turns in a match
   \item Players carry no acquired state between matches
@@
 
-Pairwise payoff results are given as a heatmap (Figure ) which
-shows that many strategies achieve mutual cooperation with each other and
+% Table of best strategies
+\begin{table}[!hbtp]
+    \centering
+        \input{./assets/standard_top_15_scores_summary.tex}
+        \caption{Standard Tournament: Top Ranking Strategies by median score
+        (50th percentile) in 15,000 Tournaments}
+        % TODO Update caption as more repetitions are carried out
+        % TODO Potentially remove count from table (including it for now so as
+        % to avoid confusion.
+        \label{tbl:standard_score}
+\end{table}
+
+Violin plots showing the distribution of the scores of each strategy (again
+ranked by median score) are shown in Figure~\ref{fig:standard_boxplot}.
+
+\begin{landscape}
+    \begin{figure}[!hbtp]
+        \includegraphics[width=\paperwidth]{./assets/standard_scores_boxplots.pdf}
+        \caption{Ranking by median score for the Standard Tournament}
+        \label{fig:standard_boxplot}
+    \end{figure}
+\end{landscape}
+
+Pairwise payoff results are given as a heatmap (Figure~\ref{fig:standard_heatmap})
+which shows that many strategies achieve mutual cooperation with each other and
 that the top performing strategies never defect first but are able to exploit
 weaker strategies that attempt to defect.
+
+\begin{figure}[!hbtp]
+    \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
+    \caption{Pairwise Match results for the Standard Tournament}
+    \label{fig:standard_heatmap}
+\end{figure}
 
@@
 strategies that were the result of training to maximize Moran process fixation.
-No strategies were trained specifically to win matches. None of the top scoring
+No strategies were trained specifically to win matches.
+None of the top scoring
 strategies appear in the top 20 list of strategies ranked by match wins.
+This can be seen in Figure~\ref{fig:standard_winplot} where the distribution of
+the number of wins of each strategy is shown.
 
-% Table of best strategies
+\begin{landscape}
+    \begin{figure}[!hbtp]
+        \centering
+        \includegraphics[width=\textwidth]{./assets/standard_wins_boxplots.pdf}
+        \caption{Ranking by Total wins for the Standard Tournament}
+        \label{fig:standard_winplot}
+    \end{figure}
+\end{landscape}
+
+The number of wins of the top strategies of Table~\ref{tbl:standard_wins} are
+shown in Table~\ref{tbl:standard_wins}. It is evident that although these
+strategies score highly they do not win many matches: the strategy with the most
+number of wins is the Evolved FSM 16 strategy that at most won 60
+(\(60/175\approx34\%\)) matches in a given tournament.
+% TODO Update this when more data comes in.
+
 \begin{table}[!hbtp]
     \centering
-        \input{./tex/standard_scores.tex}
-        \caption{Standard Tournament: Top Ranking Strategies by Median Score in 15,000 Tournaments}
-        \label{tbl:standard_score}
+        \input{./assets/standard_top_15_wins_summary.tex}
+        \caption{Standard Tournament: Number of wins of Top Ranking Strategies
+        by median score (50th percentile) in 15,000 Tournaments}
+        % TODO Update caption as more repetitions are carried out
+        % TODO Potentially remove count from table (including it for now so as
+        % to avoid confusion.
+        \label{tbl:standard_wins}
+\end{table}
+
+Finally, Table~\ref{tbl:standard_ranks} and
+Figure~\ref{fig:standard_ranks_boxplot} show the ranks (based on median score)
+of each strategy over the repeated tournaments. Whilst there is some
+stochasticity, the top three strategies almost always rank in the top three. For
+example, the worst that the Evolved Lookerup 2 2 2 ranks in a given tournament
+is 7th.
+
+\begin{table}[!hbtp]
+    \centering
+        \input{./assets/standard_top_15_ranks_summary.tex}
+        \caption{Standard Tournament: Ranks of Top Ranking Strategies
+        by median score (50th percentile) in 15,000 Tournaments}
+        % TODO Update caption as more repetitions are carried out
+        % TODO Potentially remove count from table (including it for now so as
+        % to avoid confusion.
+        \label{tbl:standard_ranks}
 \end{table}
@@
     \begin{figure}[!hbtp]
-        \includegraphics[width=\paperwidth]{plots/Standard_boxplot.pdf}
-        \caption{Ranking by Median Payoff for the Standard Tournament}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/standard_ranks_boxplots.pdf}
+        \caption{Rankings over each repeated tournament}
+        \label{fig:standard_ranks_boxplot}
     \end{figure}
@@
 
-\begin{landscape}
-    \begin{figure}[!hbtp]
-        \includegraphics[width=\paperwidth]{plots/Standard_winplot.pdf}
-        \caption{Ranking by Total wins for the Standard Tournament}
-    \end{figure}
-\end{landscape}
-
-\begin{figure}[!hbtp]
-    \includegraphics[width=\paperwidth]{plots/Standard_payoff.pdf}
-    \caption{Pairwise Match results for the Standard Tournament}
-\end{figure}
-
 Using the method of fingerprinting described in \cite{ashlock2008fingerprinting}
+% TODO This is actually a numerical approximation of the fingerprinting
+% described in ashlock's paper. There they consider a fingerprint to be an
+% analytic function.
 \cite{ashlock2009fingerprint}, we can compare

### 2017-07-04 main.tex
Update section on Noisy tournaments.

@@
         \centering
-        \includegraphics[width=\textwidth]{./plots/EvolvedLookerUp2_2_2.png}
+        \includegraphics[width=\textwidth]{./assets/EvolvedLookerUp2_2_2.png}
         \caption{Fingerprint for EvolvedLookerUp\_2\_2\_2}
@@
         \centering
-        \includegraphics[width=\textwidth]{./plots/Evolved_HMM_5.png}
+        \includegraphics[width=\textwidth]{./assets/Evolved_HMM_5.png}
         \caption{Fingerprint for Evolved\_HMM\_5}
@@
         \centering
-        \includegraphics[width=\textwidth]{./plots/Evolved_FSM_16.png}
+        \includegraphics[width=\textwidth]{./assets/Evolved_FSM_16.png}
         \caption{Fingerprint for Evolved\_FSM\_16}
@@
 
-We also ran noisy tournaments in which there is a 10\% chance that an action
-is flipped. The best performing strategies in mean payoff are DBS, designed
-to correct for noise, followed by two strategies trained
-in the presence of noise, Spiteful TFT (TFT but defects indefinitely if the
-opponent defects twice consecutively), two strategies trained without noise, then
-OmegaTFT (also designed to handle noise).
-
-The strategies trained in the presence of noise are also among the best performers
-in the absence of noise. The cluster of mutually cooperative strategies is
-broken by the noise at 5\%. A similar collection of players excels at winning
-matches but again they have a poor total payoff.
-
-The strategies tallying the most wins are somewhat similar, with Defector, the
-handshaking CollectiveStrategy, and Aggravate appearing as the top three again,
-followed by Spiteful TFT and strategies designed to be retaliatory. Players ranked
-12, 13, and 15 (TF3, Fool Me Once, and Evolved ANN 5) all appear in the top 15
-strategies by score, indicating that noise breaks the asymmetry between wins
-and scores to some extent.
+We also ran noisy tournaments in which there is a 5\% chance that an action is
+flipped. As shown in Table~\ref{tbl:noisy_score} and
+Figure~\ref{fig:noisy_score}, the best performing strategies in median payoff
+are DBS, designed to correct for noise, followed by two strategies trained in
+the presence of noise and three trained strategies trained without noise. One of
+the strategies trained with noise (PSO Gambler) actually performs less well than
+some of the other high ranking strategies including
+Spiteful TFT (TFT but defects indefinitely if the opponent defects twice
+consecutively) and OmegaTFT (also
+designed to handle noise).
 
 % Table of best strategies
-
 \begin{table}[!hbtp]
     \centering
-        \input{./tex/noisy_scores.tex}
+        \input{./assets/noisy_top_15_scores_summary.tex}
         \caption{Noisy Tournament: Top Ranking Strategies by Median Score in a
-        15000 Tournaments with 10\% noise}
+        15000 Tournaments with 5\% noise}
         \label{tbl:noisy_score}
@@
     \begin{figure}[!hbtp]
-        \includegraphics[width=\paperwidth]{plots/Noisy_boxplot.pdf}
+        \includegraphics[width=\paperwidth]{./assets/noisy_scores_boxplots.pdf}
         \caption{Ranking by Median Payoff for the Noisy Tournament}
+        \label{fig:noisy_score}
     \end{figure}
@@
 
+The strategies trained in the presence of noise are also among the best
+performers in the absence of noise. As shown in Figure~\ref{fig:noisy_heatmap}
+the cluster of mutually cooperative strategies is broken by the noise at 5\%. A
+similar collection of players excels at winning matches but again they have a
+poor total payoff.
+
+\begin{figure}[!hbtp]
+    \includegraphics[width=\textwidth]{./assets/noisy_scores_heatmap.pdf}
+    \caption{Pairwise Match results for the Noisy Tournament}
+    \label{fig:noisy_heatmap}
+\end{figure}
+
+As shown in Figure~\ref{fig:noisy_winplot} the strategies tallying the most wins
+are somewhat similar, with Defector, the handshaking CollectiveStrategy, and
+Aggravate appearing as the top three again.
+
 \begin{landscape}
     \begin{figure}[!hbtp]
-        \includegraphics[width=\paperwidth]{plots/Noisy_winplot.pdf}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/noisy_wins_boxplots.pdf}
         \caption{Ranking by Total wins for the Noisy Tournament}
+        \label{fig:noisy_winplot}
     \end{figure}
@@
 
+As shown in Table~\ref{tbl:noisy_wins}, the top ranking strategies win a larger
+number of matches in the presence of noise. For example Spiteful Tit For Tat in
+one tournament won almost all it's matches (167).
+
+\begin{table}[!hbtp]
+    \centering
+        \input{./assets/noisy_top_15_wins_summary.tex}
+        \caption{Noisy Tournament: Number of wins of Top Ranking Strategies
+        by median score (50th percentile) in 15,000 Tournaments}
+        % TODO Update caption as more repetitions are carried out
+        % TODO Potentially remove count from table (including it for now so as
+        % to avoid confusion.
+        \label{tbl:noisy_wins}
+\end{table}
+
+Finally, Table~\ref{tbl:noisy_ranks} and
+Figure~\ref{fig:noisy_ranks_boxplot} show the ranks (based on median score)
+of each strategy over the repeated tournaments. We see, that the stochasticity
+of the ranks understandably increases the DBS strategy never ranks lower than
+third and wins 75\% of the time. The two strategies trained for noisy
+tournaments rank in the top three 95\% of the time.
+% TODO Possibly update this with more data.
+
+\begin{table}[!hbtp]
+    \centering
+        \input{./assets/noisy_top_15_ranks_summary.tex}
+        \caption{Noisy Tournament: Ranks of Top Ranking Strategies
+        by median score (50th percentile) in 15,000 Tournaments}
+        % TODO Update caption as more repetitions are carried out
+        % TODO Potentially remove count from table (including it for now so as
+        % to avoid confusion.
+        \label{tbl:noisy_ranks}
+\end{table}
+
+\begin{landscape}
     \begin{figure}[!hbtp]
-    \includegraphics[width=\paperwidth]{plots/Noisy_payoff.pdf}
-    \caption{Pairwise Match results for the Noisy Tournament}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/noisy_ranks_boxplots.pdf}
+        \caption{Rankings over each repeated tournament}
+        \label{fig:noisy_ranks_boxplot}
     \end{figure}
+\end{landscape}
 
@@
         \centering
-        \includegraphics[width=\textwidth]{./plots/DBS.png}
+        \includegraphics[width=\textwidth]{./assets/DBS.png}
         \caption{Fingerprint for DBS}
@@
         \centering
-        \includegraphics[width=\textwidth]{./plots/Evolved_ANN_5_Noise_05.png}
+        \includegraphics[width=\textwidth]{./assets/Evolved_ANN_5_Noise_05.png}
         \caption{Fingerprint for Evolved\_ANN\_5\_Noise\_05}
@@
         \centering
-        \includegraphics[width=\textwidth]{./plots/Evolved_FSM_16_Noise_05.png}
+        \includegraphics[width=\textwidth]{./assets/Evolved_FSM_16_Noise_05.png}
         \caption{Fingerprint for Evolved\_FSM\_16\_Noise\_05}
@@
 opponents. A simple evolutionary algorithm produces strategies based on multiple
-standard machine learning techniques that are able to achieve a higher mean
+standard machine learning techniques that are able to achieve a higher median
 score than any other known opponent in a standard tournament. Most of the trained
@@
 
-Of the strategies trained to maximize their mean score all are generally
+Of the strategies trained to maximize their median score all are generally
 cooperative, not defecting until the opponent defects. Maximizing for individual

### 2017-07-04 main.tex
Tidy up captions.
Also remove count from tables and automatically generate these from nb.

@@
         \input{./assets/standard_top_15_scores_summary.tex}
-        \caption{Standard Tournament: Top Ranking Strategies by median score
-        (50th percentile) in 15,000 Tournaments}
-        % TODO Update caption as more repetitions are carried out
-        % TODO Potentially remove count from table (including it for now so as
-        % to avoid confusion.
+        \caption{Standard Tournament: Mean score per turn of top 15 strategies
+            (ranked by median over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{tbl:standard_score}
@@
         \includegraphics[width=\paperwidth]{./assets/standard_scores_boxplots.pdf}
-        \caption{Ranking by median score for the Standard Tournament}
+        \caption{Standard Tournament: Mean score per turn (ranked by median
+        over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{fig:standard_boxplot}
@@
     \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
-    \caption{Pairwise Match results for the Standard Tournament}
+    \caption{Standard Tournament: Mean score per turn of row players against
+    column players (ordered by median over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
     \label{fig:standard_heatmap}
@@
         \includegraphics[width=\textwidth]{./assets/standard_wins_boxplots.pdf}
-        \caption{Ranking by Total wins for the Standard Tournament}
+        \caption{Standard Tournament: number of wins per tournament (ordered by
+        median over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{fig:standard_winplot}
@@
         \input{./assets/standard_top_15_wins_summary.tex}
-        \caption{Standard Tournament: Number of wins of Top Ranking Strategies
-        by median score (50th percentile) in 15,000 Tournaments}
-        % TODO Update caption as more repetitions are carried out
-        % TODO Potentially remove count from table (including it for now so as
-        % to avoid confusion.
+        \caption{Standard Tournament: Number of wins per tournament
+        of top 15 strategies (ranked by median score over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{tbl:standard_wins}
@@
         \input{./assets/standard_top_15_ranks_summary.tex}
-        \caption{Standard Tournament: Ranks of Top Ranking Strategies
-        by median score (50th percentile) in 15,000 Tournaments}
-        % TODO Update caption as more repetitions are carried out
-        % TODO Potentially remove count from table (including it for now so as
-        % to avoid confusion.
+        \caption{Standard Tournament: Rank in each tournament
+        of top 15 strategies (ranked by median over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{tbl:standard_ranks}
@@
         \includegraphics[width=\textwidth]{./assets/standard_ranks_boxplots.pdf}
-        \caption{Rankings over each repeated tournament}
+        \caption{Standard Tournament: rank in each tournament (ordered by
+        median over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{fig:standard_ranks_boxplot}
@@
         \input{./assets/noisy_top_15_scores_summary.tex}
-        \caption{Noisy Tournament: Top Ranking Strategies by Median Score in a
-        15000 Tournaments with 5\% noise}
+        \caption{Noisy (5\%) Tournament: Mean score per turn of top 15 strategies
+        (ranked by median over
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{tbl:noisy_score}
@@
         \includegraphics[width=\paperwidth]{./assets/noisy_scores_boxplots.pdf}
-        \caption{Ranking by Median Payoff for the Noisy Tournament}
+        \caption{Noisy (5\%) Tournament: Mean score per turn (ranked by median
+        over
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{fig:noisy_score}
@@
     \includegraphics[width=\textwidth]{./assets/noisy_scores_heatmap.pdf}
-    \caption{Pairwise Match results for the Noisy Tournament}
+    \caption{Noisy (5\%) Tournament: Mean score per turn of row players against
+    column players (ordered by median over
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
     \label{fig:noisy_heatmap}
@@
         \includegraphics[width=\textwidth]{./assets/noisy_wins_boxplots.pdf}
-        \caption{Ranking by Total wins for the Noisy Tournament}
+        \caption{Noisy (5\%) Tournament: number of wins per tournament (ordered by
+        median over
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{fig:noisy_winplot}
@@
         \input{./assets/noisy_top_15_wins_summary.tex}
-        \caption{Noisy Tournament: Number of wins of Top Ranking Strategies
-        by median score (50th percentile) in 15,000 Tournaments}
-        % TODO Update caption as more repetitions are carried out
-        % TODO Potentially remove count from table (including it for now so as
-        % to avoid confusion.
+        \caption{Noisy (5\%) Tournament: Number of wins per tournament
+        of top 15 strategies (ranked by median score over
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{tbl:noisy_wins}
@@
         \input{./assets/noisy_top_15_ranks_summary.tex}
-        \caption{Noisy Tournament: Ranks of Top Ranking Strategies
-        by median score (50th percentile) in 15,000 Tournaments}
-        % TODO Update caption as more repetitions are carried out
-        % TODO Potentially remove count from table (including it for now so as
-        % to avoid confusion.
+        \caption{Noisy (5\%) Tournament: Rank in each tournament
+        of top 15 strategies (ranked by median over
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{tbl:noisy_ranks}
@@
         \includegraphics[width=\textwidth]{./assets/noisy_ranks_boxplots.pdf}
-        \caption{Rankings over each repeated tournament}
+        \caption{Noisy (5\%) Tournament: rank in each tournament (ordered by
+        median over
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{fig:noisy_ranks_boxplot}

### 2017-07-04 src/submit_ml_jobs.sh
Submit more jobs

@@ -47,26 +47,26 @@
 #qsub pbs_files/ml-23-5-1000.pbs
 #qsub pbs_files/ml-23-0-1000.pbs
 #qsub pbs_files/ml-24-5-1000.pbs
-qsub pbs_files/ml-24-0-1000.pbs
-qsub pbs_files/ml-25-5-1000.pbs
-qsub pbs_files/ml-25-0-1000.pbs
-qsub pbs_files/ml-26-5-1000.pbs
-qsub pbs_files/ml-26-0-1000.pbs
-qsub pbs_files/ml-27-5-1000.pbs
-qsub pbs_files/ml-27-0-1000.pbs
-qsub pbs_files/ml-28-5-1000.pbs
-qsub pbs_files/ml-28-0-1000.pbs
-qsub pbs_files/ml-29-5-1000.pbs
-qsub pbs_files/ml-29-0-1000.pbs
-qsub pbs_files/ml-30-5-1000.pbs
-qsub pbs_files/ml-30-0-1000.pbs
-qsub pbs_files/ml-31-5-1000.pbs
-qsub pbs_files/ml-31-0-1000.pbs
-qsub pbs_files/ml-32-5-1000.pbs
-qsub pbs_files/ml-32-0-1000.pbs
-qsub pbs_files/ml-33-5-1000.pbs
-qsub pbs_files/ml-33-0-1000.pbs
-qsub pbs_files/ml-34-5-1000.pbs
+#qsub pbs_files/ml-24-0-1000.pbs
+#qsub pbs_files/ml-25-5-1000.pbs
+#qsub pbs_files/ml-25-0-1000.pbs
+#qsub pbs_files/ml-26-5-1000.pbs
+#qsub pbs_files/ml-26-0-1000.pbs
+#qsub pbs_files/ml-27-5-1000.pbs
+#qsub pbs_files/ml-27-0-1000.pbs
+#qsub pbs_files/ml-28-5-1000.pbs
+#qsub pbs_files/ml-28-0-1000.pbs
+#qsub pbs_files/ml-29-5-1000.pbs
+#qsub pbs_files/ml-29-0-1000.pbs
+#qsub pbs_files/ml-30-5-1000.pbs
+#qsub pbs_files/ml-30-0-1000.pbs
+#qsub pbs_files/ml-31-5-1000.pbs
+#qsub pbs_files/ml-31-0-1000.pbs
[…]

### 2017-07-05 src/submit_ml_jobs.sh
Submit more jobs.

@@ -67,21 +67,21 @@
 #qsub pbs_files/ml-33-5-1000.pbs
 #qsub pbs_files/ml-33-0-1000.pbs
 #qsub pbs_files/ml-34-5-1000.pbs
-qsub pbs_files/ml-34-0-1000.pbs
-qsub pbs_files/ml-35-5-1000.pbs
-qsub pbs_files/ml-35-0-1000.pbs
-qsub pbs_files/ml-36-5-1000.pbs
-qsub pbs_files/ml-36-0-1000.pbs
-qsub pbs_files/ml-37-5-1000.pbs
-qsub pbs_files/ml-37-0-1000.pbs
-qsub pbs_files/ml-38-5-1000.pbs
-qsub pbs_files/ml-38-0-1000.pbs
-qsub pbs_files/ml-39-5-1000.pbs
-qsub pbs_files/ml-39-0-1000.pbs
-qsub pbs_files/ml-40-5-1000.pbs
-qsub pbs_files/ml-40-0-1000.pbs
-qsub pbs_files/ml-41-5-1000.pbs
-qsub pbs_files/ml-41-0-1000.pbs
+#qsub pbs_files/ml-34-0-1000.pbs
+#qsub pbs_files/ml-35-5-1000.pbs
+#qsub pbs_files/ml-35-0-1000.pbs
+#qsub pbs_files/ml-36-5-1000.pbs
+#qsub pbs_files/ml-36-0-1000.pbs
+#qsub pbs_files/ml-37-5-1000.pbs
+#qsub pbs_files/ml-37-0-1000.pbs
+#qsub pbs_files/ml-38-5-1000.pbs
+#qsub pbs_files/ml-38-0-1000.pbs
+#qsub pbs_files/ml-39-5-1000.pbs
+#qsub pbs_files/ml-39-0-1000.pbs
+#qsub pbs_files/ml-40-5-1000.pbs
+#qsub pbs_files/ml-40-0-1000.pbs
+#qsub pbs_files/ml-41-5-1000.pbs
+#qsub pbs_files/ml-41-0-1000.pbs
 qsub pbs_files/ml-42-5-1000.pbs
 qsub pbs_files/ml-42-0-1000.pbs
 qsub pbs_files/ml-43-5-1000.pbs

### 2017-07-05 main.tex
Run analysis with 25k repetitions.
Some minor esthetic improvements.
- Increase the font size of labels
- Increase the height for landscape images.
- Rearrange group citations
- Fix probabilistic notation

@@
 There are several previous publications that use evolutionary algorithms to
-evolve IPD strategies in various circumstances \cite{marks1989niche} \cite{fogel1993evolving} \cite{ashlock2006training}
-\cite{ashlock2006changes} \cite{vassiliades2010multiagent} \cite{ashlock2014shaped}
-\cite{ashlock2014evolution} \cite{ashlock2015multiple} \cite{barlow2015varying}
-\cite{sudo2015effects}. See also \cite{gaudesi2016exploiting} for a strategy
-trained to win against a collection of well-known IPD opponents and see
+evolve IPD strategies in various circumstances
+\cite{ashlock2006training, ashlock2015multiple, ashlock2006changes,
+      ashlock2014shaped, ashlock2014evolution, barlow2015varying,
+      fogel1993evolving, marks1989niche, sudo2015effects,
+      vassiliades2010multiagent}. See also \cite{gaudesi2016exploiting} for a
+strategy trained to win against a collection of well-known IPD opponents and see
 \cite{franken2005particle} for a prior use of particle swarm algorithms. Our
@@
 
-The Axelrod library now contains many strategies based on machine learning
+The Axelrod library now contains many parametrised strategies trained using
+machine learning
 methods. Most are deterministic, use many rounds of memory, and perform
 extremely well in tournaments.
+
+The various archetypes will be described in the following sections.
 
@@
 training was obtained for $n_1 = m_1 = m_2 = 2$ and generally for $n_1 > 0$.
-First impressions matter in the IPD. The library includes a strategy
+First impressions matter in the IPD\@. The library includes a strategy
 called EvolvedLookerUp2\_2\_2 which is among the top strategies in the library.
@@
 memory one strategy was trained and is called PSO Gambler Mem 1, with
-probabilities $(\text{Pr(C|CC)}, \text{Pr(C|CD)}, \text{Pr(C|DC)}, \text{Pr(C|DD)}) = (1, 0.5217, 0, 0.121)$. Though it performs well in deterministic tournaments
+probabilities $(\text{Pr}(\text{C}\;|\;\text{CC}),
+                \text{Pr}(\text{C}\;|\;\text{CD}),
+                \text{Pr}(\text{C}\;|\;\text{DC}),
+                \text{Pr}(\text{C}\;|\;\text{DD})) = (1, 0.5217, 0, 0.121)$.
+Though it performs well in standard tournaments (see
+Table~\ref{tbl:standard_score})
 it is not as good as the longer memory strategies, and is bested by a similar
-strategy that also uses the first round of play.
+strategy that also uses the first round of play: PSO Gamble 1 1 1.
 
@@
     \begin{figure}[!hbtp]
+        \centering
         \includegraphics[width=\paperwidth]{./assets/standard_scores_boxplots.pdf}
@@
 \begin{figure}[!hbtp]
+    \centering
     \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
     \caption{Standard Tournament: Mean score per turn of row players against
-    column players (ordered by median over
+    column players (ranked by median over
         \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/standard_wins_boxplots.pdf}
-        \caption{Standard Tournament: number of wins per tournament (ordered by
+        \includegraphics[width=\paperwidth]{./assets/standard_wins_boxplots.pdf}
+        \caption{Standard Tournament: number of wins per tournament (ranked by
         median over
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/standard_ranks_boxplots.pdf}
-        \caption{Standard Tournament: rank in each tournament (ordered by
+        \includegraphics[width=\paperwidth]{./assets/standard_ranks_boxplots.pdf}
+        \caption{Standard Tournament: rank in each tournament (ranked by
         median over
@@
     \begin{figure}[!hbtp]
+        \centering
         \includegraphics[width=\paperwidth]{./assets/noisy_scores_boxplots.pdf}
@@
 \begin{figure}[!hbtp]
+    \centering
     \includegraphics[width=\textwidth]{./assets/noisy_scores_heatmap.pdf}
     \caption{Noisy (5\%) Tournament: Mean score per turn of row players against
-    column players (ordered by median over
+    column players (ranked by median over
         \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/noisy_wins_boxplots.pdf}
-        \caption{Noisy (5\%) Tournament: number of wins per tournament (ordered by
+        \includegraphics[width=\paperwidth]{./assets/noisy_wins_boxplots.pdf}
+        \caption{Noisy (5\%) Tournament: number of wins per tournament (ranked by
         median over
@@
 of the ranks understandably increases the DBS strategy never ranks lower than
-third and wins 75\% of the time. The two strategies trained for noisy
+second and wins 75\% of the time. The two strategies trained for noisy
 tournaments rank in the top three 95\% of the time.
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/noisy_ranks_boxplots.pdf}
-        \caption{Noisy (5\%) Tournament: rank in each tournament (ordered by
+        \includegraphics[width=\paperwidth]{./assets/noisy_ranks_boxplots.pdf}
+        \caption{Noisy (5\%) Tournament: rank in each tournament (ranked by
         median over

### 2017-07-05 assets/list_of_players.tex
Write list of players.

\item $\phi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item $\pi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item $e$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item ALLCorALLD - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
\item Adaptive - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
\item Adaptive Pavlov 2006 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
\item Adaptive Pavlov 2011 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
\item Adaptive Tit For Tat: 0.5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Tzafestas2000}
\item Aggravater - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Alternator - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1984, Mittal2009}
\item Alternator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Anti Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Hilbe2013}
\item AntiCycler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Appeaser - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Arrogant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Better and Better - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Bully - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Nachbar1992}
\item Calculator - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Cautious QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item CollectiveStrategy (\textbf{CS}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2009}
\item Contrite Tit For Tat (\textbf{CTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1995}
\item Cooperator - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
\item Cooperator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Cycler CCCCCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
\item Cycler CCCD - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{axelrodproject}
\item Cycler CCCDCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
\item Cycler CCD - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
\item Cycler DC - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{axelrodproject}
\item Cycler DDC - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
\item DBS: 0.75, 3, 4, 3, 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Au2006}
\item Davis: 10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
\item Defector - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
\item Defector Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Desperate - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
\item DoubleResurrection - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{Eckhart2015}
\item Doubler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Dynamic Two Tits For Tat - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{axelrodproject}
\item EasyGo - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011, Prison1998}
\item Eatherley - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
\item Eventual Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Evolved ANN - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Evolved ANN 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Evolved ANN 5 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16. \cite{axelrodproject}
\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16. \cite{axelrodproject}
\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{axelrodproject}
\item Evolved HMM 5 - \textit{Stochastic} - \textit{Memory depth}: 5. \cite{axelrodproject}
\item EvolvedLookerUp1\_1\_1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item EvolvedLookerUp2\_2\_2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Feld: 1.0, 0.5, 200 - \textit{Stochastic} - \textit{Memory depth}: 200. \cite{Axelrod1980}
\item Firm But Fair - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Frean1994}
\item Fool Me Forever - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Fool Me Once - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Forgetful Fool Me Once: 0.05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Forgetful Grudger - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
\item Forgiver - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Forgiving Tit For Tat (\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2006b}
\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{Ashlock2006b}
\item GTFT: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1.
\item GTFT: 0.3 - \textit{Stochastic} - \textit{Memory depth}: 1.
\item GTFT: 0.33 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Gaudesi2016, Nowak1993}
\item GTFT: 0.7 - \textit{Stochastic} - \textit{Memory depth}: 1.
\item GTFT: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1.
\item General Soft Grudger: n=1,d=4,c=2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Gradual - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Beaufils1997}
\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C') - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Grofman - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
\item Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980, Banks1990, Beaufils1997, Berg2015, Li2011}
\item GrudgerAlternator - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Grumpy: Nice, 10, -10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Handshake - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Robson1990}
\item Hard Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Mittal2009}
\item Hard Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
\item Hard Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
\item Hard Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
\item Hard Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
\item Hard Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Hard Tit For 2 Tats (\textbf{HTf2T}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Stewart2012}
\item Hard Tit For Tat (\textbf{HTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{PD2017}
\item Hesitant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Hopeless - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
\item Inverse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Inverse Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Axelrod1980, Stewart2012}
\item Level Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Eckhart2015}
\item Limited Retaliate 2: 0.08, 15 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Limited Retaliate 3: 0.05, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Limited Retaliate: 0.1, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item MEM2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2014}
\item Math Constant Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Meta Hunter Aggressive: 7 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Meta Hunter: 6 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Meta Mixer: 173 players - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Naive Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Li2011}
\item Negation - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{PD2017}
\item Nice Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Nydegger - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1980}
\item Omega TFT: 3, 8 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
\item Once Bitten - \textit{Deterministic} - \textit{Memory depth}: 12. \cite{axelrodproject}
\item Opposite Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item PSO Gambler 1\_1\_1 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item PSO Gambler 2\_2\_2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item PSO Gambler 2\_2\_2 Noise 05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9. \cite{Ashlock2006b}
\item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
\item Prober 2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Prober 3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Prober 4 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2006}
\item Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2014}
\item Random Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Random: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 0.
\item Random: 0.3 - \textit{Stochastic} - \textit{Memory depth}: 0.
\item Random: 0.5 - \textit{Stochastic} - \textit{Memory depth}: 0. \cite{Axelrod1980, Tzafestas2000}
\item Random: 0.7 - \textit{Stochastic} - \textit{Memory depth}: 0.
\item Random: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 0.
\item Remorseful Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{Li2011}
\item Resurrection - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{Eckhart2015}
\item Retaliate 2: 0.08 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Retaliate 3: 0.05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Retaliate: 0.1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Revised Downing: True - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2008}
\item Risky QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item SelfSteem - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
\item ShortMem - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{Andre2013}
\item Shubik - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
\item Slow Tit For Two Tats - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{axelrodproject}
\item Slow Tit For Two Tats 2 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Prison1998}
\item Sneaky Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Soft Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1984, Mittal2009}
\item Soft Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
\item Soft Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
\item Soft Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
\item Soft Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
\item Soft Grudger - \textit{Deterministic} - \textit{Memory depth}: 6. \cite{Li2011}
\item Soft Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Prison1998}
\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2015}
\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{Ashlock2015}
\item Spiteful Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Stochastic Cooperator - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Adami2013}
\item Stochastic WSLS: 0.05 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
\item Suspicious Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Beaufils1997, Hilbe2013}
\item TF1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item TF2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item TF3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Tester - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
\item ThueMorse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item ThueMorseInverse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2008}
\item Tit For 2 Tats (\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
\item Tit For Tat (\textbf{TfT}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980}
\item Tricky Cooperator - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
\item Tricky Defector - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Tullock: 11 - \textit{Stochastic} - \textit{Memory depth}: 11. \cite{Axelrod1980}
\item Two Tits For Tat (\textbf{2TfT}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
\item VeryBad - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
\item Willing - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
\item Win-Shift Lose-Stay: D (\textbf{WShLSt}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Li2011}
\item Win-Stay Lose-Shift: C (\textbf{WSLS}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Kraines1989, Nowak1993, Stewart2012}
\item Winner12 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
\item Winner21 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
\item Worse and Worse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Worse and Worse 2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Worse and Worse 3 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item ZD-Extort-2 v2: 0.125, 0.5, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
\item ZD-Extort-2: 0.1111111111111111, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
\item ZD-Extort-4: 0.23529411764705882, 0.25, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
\item ZD-GEN-2: 0.125, 0.5, 3 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
\item ZD-GTFT-2: 0.25, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
\item ZD-SET-2: 0.25, 0.0, 2 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}

### 2017-07-06 main.tex
Write list of players.

@@
 Iterated Prisoner's Dilemma}
-\author{Marc Harper \and Vincent Knight} % TODO Authors?
+\author{Marc Harper \and Vincent Knight} % TODO Authors
 \date{}
@@
 
-* Update on Axelrod Library
+The Axelrod library \cite{knight2016open} is an open source software for
+conducting iterated prisoner's dilemma (IPD) research with reproducibilty as a
+principal goal. Written in the Python programming language, to date over the
+library contains source code contibuted by over 50 individuals from a variety
+of geographic locations and technical backgrounds. The library is supported by
+a comprehensive test suite that covers all the intended behaviors of the
+strategies in the library, as well as the features that conduct matches,
+tournaments, and population dynamics.
 
-% TODO: more
-
-The Axelrod library \cite{knight2016open} now contains over 200 strategies,
+As of version 3.0.0, the library contains over 200 strategies,
 many from the scientific literature, including classic strategies like Win Stay
@@
 
-There are several previous publications that use evolutionary algorithms to
+In this work we utilize the collection of strategies in the Axelrod library
+to train new strategies specifically to win IPD tournaments. We train these
+strategies using generic strategy archetypes based on e.g. finite state
+machines, arriving at particularly effective parameter choices through
+evolutionary or particle swarm algorithms. There are several
+previous publications that use evolutionary algorithms to
 evolve IPD strategies in various circumstances
@@
 results are unique in that we are able to train against a large collection of
-well-known strategies available in the scientific literature.
+well-known strategies available in the scientific literature. Crucially, the
+software used in this work is openly available and can be used to train strategies
+in the future in a reliable manner, with confidence that the opponent strategies
+are correctly implemented and documented. Moreover, as of the time of writing,
+we claim that this work contains the best known strategies for the iterated
+prisoner's dilemma.
 
@@
 training was obtained for $n_1 = m_1 = m_2 = 2$ and generally for $n_1 > 0$.
-First impressions matter in the IPD\@. The library includes a strategy
+The library includes a strategy
 called EvolvedLookerUp2\_2\_2 which is among the top strategies in the library.
@@
 
-This strategy type can be used to train arbitrary memory-$n$ strategies and a
-memory one strategy was trained and is called PSO Gambler Mem 1, with
+This strategy type can be used to train arbitrary memory-$n$ strategies. A
+memory one strategy called PSO Gambler Mem 1 was trained, with
 probabilities $(\text{Pr}(\text{C}\;|\;\text{CC}),
@@
 it is not as good as the longer memory strategies, and is bested by a similar
-strategy that also uses the first round of play: PSO Gamble 1 1 1.
+strategy that also uses the first round of play: PSO Gambler 1 1 1.
 
@@
 \cite{franken2005particle}.
-
-% TODO: quantify how stochastic
 
@@
 An inner layer with just five nodes performs quite well in both deterministic and
-noisy tournaments. The output of the ANN used in this work is deterministic and
+noisy tournaments. The output of the ANN used in this work is deterministic;
 a stochastic variant that outputs probabilities rather than exact moves could
 be easily created.
-
-% TODO: list features
 
@@
 We used strategies based on finite state machines to create a number of
-strategies. These strategies are deterministic and are efficient computational.
-At each state the machine transitions to a new state and plays a specified move
-depending on the opponent's last action. These strategies can encode a variety
-of other strategies, including classic strategies like TitForTat, encode
-handshakes, and grudging strategies that always defect after an opponent
-defection.
+strategies. These strategies are deterministic and are efficient computationally.
+In each round of play the strategy selects an action based on the current state
+and the opponent's last action, transitioning to a new state for the next round.
+These strategies can encode a variety
+of other strategies, including classic strategies like TitForTat, 
+handshake strategies, and grudging strategies that always defect after
+an opponent defection.
 
@@
 We also trained stochastic versions of finite state machine players called
-hidden Markov model players or HMMs. These strategies also encode an internal
-state with probabilistic transitions to other states and cooperate or defect
-with various probabilities at each state. These are the best performing
-stochastic strategies in the library but take longer to train due to their
-stochasticity.
+hidden Markov model players or HMMs. Like the finite state machines, these
+strategies also encode an internal
+state with probabilistic transitions based on the prior round of play to other
+states and cooperate or defect with various probabilities at each state. These
+are the best performing stochastic strategies in the library but take longer
+to train due to their stochasticity.
 
@@
 are common in machine learning called Meta strategies. These strategies are
-composed of a team of other strategies and each is polled for its desired next
-move. The ensemble then selects the next move based on some rule, such as the
+composed of a team of other strategies. In each round, each member of the team
+is polled for its desired next
+move. The ensemble then selects the next move based on a rule, such as the
 consensus vote in the case of MetaMajority or the best individual performance
@@
 
-We conducted a tournament with all strategies in the Axelrod library, including
-some parametrized strategies. These are listed in
+We conducted a tournament with a large collection of strategies from the Axelrod
+library, including some additional parametrized strategies (e.g. various parameter
+choices for Generous Tit For Tat). These are listed in
 Appendix~\ref{app:list_of_players}.
-% TODO Add list of players
-The top
-11 performing strategies by median payoff are all strategies trained to maximize
+The top 11 performing strategies by median payoff are all strategies trained to maximize
 % TODO Potentially modify this as more repetitions are analysed.
 total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
-The next strategy is
-Desired Belief Strategy (DBS)
+The next strategy is Desired Belief Strategy (DBS)
 % TODO Add reference for DBS
@@
 Fool Me Once, a grudging strategy that defects indefinitely on
-the second defection and Omega Tit For Tat.
-% TODO Add a reference for Omega TfT
+the second defection, and Omega Tit For Tat \cite{Slany2007}.
 All strategies in the tournament follow a simple set of
@@
 
+Any strategy that does not follow these rules, such as a strategy that defects
+on the last round of play, was omitted from the tournament presented here (but
+not from the training pool).
+
 % Table of best strategies
@@
             (ranked by median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).
+        The leaderboard is dominated by the machine learning strategies. ~$^{*}$
+        indicates that the strategy was trained.}
         \label{tbl:standard_score}
@@
 Pairwise payoff results are given as a heatmap (Figure~\ref{fig:standard_heatmap})
-which shows that many strategies achieve mutual cooperation with each other and
-that the top performing strategies never defect first but are able to exploit
-weaker strategies that attempt to defect.
+which shows that many strategies achieve mutual cooperation. The top performing
+strategies never defect first yet are able to exploit weaker strategies that
+attempt to defect.
 
@@
 strategies that were the result of training to maximize Moran process fixation.
-No strategies were trained specifically to win matches.
-None of the top scoring
+No strategies were trained specifically to win matches. None of the top scoring
 strategies appear in the top 20 list of strategies ranked by match wins.
@@
 example, the worst that the Evolved Lookerup 2 2 2 ranks in a given tournament
-is 7th.
+is 8th.
 
@@
 Spiteful TFT (TFT but defects indefinitely if the opponent defects twice
-consecutively) and OmegaTFT (also
-designed to handle noise).
+consecutively) and OmegaTFT (also designed to handle noise).
 
@@
         (ranked by median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)
+        ~$^{*}$ indicates that the strategy was trained.}
         \label{tbl:noisy_score}
@@
 number of matches in the presence of noise. For example Spiteful Tit For Tat in
-one tournament won almost all it's matches (167).
+one tournament won almost all its matches (167).
 
@@
 Figure~\ref{fig:noisy_ranks_boxplot} show the ranks (based on median score)
-of each strategy over the repeated tournaments. We see, that the stochasticity
+of each strategy over the repeated tournaments. We see that the stochasticity
 of the ranks understandably increases the DBS strategy never ranks lower than
@@
 
-Using the method of fingerprinting described in \cite{ashlock2008fingerprinting}
-\cite{ashlock2009fingerprint}, we can compare
-strategies. For the top performing noisy strategies there is a striking similarity
-in the fingerprints.
+Again we compare the fingerprints. For the top performing noisy strategies there
+is a striking similarity in the fingerprints which indicates that the strategies
+may behave similarly in principle.
 
@@
 We trained a variety of strategies using evolutionary algorithms, and in the
-case of PSO Gambler particle swarm algorithms. The evolutionary algorithms
+case of PSO Gambler using a particle swarm algorithm. The evolutionary algorithms
 used standard techniques, varying strategies by mutation and crossover, and
@@
 
-% Todo: Diagram with ANN training performance?
+% TODO: Diagram with ANN training performance?
 
 All training code is available on github. There are objective functions for
-* total payoff
-* total payoff difference
-* total Moran process wins (fixation probability)
+\begin{itemize}
+ \item total or mean payoff
+ \item total or mean payoff difference (unused in this work)
+ \item total Moran process wins (fixation probability)
+\end{itemize}
 
-New strategies can be easily trained with variations including noise, spatial
-structure, and probabilistically ending matches.
+These objectives can be easily modified to suit other purposes. New strategies
+can be easily trained with variations including noise, spatial structure, and
+probabilistically ending matches.
 
@@
 opponents. A simple evolutionary algorithm produces strategies based on multiple
-standard machine learning techniques that are able to achieve a higher median
+standard machine learning techniques that are able to achieve a higher average
 score than any other known opponent in a standard tournament. Most of the trained
@@
 outperform memory-one strategies (though the trained memory one strategy performs
-well). The generic structure of the trained strategy did not appear to be
+well). The generic structure of the trained strategies did not appear to be
 critical -- strategies based on lookup tables, finite state machines, and stochastic
@@
 performance across a collection of opponents leads to mutual cooperation despite
-the fact that mutual cooperation is an unstable equilibrium for the prisoner's
+the fact that mutual cooperation is an unstable evolutionary equilibrium for the prisoner's
 dilemma. Specifically we note that the reinforcement learning process for maximizing
-payout does not
-lead to exploitative zero determinant strategies, which may be a result of the
-collection of training strategies, many of which retaliate harshly.
+payout does not lead to exploitative zero determinant strategies, which may also
+be a result of the collection of training strategies, of which several retaliate harshly.
+
+We take the liberty of generalizing from the results of this study. For the trained
+strategies utilizing look up tables we generally found those that incorporate
+one of more of the initial rounds of play outperformed those that did not. The
+strategies based on neural networks and finite state machines also are able to
+condition throughout a match on the first rounds of play. Accordingly, we conclude
+that first impressions matter in the IPD\@. The best strategies are nice (never
+defecting first) and this property could be further investigated with the library
+in future work by e.g. forcing all strategies to defect on the first round.
 
@@
 fewer nodes and features and finite state machines with fewer states may suffice.
-See \cite{ashlock2013impact} for discussion of resource availability for IPD strategies.
+See \cite{ashlock2013impact} for discussion of resource availability for IPD
+strategies. It may be possible to train strategies more effective in noisy tournaments
+than DBS.
 
@@
 * further refine features and training parameters
-
-% TODO: Full strategy list
 
@@
 
+\appendix
+
+\section{List of players}\label{app:list_of_players}
+
+\begin{multicols}{2}
+	\begin{enumerate}
+		\input{./assets/list_of_players.tex}
+	\end{enumerate}
+\end{multicols}
+
 \end{document}

### 2017-07-06 src/submit_ml_jobs.sh
Submit final jobs.

@@ -82,19 +82,19 @@
 #qsub pbs_files/ml-40-0-1000.pbs
 #qsub pbs_files/ml-41-5-1000.pbs
 #qsub pbs_files/ml-41-0-1000.pbs
-qsub pbs_files/ml-42-5-1000.pbs
-qsub pbs_files/ml-42-0-1000.pbs
-qsub pbs_files/ml-43-5-1000.pbs
-qsub pbs_files/ml-43-0-1000.pbs
-qsub pbs_files/ml-44-5-1000.pbs
-qsub pbs_files/ml-44-0-1000.pbs
-qsub pbs_files/ml-45-5-1000.pbs
-qsub pbs_files/ml-45-0-1000.pbs
-qsub pbs_files/ml-46-5-1000.pbs
-qsub pbs_files/ml-46-0-1000.pbs
-qsub pbs_files/ml-47-5-1000.pbs
-qsub pbs_files/ml-47-0-1000.pbs
-qsub pbs_files/ml-48-5-1000.pbs
-qsub pbs_files/ml-48-0-1000.pbs
-qsub pbs_files/ml-49-5-1000.pbs
-qsub pbs_files/ml-49-0-1000.pbs
+#qsub pbs_files/ml-42-5-1000.pbs
+#qsub pbs_files/ml-42-0-1000.pbs
+#qsub pbs_files/ml-43-5-1000.pbs
+#qsub pbs_files/ml-43-0-1000.pbs
+#qsub pbs_files/ml-44-5-1000.pbs
+#qsub pbs_files/ml-44-0-1000.pbs
+#qsub pbs_files/ml-45-5-1000.pbs
+#qsub pbs_files/ml-45-0-1000.pbs
+#qsub pbs_files/ml-46-5-1000.pbs
+#qsub pbs_files/ml-46-0-1000.pbs
+#qsub pbs_files/ml-47-5-1000.pbs
+#qsub pbs_files/ml-47-0-1000.pbs
+#qsub pbs_files/ml-48-5-1000.pbs
+#qsub pbs_files/ml-48-0-1000.pbs
+#qsub pbs_files/ml-49-5-1000.pbs
+#qsub pbs_files/ml-49-0-1000.pbs

### 2017-07-06 main.tex
Add table of wins for top winners.
Discussed on #4

@@
 
+Table~\ref{tbl:standard_wins_top_winners} shows the same information as
+Table~\ref{tbl:standard_wins} but for the top 15 strategies who win the most
+head to head matches.
+% TODO Add more?
+
+\begin{table}[!hbtp]
+    \centering
+        \input{./assets/standard_top_15_winners_wins_summary.tex}
+        \caption{Standard Tournament: Number of wins per tournament
+        of top 15 strategies (ranked by median wins over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \label{tbl:standard_wins_top_winners}
+\end{table}
+
 Finally, Table~\ref{tbl:standard_ranks} and
@@
         \label{tbl:noisy_wins}
+\end{table}
+
+Table~\ref{tbl:noisy_wins_top_winners} shows the same information as
+Table~\ref{tbl:noisy_wins} but for the top 15 strategies who win the most
+head to head matches.
+% TODO Add more?
+
+\begin{table}[!hbtp]
+    \centering
+        \input{./assets/noisy_top_15_winners_wins_summary.tex}
+        \caption{Noisy (5\%) Tournament: Number of wins per tournament
+        of top 15 strategies (ranked by median wins over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \label{tbl:noisy_wins_top_winners}
 \end{table}

### 2017-07-07 main.tex
Draw remaining diagrams for players.

@@
 the players last $m_2$ moves. If $n_1 > 0$ then the player has infinite memory
-depth, otherwise it has depth $\max{m_1, m_2}$. Although we tried various
+depth, otherwise it has depth $\max{m_1, m_2}$.
+This is shown diagrammatically in Figure~\ref{fig:lookerup}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includestandalone[height=.3\textheight]{./assets/lookerup}
+    \caption{Diagrammatic representation of the Looker up Archetype}
+    \label{fig:lookerup}
+\end{figure}
+
+Although we tried various
 combinations of $n_1, m_1,$ and $m_2$, the best performance at the time of
@@
 
-\subsection{PSO Gambler}
+\subsection{Gambler}
 
-PSO Gambler is a stochastic variant of LookerUp. Instead of deterministically
+Gambler is a stochastic variant of LookerUp. Instead of deterministically
 encoded moves the lookup table emits probabilities which are
-used to choose cooperation or defection. The library includes a player trained
+used to choose cooperation or defection.
+This is shown diagrammatically in Figure~\ref{fig:gambler}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includestandalone[height=.3\textheight]{./assets/gambler}
+    \caption{Diagrammatic representation of the Gambler Archetype}
+    \label{fig:gambler}
+\end{figure}
+
+The library includes a player trained
 with $n_1 = m_1 = m_2 = 2$ that is \emph{mostly deterministic}, with most of the
@@
 into a feed forward neural network with one layer and user-supplied width.
+This is shown diagrammatically in Figure~\ref{fig:ann}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includestandalone[height=.3\textheight]{./assets/ann}
+    \caption{Diagrammatic representation of the ANN Archetype}
+    \label{fig:ann}
+\end{figure}
+
 An inner layer with just five nodes performs quite well in both deterministic and
@@
 an opponent defection.
+This is shown diagrammatically in Figure~\ref{fig:fsm}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includestandalone[height=.3\textheight]{./assets/fsm}
+    \caption{Diagrammatic representation of the Finite state machine Archetype}
+    \label{fig:fsm}
+\end{figure}
 
@@
 to train due to their stochasticity.
+This is shown diagrammatically in Figure~\ref{fig:hmm}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includestandalone[height=.3\textheight]{./assets/hmm}
+    \caption{Diagrammatic representation of the Hidden Markov Model Archetype}
+    \label{fig:hmm}
+\end{figure}
 

### 2017-07-07 main.tex
Make minor adjustments.
- Clean up description of strategies to be consistent.
- Explain what training corresponds to for each strategy.
- Add a number of TODOs.

@@
     (evolutionary and particle swarm algorithms). These strategies are
-    trained to perform well against a corpus of over 100 distinct
-    opponents, including many well-known strategies from the literature, and all
+    trained to perform well against a corpus of over 170 distinct
+    opponents, including many well-known strategies from the literature. All
     the trained strategies win standard tournaments against the total collection
@@
 methods. Most are deterministic, use many rounds of memory, and perform
-extremely well in tournaments.
+extremely well in tournaments as will be discussed in Section~\ref{sec:results}.
+Training of these strategies will be discussed in Section~\ref{sec:methods}.
+
+These strategies can encode a variety
+of other strategies, including classic strategies like Tit For Tat,
+handshake strategies, and grudging strategies that always defect after
+an opponent defection.
 
@@
 
-The first strategy trained with reinforcement learning in the library is based
-on lookup tables. The strategy encodes a set of deterministic responses
-based on the opponent's first $n_1$ moves, the opponent's last $m_1$ moves, and
-the players last $m_2$ moves. If $n_1 > 0$ then the player has infinite memory
-depth, otherwise it has depth $\max{m_1, m_2}$.
-This is shown diagrammatically in Figure~\ref{fig:lookerup}.
+The LookerUp strategy is based on a lookup tables and  encodes a set of
+deterministic responses based on the opponent's first $n_1$ moves, the
+opponent's last $m_1$ moves, and the players last $m_2$ moves. If $n_1 > 0$ then
+the player has infinite memory depth, otherwise it has depth $\max{m_1, m_2}$.
+This is illustrated diagrammatically in Figure~\ref{fig:lookerup}.
 
@@
 
-Although we tried various
-combinations of $n_1, m_1,$ and $m_2$, the best performance at the time of
+Training of this strategy corresponds to finding maps from histories to either a
+cooperation or a defection.
+
+Although various
+combinations of $n_1, m_1,$ and $m_2$ have been tried, the best performance at
+the time of
 training was obtained for $n_1 = m_1 = m_2 = 2$ and generally for $n_1 > 0$.
-The library includes a strategy
-called EvolvedLookerUp2\_2\_2 which is among the top strategies in the library.
+A strategy
+called EvolvedLookerUp2\_2\_2 is among the top strategies in the library.
 
@@
 used to choose cooperation or defection.
-This is shown diagrammatically in Figure~\ref{fig:gambler}.
+This is illustrated diagrammatically in Figure~\ref{fig:gambler}.
 
@@
 
-The library includes a player trained
+Training of this strategy corresponds to finding maps from histories to
+a probability of cooperation.
+
+The library includes a strategy trained
 with $n_1 = m_1 = m_2 = 2$ that is \emph{mostly deterministic}, with most of the
@@
 it is not as good as the longer memory strategies, and is bested by a similar
-strategy that also uses the first round of play: PSO Gambler 1 1 1.
+strategy that also uses the first round of play: PSOGambler\_1\_1\_1.
 
@@
 
-Strategies based on artificial neural networks can also be trained with an
-evolutionary algorithm. A variety of features are computed from the history
-of play such as the opponents trailing moves, the total number of cooperations
-of the player and the opponent, and several others, which are then input
-into a feed forward neural network with one layer and user-supplied width.
-This is shown diagrammatically in Figure~\ref{fig:ann}.
+Strategies based on artificial neural networks use a variety of features
+computed from the history of play:
+
+\begin{multicols}{2}
+    \begin{itemize}
+        \item Opponent's first move is C
+        \item Opponent's first move is D
+        \item Opponent's second move is C
+        \item Opponent's second move is D
+        \item Player's previous move is C
+        \item Player's previous move is D
+        \item Player's second previous move is C
+        \item Player's second previous move is D
+        \item Opponent's previous move is C
+        \item Opponent's previous move is D
+        \item Opponent's second previous move is C
+        \item Opponent's second previous move is D
+        \item Total opponent cooperations
+        \item Total opponent defections
+        \item Total player cooperations
+        \item Total player defections
+        \item Round number
+    \end{itemize}
+\end{multicols}
+
+These are then input into a feed forward neural network with one layer and
+user-supplied width.  This is illustrated diagrammatically in
+Figure~\ref{fig:ann}.
 
@@
 
+Training of this strategy corresponds to finding parameters of the neural
+network.
+
 An inner layer with just five nodes performs quite well in both deterministic and
@@
 
-We used strategies based on finite state machines to create a number of
-strategies. These strategies are deterministic and are efficient computationally.
+Strategies based on finite state machines are deterministic and computationally efficient.
 In each round of play the strategy selects an action based on the current state
 and the opponent's last action, transitioning to a new state for the next round.
-These strategies can encode a variety
-of other strategies, including classic strategies like TitForTat,
-handshake strategies, and grudging strategies that always defect after
-an opponent defection.
-This is shown diagrammatically in Figure~\ref{fig:fsm}.
+This is illustrated diagrammatically in Figure~\ref{fig:fsm}.
 
@@
 
-% TODO: One or more FSM diagrams
+Training this strategy corresponds to finding mappings of states and histories
+to an action and a state. Figures~\ref{} show two of the trained finite state
+machines...
+% TODO Update sentence above.
+% TODO Add diagrams of FSMs.
 
@@
 
-We also trained stochastic versions of finite state machine players called
-hidden Markov model players or HMMs. Like the finite state machines, these
-strategies also encode an internal
-state with probabilistic transitions based on the prior round of play to other
-states and cooperate or defect with various probabilities at each state. These
-are the best performing stochastic strategies in the library but take longer
-to train due to their stochasticity.
-This is shown diagrammatically in Figure~\ref{fig:hmm}.
+A variant of finite state machine strategies are called hidden Markov models
+(HMMs). Like the strategies based on finite state machines, these strategies
+also encode an internal state however use probabilistic transitions based on the
+prior round of play to other states and cooperate or defect with various
+probabilities at each state. This is
+shown diagrammatically in Figure~\ref{fig:hmm}.
 
@@
 \end{figure}
+
+Training this strategy corresponds to finding mappings of states and histories
+to probabilities of cooperating as well as probabilities of the next internal
+state.
+
+These are the best performing stochastic strategies
+in the library but take longer to train due to their stochasticity.
 
@@
 on which they are based, including using the match length to defect on the last
-rounds of play, these strategies were omitted from the tournament results.
+rounds of play, not all of these strategies were included in results of this
+paper.
 
-\section{Results}
+\section{Results}\label{sec:results}
 
@@
 
-Using the method of fingerprinting described in \cite{ashlock2008fingerprinting}
+Using the method of fingerprinting described in \cite{ashlock2008fingerprinting,
+ashlock2009fingerprint}
 % TODO This is actually a numerical approximation of the fingerprinting
@@
 % analytic function.
-\cite{ashlock2009fingerprint}, we can compare
+we can compare
 strategies. For the top performing noisy strategies there is a striking similarity
@@
 \end{figure}
+
+% TODO Include collaboration rating heatmaps
 
@@
 
-\section{Methods}
+% TODO Include collaboration rating heatmaps
+
+\section{Methods}\label{sec:methods}
 
@@
 200 generations or until strategies no longer improve significantly.
+% TODO Improve the explanation here with more details. As described this is not
+% reproducible.
+% TODO Include references
 
@@
 All training code is available on github. There are objective functions for
+% TODO We should archive the code.
+
 \begin{itemize}

### 2017-07-07 src/abbreviations.py
Add stars to trained strategy names.
Also tweaked other abbreviations that were incorrect (because of
parametrization we still need to differentiate).

FYI, anything in `assets` is automatically generated so best not to
modify that.

@@ -4,7 +4,7 @@ A dictionary of player name abbreviations
 import players
 
 # Abbreviate all player names to their strategy names
-abbreviations = {str(player):player.name for player in players.players}
+abbreviations = {str(player): player for player in players.players}
 
 # Some manual overwrites:
 
@@ -18,3 +18,14 @@ abbreviations["Two Tits For Tat"] = "2TfT"
 abbreviations["Tit For 2 Tats"] = "Tf2T"
 abbreviations["Win-Stay Lose-Shift: C"] = "WSLS"
 abbreviations["Win-Shift Lose-Stay: D"] = "WShLSt"
+abbreviations["DBS: 0.75, 3, 4, 3, 5"] = "DBS"
+
+for name, player in abbreviations.items():
+    if "Evolved" in name or "PSO" in name:
+        abbreviations[name] = "{}$^{{*}}$".format(player)
+    elif "Gradual Killer" in name:
+        abbreviations[name] = "Gradual Killer"
+    elif "ZD" in name:
+        abbreviations[name] = player.name
+    else:
+        abbreviations[name] = str(player)

### 2017-07-07 main.tex
Add placeholder cooperation rate heatmaps.
Added without comment. These are for 20 repetitions. I've got 10k
repetitions coming down the pipes.

@@
 
-    \caption{Comparison of Fingerprints for Noisy Tournament Top 3}
-    \label{fig:comparison_fingerprint_noisy}
+    \caption{Comparison of Fingerprints for Standard Tournament Top 3}
+    \label{fig:comparison_fingerprint_standard}
+\end{figure}
+% TODO Add text ref to this
+
+Figure~\ref{fig:comparison_cooperation_heatmaps_standard} shows the rate of
+cooperation in each round for the top three strategies.
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_EvolvedLookerUp2_2_2_array.pdf}
+        \caption{Cooperation rate per round for EvolvedLookerUp\_2\_2\_2 (over
+        20 repetitions)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_HMM_5_array.pdf}
+        \caption{Cooperation rate per round for Evolved\_HMM\_5 (over 20
+        repetitions)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_FSM_16_array.pdf}
+        \caption{Cooperation rate per round for Evolved\_FSM\_16 (over 20
+        repetitions)}
+    \end{subfigure}%
+
+    \caption{Comparison of collaboration rates for Standard Tournament Top 3}
+    \label{fig:comparison_cooperation_heatmaps_standard}
 \end{figure}
 
-% TODO Include collaboration rating heatmaps
+% TODO Update these with 10k repetition version
 
@@
 
-    \caption{Comparison of Fingerprints for Noisy Tournament Top 3}
+    \caption{Comparison of Fingerprints for Noisy (5\%) Tournament Top 3}
     \label{fig:comparison_fingerprint_noisy}
 \end{figure}
+% TODO Add text ref to this
 
-% TODO Include collaboration rating heatmaps
+Figure~\ref{fig:comparison_cooperation_heatmaps_noisy} shows the rate of
+cooperation in each round for the top three strategies.
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_DBS_0-75_3_4_3_5_array.pdf}
+        \caption{Cooperation rate per round for DBS (over 20 repetitions)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_ANN_5_Noise_05_array.pdf}
+        \caption{Cooperation rate per round for Evolved\_ANN\_5\_Noise\_05 (over 20
+        repetitions)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_FSM_16_Noise_05_array.pdf}
+        \caption{Cooperation rate per round for Evolved\_FSM\_16\_Noise\_05 (over 20
+        repetitions)}
+    \end{subfigure}%
+
+    \caption{Comparison of collaboration rates for Noisy (5\%) Tournament Top 3}
+    \label{fig:comparison_cooperation_heatmaps_noisy}
+\end{figure}
+
+% TODO Update these with 10k repetition version
 

### 2017-07-07 main.tex
Minor adjustments and adding a few TODOs.

@@
 % TODO Update sentence above.
-% TODO Add diagrams of FSMs.
+% TODO Add diagrams of FSMs. Note how the strategies are called FSM 16 but as is
+% evident in the diagram, it is in fact a 14 state fsm.
 
@@
 total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
-The next strategy is Desired Belief Strategy (DBS)
-% TODO Add reference for DBS
+The next strategy is Desired Belief Strategy (DBS) \cite{Au2006}.
 which actively analyzes the opponent and responds
@@
 Fool Me Once, a grudging strategy that defects indefinitely on
-the second defection, and Omega Tit For Tat \cite{Slany2007}.
+the second defection, and Omega Tit For Tat \cite{kendall2007iterated}.
 All strategies in the tournament follow a simple set of
@@
         \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).
-        The leaderboard is dominated by the machine learning strategies. ~$^{*}$
+        The leaderboard is dominated by the trained strategies. Starred
+        strategies $^{*}$
         indicates that the strategy was trained.}
@@
 head to head matches.
-% TODO Add more?
+% TODO Add more discussion?
 
@@
 
-Using the method of fingerprinting described in \cite{ashlock2008fingerprinting,
-ashlock2009fingerprint}
-% TODO This is actually a numerical approximation of the fingerprinting
-% described in ashlock's paper. There they consider a fingerprint to be an
-% analytic function.
-we can compare
-strategies. For the top performing noisy strategies there is a striking similarity
-in the fingerprints.
+Using the a numerical method of fingerprinting based on
+\cite{ashlock2008fingerprinting, ashlock2009fingerprint} we can compare
+strategies. The fingerprints of the top performing standard strategies are shown
+in Figures~\ref{fig:comparison_fingerprint_standard}. There is a striking
+similarity in the fingerprints.
 
@@
 \end{figure}
-% TODO Add text ref to this
 
@@
 cooperation in each round for the top three strategies.
+% TODO Discuss more? (If we want to keep this)
 
@@
 
-Again we compare the fingerprints. For the top performing noisy strategies there
+Again we compare the fingerprints. For the top performing noisy strategies
+(Figure~\ref{fig:comparison_fingerprint_noisy}) there
 is a striking similarity in the fingerprints which indicates that the strategies
@@
 cooperation in each round for the top three strategies.
+% TODO Add more discussion
 
@@
 All training code is available on github. There are objective functions for
-% TODO We should archive the code.
+% TODO Include pointer when code is archived.
 
@@
 than human designed strategies at maximizing payoff against a diverse set of
-opponents. A simple evolutionary algorithm produces strategies based on multiple
+opponents. An evolutionary algorithm produces strategies based on multiple
 standard machine learning techniques that are able to achieve a higher average
@@
 our results show that complex strategies can be very effective for the
-IPD. It is not the complexity of strategies that is disadvantageous; rather that directly
+IPD\@. It is not the complexity of strategies that is disadvantageous; rather that directly
 designing a broadly effective strategy is no easy task. Of all the human-designed
@@
 for most strategies. Two strategies designed specifically to account for noise,
-DBS and OmegaTFT, perform well and only DBS performs better than our trained
-strategies.
+DBS and OmegaTFT, perform well and only DBS performs better than the trained
+strategies and \textbf{only} in the noisy context.
 
-Of the strategies trained to maximize their median score all are generally
+Of the strategies trained to maximize their average score all are generally
 cooperative, not defecting until the opponent defects. Maximizing for individual
@@
 the fact that mutual cooperation is an unstable evolutionary equilibrium for the prisoner's
-dilemma. Specifically we note that the reinforcement learning process for maximizing
-payout does not lead to exploitative zero determinant strategies, which may also
+dilemma. Specifically it is noted that the reinforcement learning process for maximizing
+payoff does not lead to exploitative zero determinant strategies, which may also
 be a result of the collection of training strategies, of which several retaliate harshly.
@@
 strategies utilizing look up tables we generally found those that incorporate
-one of more of the initial rounds of play outperformed those that did not. The
+one or more of the initial rounds of play outperformed those that did not. The
 strategies based on neural networks and finite state machines also are able to
@@
 that first impressions matter in the IPD\@. The best strategies are nice (never
-defecting first) and this property could be further investigated with the library
-in future work by e.g. forcing all strategies to defect on the first round.
+defecting first) and this property could be further investigated with the
+Axelrod library
+in future work by e.g.\ forcing all strategies to defect on the first round.
 
@@
 trained on an earlier version of the library (v2.2.0) that did not include DBS
+% Cite v2.2.0
 and several other opponents. The precise parameters that are optimal will depend
@@
 Future work:
-* spatial tournaments and other variants
-* Additional strategy archetypes by the Ashlocks, e.g. function stacks, binary
-decision players
-* further refine features and training parameters
+% TODO Write the future work section
+%* spatial tournaments and other variants
+%* Additional strategy archetypes by the Ashlocks, e.g. function stacks, binary
+%decision players
+%* further refine features and training parameters
 
@@
 
+The players used for this study are from Axelrod version 2.13.0. The starred $*$
+strategies indicate those that have been trained using reinforcement learning
+algorithms.
+
 \begin{multicols}{2}

### 2017-07-07 main.tex

@@
 
-The Axelrod library \cite{knight2016open} is an open source software for
-conducting iterated prisoner's dilemma (IPD) research with reproducibilty as a
-principal goal. Written in the Python programming language, to date over the
-library contains source code contibuted by over 50 individuals from a variety
-of geographic locations and technical backgrounds. The library is supported by
-a comprehensive test suite that covers all the intended behaviors of the
-strategies in the library, as well as the features that conduct matches,
-tournaments, and population dynamics.
+The Axelrod library \cite{axelrodproject, knight2016open} is an open source
+software for conducting iterated prisoner's dilemma (IPD) research with
+reproducibility as a principal goal. Written in the Python programming language,
+to date over the library contains source code contributed by over 50 individuals
+from a variety of geographic locations and technical backgrounds. The library
+is supported by a comprehensive test suite that covers all the intended
+behaviors of the strategies in the library, as well as the features that
+conduct matches, tournaments, and population dynamics.
 
-As of version 3.0.0, the library contains over 200 strategies,
-many from the scientific literature, including classic strategies like Win Stay
-Lose Shift \cite{nowak1993strategy} and previous tournament winners such as
-OmegaTFT \cite{slany2007some}, Adaptive Pavlov \cite{li2007design}, and
-ZDGTFT2 \cite{stewart2012extortion}.
+The library is continuously developed and as of version 3.0.0, the library
+contains over 200 strategies, many from the scientific literature, including
+classic strategies like Win Stay Lose Shift \cite{nowak1993strategy} and
+previous tournament winners such as OmegaTFT \cite{slany2007some}, Adaptive
+Pavlov \cite{li2007design}, and ZDGTFT2 \cite{stewart2012extortion}.
 
@@
 
-In this work we utilize the collection of strategies in the Axelrod library
-to train new strategies specifically to win IPD tournaments. We train these
-strategies using generic strategy archetypes based on e.g. finite state
+In this work we describe how collections of strategies in the Axelrod library
+have been used to train new strategies specifically to win IPD tournaments.
+These strategies are trained using generic strategy archetypes based on e.g.
+finite state
 machines, arriving at particularly effective parameter choices through
@@
 in the future in a reliable manner, with confidence that the opponent strategies
-are correctly implemented and documented. Moreover, as of the time of writing,
+are correctly implemented, tested and documented.
+Moreover, as of the time of writing,
 we claim that this work contains the best known strategies for the iterated
@@
 We conducted a tournament with a large collection of strategies from the Axelrod
-library, including some additional parametrized strategies (e.g. various parameter
+library, including some additional parametrized strategies (e.g.\ various parameter
 choices for Generous Tit For Tat). These are listed in
@@
 
-Using the a numerical method of fingerprinting based on
+Using a numerical method of fingerprinting based on
 \cite{ashlock2008fingerprinting, ashlock2009fingerprint} we can compare
@@
 
-We trained a variety of strategies using evolutionary algorithms, and in the
-case of PSO Gambler using a particle swarm algorithm. The evolutionary algorithms
-used standard techniques, varying strategies by mutation and crossover, and
-evaluating the performance against each opponent for many repetitions. The
-best performing strategies in each generation are persisted, variants created,
-and objective functions computed again. This process continues for approximately
-200 generations or until strategies no longer improve significantly.
-% TODO Improve the explanation here with more details. As described this is not
-% reproducible.
-% TODO Include references
+The trained strategies (denoted by a \(^{*}\) in
+Appendix~\ref{app:list_of_players} were trained using reinforcement
+learning algorithms. The ideas of reinforcement learning can be attributed to
+the original work of \cite{turing1950computing} in which the notion that
+computers would learn by taking random actions but according to a distribution
+that picked actions with high rewards more often. The two particular algorithms
+used here:
 
-% TODO: Diagram with ANN training performance?
+\begin{itemize}
+    \item Evolutionary algorithm: \cite{moriarty1999evolutionary}.
+    \item Particle Swarm Algorithm: \cite{imran2013overview}.
+\end{itemize}
 
-All training code is available on github. There are objective functions for
-% TODO Include pointer when code is archived.
+The Particle Swarm Algorithm is implemented using the Python library:
+\url{https://pypi.python.org/pypi/pyswarm}. This algorithm was used only to
+train the Gambler archetype.
+
+All other strategies were trained using evolutionary algorithms. The
+evolutionary algorithms used standard techniques, varying strategies by
+mutation and crossover, and evaluating the performance against each opponent
+for many repetitions. The best performing strategies in each generation are
+persisted, variants created, and objective functions computed again.
+
+The default parameters for this procedure:
+
+\begin{itemize}
+	\item A population size of 40 individuals (kept constant across the
+        generations);
+	\item A mutation rate of 10\%;
+	\item 10 individuals kept from one generation to the next;
+    \item A total of 500 generations.
+\end{itemize}
+
+All implementations of these algorithms are archived at
+\cite{marc_harper_2017_824264}. This software is (similarly to the Axelrod
+library) available on github
+\url{https://github.com/Axelrod-Python/axelrod-dojo}.  There are objective
+functions for:
 
@@
  \item total or mean payoff difference (unused in this work)
- \item total Moran process wins (fixation probability)
+ \item total Moran process wins (fixation probability). This lead to the
+     strategies named TF1, TF2, TF3 listed in
+     Appendix~\ref{app:list_of_players}.
 \end{itemize}
 
-These objectives can be easily modified to suit other purposes. New strategies
-can be easily trained with variations including noise, spatial structure, and
-probabilistically ending matches.
+These can be used in Noisy or Standard environments (as evidenced by
+Sections~\ref{sec:standard} and~\ref{sec:noisy}). These objectives can be
+further modified to suit other purposes. New strategies could be trained with
+variations including spatial structure, and probabilistically ending matches.
 
@@
 though these had some aspect of human involvement in the selection of features.
+% TODO Question: is this arguably just as much human involvement in the design
+% of the lookup tables etc? We could use a lookup table that also picks out the
+% action from the middle round, however we have chosen not too.
 The success of the other strategy types suggests that a deeper network that
@@
 sometimes shuffle, and are not retrained regularly. Most of the strategies were
-trained on an earlier version of the library (v2.2.0) that did not include DBS
-% Cite v2.2.0
-and several other opponents. The precise parameters that are optimal will depend
-on the pool of opponents. Moreover we have not extensively trained strategies to
-determine the minimum parameters that are sufficient -- neural networks with
-fewer nodes and features and finite state machines with fewer states may suffice.
-See \cite{ashlock2013impact} for discussion of resource availability for IPD
-strategies. It may be possible to train strategies more effective in noisy tournaments
-than DBS.
+trained on an earlier version of the library (v2.2.0: \cite{axelrodproject2.2})
+that did not include DBS and several other opponents. The precise parameters
+that are optimal will depend on the pool of opponents. Moreover we have not
+extensively trained strategies to determine the minimum parameters that are
+sufficient -- neural networks with fewer nodes and features and finite state
+machines with fewer states may suffice. See \cite{ashlock2013impact} for
+discussion of resource availability for IPD strategies. It may be possible to
+train strategies more effective in noisy tournaments than DBS.
 
@@
 
-The players used for this study are from Axelrod version 2.13.0. The starred $*$
+The players used for this study are from Axelrod version 2.13.0
+\cite{axelrodproject}. The starred $*$
 strategies indicate those that have been trained using reinforcement learning

### 2017-07-07 assets/FSM16.tex
tex to draw FSM16

\documentclass{standalone}

\usepackage{tikz}
\usepackage{standalone}
\usetikzlibrary{calc}

\begin{document}
    \begin{tikzpicture}

    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];

    \node[circle, draw=black, thick] (0) at (0.0: 6cm) [state]    {$1$};
    \node[circle, draw=black, thick] (1) at (24.0: 6cm) [state]   {$2$};
    \node[circle, draw=black, thick] (2) at (48.0: 6cm) [state]   {$3$};
    \node[circle, draw=black, thick] (3) at (72.0: 6cm) [state]   {$4$};
    \node[circle, draw=black, thick] (4) at (96.0: 6cm) [state]   {$5$};
    \node[circle, draw=black, thick] (6) at (120.0: 6cm) [state]  {$7$};
    \node[circle, draw=black, thick] (7) at (144.0: 6cm) [state]  {$8$};
    \node[circle, draw=black, thick] (8) at (168.0: 6cm) [state]  {$9$};
    \node[circle, draw=black, thick] (9) at (192.0: 6cm) [state]  {$10$};
    \node[circle, draw=black, thick] (10) at (216.0: 6cm) [state] {$11$};
    \node[circle, draw=black, thick] (11) at (240.0: 6cm) [state] {$12$};
    \node[circle, draw=black, thick] (12) at (264.0: 6cm) [state] {$13$};
    \node[circle, draw=black, thick] (13) at (288.0: 6cm) [state] {$14$};
    \node[circle, draw=black, thick] (14) at (312.0: 6cm) [state] {$15$};
    \node[circle, draw=black, thick] (15) at (336.0: 6cm) [state] {$16$};

    \node[circle, draw=black, thick] (5) at (0, 1) [state]   {$6$};

    \coordinate[right of=0] (s);

    \draw (s) edge[out=180, in=0, ->, thick] node [above] {$C$} (0);
    \draw (0) edge[out=45, in=90, ->, thick, loop] node [above] {$C/C$} (0);
    \draw (0) edge[out=180, in=45, ->, thick] node [above right, yshift=2cm, xshift=2.5cm] {$D/D$} (12);

    \draw (1) edge[out=135, in=-90, ->, thick] node [above, yshift=1cm, xshift=-0.5cm] {$C/D$} (3);
    \draw (1) edge[out=180, in=0, ->, thick] node [above left, yshift=1.5cm, xshift=-2.5cm] {$D/C$} (6);

    \draw (2) edge[out=45, in=90, ->, thick, loop] node [above] {$C/D$} (2);
    \draw (2) edge[out=-110, in=110, ->, thick] node [right, yshift=-3.7cm, xshift=0.8cm] {$D/D$} (14);

    \draw (3) edge[out=45, in=80, ->, thick, loop] node [above] {$C/D$} (3);
    \draw (3) edge[out=135, in=100, ->, thick, loop] node [above] {$D/D$} (3);

    \draw (5) edge[out=-90, in=90, ->, thick] node [above, rotate=90] {$C/D$} (12);
    \draw (5) edge[out=180, in=90, ->, thick] node [above left, yshift=-3cm] {$D/D$} (10);

    \draw (6) edge[out=-45, in=90, ->, thick] node [above right] {$C/C$} (5);
    \draw (6) edge[out=-90, in=135, ->, thick] node [right, yshift=4.4cm, xshift=-0.2cm, rotate=90] {$D/D$} (12);

    \draw (7) edge[out=45, in=-135, ->, thick] node [above right, xshift=1.5cm, yshift=0.5cm] {$C/D$} (3);
    \draw (7) edge[out=0, in=-135, ->, thick] node [above right, yshift=-0.5cm, xshift=4cm] {$D/C$} (1);

    \draw (8) edge[out=45, in=135, ->, thick] node [above left, xshift=-2cm, yshift=-0.2cm, rotate=45] {$C/C$} (5);
    \draw (8) edge[out=-45, in=-135, ->, thick] node [above left, xshift=-2.2cm, rotate=-45] {$D/C$} (5);

    \draw (10) edge[out=-90, in=180, ->, thick] node [below, yshift=-0.3cm] {$C/D$} (11);
    \draw (10) edge[out=180, in=180, ->, thick] node [above left, rotate=90] {$D/C$} (8);

    \draw (11) edge[out=0, in=180, ->, thick] node [above right, yshift=1.5cm, xshift=2.5cm] {$C/D$} (15);
    \draw (11) edge[out=90, in=-110, ->, thick] node [below left, yshift=-2cm, xshift=-1.2cm] {$D/D$} (5);

    \draw (12) edge[out=110, in=0, ->, thick] node [above, yshift=2.2cm, xshift=-2.2cm] {$C/C$} (8);
    \draw (12) edge[out=-135, in=-90, ->, thick] node [below, yshift=-0.1cm] {$D/D$} (11);

    \draw (13) edge[out=-45, in=-90, ->, thick, loop] node [below] {$C/D$} (13);
    \draw (13) edge[out=90, in=-45, ->, thick] node [left, xshift=-4cm, yshift=3.3cm] {$D/D$} (7);

    \draw (14) edge[out=-115, in=0, ->, thick] node [below, xshift=0.3cm] {$C/D$} (13);
    \draw (14) edge[out=-165, in=55, ->, thick] node [above] {$D/D$} (13);

    \draw (15) edge[out=45, in=90, ->, thick, loop] node [above] {$C/D$} (15);
    \draw (15) edge[out=110, in=-90, ->, thick] node [above right, yshift=2.5cm, xshift=-0.2cm] {$D/C$} (2);

    \end{tikzpicture}
\end{document}

### 2017-07-08 assets/FSM16noise.tex

\documentclass{standalone}

\usepackage{tikz}
\usepackage{standalone}
\usetikzlibrary{calc}

\begin{document}
    \begin{tikzpicture}

    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];

    \node[circle, draw=black, thick] (0) at (0.0: 6cm) [state]    {$1$};
    \node[circle, draw=black, thick] (1) at (24.0: 6cm) [state]   {$2$};
    \node[circle, draw=black, thick] (2) at (48.0: 6cm) [state]   {$3$};
    \node[circle, draw=black, thick] (3) at (72.0: 6cm) [state]   {$4$};
    \node[circle, draw=black, thick] (4) at (96.0: 6cm) [state]   {$5$};
    \node[circle, draw=black, thick] (6) at (120.0: 6cm) [state]  {$7$};
    \node[circle, draw=black, thick] (7) at (144.0: 6cm) [state]  {$8$};
    \node[circle, draw=black, thick] (8) at (168.0: 6cm) [state]  {$9$};
    \node[circle, draw=black, thick] (9) at (192.0: 6cm) [state]  {$10$};
    \node[circle, draw=black, thick] (10) at (216.0: 6cm) [state] {$11$};
    \node[circle, draw=black, thick] (11) at (240.0: 6cm) [state] {$12$};
    \node[circle, draw=black, thick] (12) at (264.0: 6cm) [state] {$13$};
    \node[circle, draw=black, thick] (13) at (288.0: 6cm) [state] {$14$};
    \node[circle, draw=black, thick] (14) at (312.0: 6cm) [state] {$15$};
    \node[circle, draw=black, thick] (15) at (336.0: 6cm) [state] {$16$};

    \node[circle, draw=black, thick] (5) at (0, 1) [state]   {$6$};

    \coordinate[right of=0] (s);

    \draw (s) edge[out=180, in=0, ->, thick] node [above] {$C$} (0);

	\draw (0) edge[out=-135, in=-45, ->, thick] node [above left, xshift=-5.5cm, yshift=1.7cm, rotate=-45] {$C/C$} (8);
	\draw (0) edge[out=180, in=-90, ->, thick] node [below, xshift=-1.8cm,yshift=3.2cm, rotate=90] {$D/D$} (3);

    \draw (1) edge[out=180, in=90, ->, thick] node [above, rotate=90] {$C/C$} (13);     
    \draw (1) edge[out=-90, in=90, ->, thick] node [above, yshift=1cm, rotate=90] {$D/D$} (15);

    \draw (2) edge[out=-135, in=90, ->, thick] node [above, rotate=90, xshift=-4.5cm, yshift=0.3cm] {$C/C$} (12);     
    \draw (2) edge[out=90, in=0, ->, thick] node [above right] {$D/D$} (3);

    \draw (3) edge[out=180, in=90, ->, thick] node [above right, xshift=3.8cm, yshift=3cm] {$C/C$} (10);     
    \draw (3) edge[out=45, in=90, ->, thick, loop] node [above] {$D/D$} (3);

    \draw (4) edge[out=-90, in=90, ->, thick] node [above, rotate=90] {$C/D$} (5);      
    \draw (4) edge[out=45, in=90, ->, thick, loop] node [above] {$D/D$} (4);

    \draw (5) edge[out=135, in=-135, ->, thick] node [above, rotate=90] {$C/D$} (4);      
    \draw (5) edge[out=-135, in=15, ->, thick] node [below, rotate=45] {$D/D$} (10);

    \draw (6) edge[out=-115, in=45, ->, thick] node [above left, xshift=-0.8cm, yshift=-0.7cm, rotate=45] {$C/C$} (8);      
    \draw (6) edge[out=45, in=90, ->, thick, loop] node [above] {$D/D$} (6);

    \draw (8) edge[out=0, in=180, ->, thick] node [above, xshift=4cm, yshift=1.6cm] {$C/C$} (2);      
    \draw (8) edge[out=25, in=-155, ->, thick] node [above, xshift=1.8cm, yshift=2cm] {$D/D$} (4);

    \draw (10) edge[out=45, in=-110, ->, thick] node [above, rotate=75] {$C/D$} (4);     
    \draw (10) edge[out=0, in=-135, ->, thick] node [below, xshift=-4cm, yshift=-1.7cm] {$D/D$} (1);

    \draw (11) edge[out=75, in=135, ->, thick] node [above right, xshift=2.5cm, yshift=-1.2cm, rotate=-45] {$C/D$} (14);    
    \draw (11) edge[out=45, in=135, ->, thick] node [above left] {$D/C$} (13);

    \draw (12) edge[out=-45, in=-135, ->, thick] node [below] {$C/C$} (13);    
    \draw (12) edge[out=45, in=-75, ->, thick] node [above, rotate=65] {$D/C$} (2);

    \draw (13) edge[out=0, in=45, ->, thick, loop] node [above] {$C/C$} (13);    
    \draw (13) edge[out=115, in=-75, ->, thick] node [above right, rotate= -65] {$D/C$} (6);

    \draw (14) edge[out=90, in=-65, ->, thick] node [above, yshift=-4cm, xshift=1cm, rotate=90] {$C/D$} (3);     
    \draw (14) edge[out=-90, in=-45, ->, thick] node [below right] {$D/D$} (13);

    \draw (15) edge[out=180, in=-90, ->, thick] node [above, xshift=3cm, yshift=-0.7cm] {$C/D$} (5);     
    \draw (15) edge[out=-90, in=-45, ->, thick, looseness=1.5] node [below] {$D/C$} (11);    
    \end{tikzpicture}
\end{document}

### 2017-07-08 main.tex
Add FSM diagrams to text.

@@
 Training this strategy corresponds to finding mappings of states and histories
-to an action and a state. Figures~\ref{} show two of the trained finite state
-machines...
-% TODO Update sentence above.
-% TODO Add diagrams of FSMs. Note how the strategies are called FSM 16 but as is
-% evident in the diagram, it is in fact a 14 state fsm.
+to an action and a state. Figure~\ref{fig:fsm_images} show two of the trained
+finite state machines. The layout of state nodes is kept the same between
+Figure~\ref{fig:fsm16} and~\ref{fig:fsm16noise} to highlight the effect of
+different training environments. Note also that two of the 16 states are not
+used, this is also an outcome of the training process.
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.5\textwidth}
+        \includestandalone[height=.3\textheight]{./assets/FSM16}
+        \caption{Evolved\_FSM\_16: trained to maximise score in a standard
+        tournament}
+        \label{fig:fsm16}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.5\textwidth}
+        \centering
+        \includestandalone[height=.3\textheight]{./assets/FSM16noise}
+        \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
+        noisy tournament}
+        \label{fig:fsm16noise}
+    \end{subfigure}%
+    \caption{Trained sixteen state finite state machine players}
+    \label{fig:fsm_images}
+\end{figure}
 

### 2017-07-08 main.tex
Add initial discussion about the results.
I've picked TfT to highlight what the data looks like.

@@
 
-\subsection{Standard Tournament}
+This section presents the results of a large IPD tournament with
+strategies from the Axelrod library, including some additional parametrized
+strategies (e.g.\ various parameter choices for Generous Tit For Tat). These are
+listed in Appendix~\ref{app:list_of_players}.
 
-We conducted a tournament with a large collection of strategies from the Axelrod
-library, including some additional parametrized strategies (e.g.\ various parameter
-choices for Generous Tit For Tat). These are listed in
-Appendix~\ref{app:list_of_players}.
-The top 11 performing strategies by median payoff are all strategies trained to maximize
-% TODO Potentially modify this as more repetitions are analysed.
-total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
-The next strategy is Desired Belief Strategy (DBS) \cite{Au2006}.
-which actively analyzes the opponent and responds
-accordingly. The next two strategies are Winner12, based on a lookup table,
-Fool Me Once, a grudging strategy that defects indefinitely on
-the second defection, and Omega Tit For Tat \cite{kendall2007iterated}.
 All strategies in the tournament follow a simple set of
@@
 on the last round of play, was omitted from the tournament presented here (but
-not from the training pool).
+not necessarily from the training pool).
+
+A total of \input{./assets/number_of_players.tex}are included, of which
+\input{./assets/number_of_stochastic_players.tex}are stochastic.  In
+Section~\ref{sec:standard} is concerned with the standard tournament with 200
+turns whereas in Section~\ref{sec:noisy} a tournament with 5\% noise is
+discussed. Due to the inherent stochasticity of these IPD tournaments, these
+tournament were repeated \input{./assets/standard_number_of_repetitions.tex}
+times. This allows for a detailed and confident analysis of the performance of
+strategies. To illustrate the results considered,
+Figure~\ref{fig:tit_for_tat_scores} shows the distribution of the mean score per
+turn of Tit For Tat over all the repetitions. Similarly,
+Figure~\ref{fig:tit_for_tat_ranks} shows the ranks of of Tit For Tat for each
+repetition (we note that it never wins a tournament). Finally
+Figure~\ref{fig:tit_for_tat_wins} shows the number of opponents beaten in any given
+tournament: Tit For Tat does not win any match (this is due to the fact that it
+will either draw with mutual cooperation or defect second).
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/standard_tft_scores.pdf}
+        \caption{Scores}
+        \label{fig:tit_for_tat_scores}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/standard_tft_ranks.pdf}
+        \caption{Ranks}
+        \label{fig:tit_for_tat_ranks}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./assets/standard_tft_wins.pdf}
+        \caption{Wins}
+        \label{fig:tit_for_tat_wins}
+    \end{subfigure}%
+
+    \caption{Results for Tit For Tat over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
+\end{figure}
+
+\subsection{Standard Tournament}\label{sec:standard}
+
+The top 11 performing strategies by median payoff are all strategies trained to maximize
+% TODO Potentially modify this as more repetitions are analysed.
+total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
+The next strategy is Desired Belief Strategy (DBS) \cite{Au2006}.
+which actively analyzes the opponent and responds
+accordingly. The next two strategies are Winner12, based on a lookup table,
+Fool Me Once, a grudging strategy that defects indefinitely on
+the second defection, and Omega Tit For Tat \cite{kendall2007iterated}.
 
@@
 
-\subsection{Noisy Tournament}
+\subsection{Noisy Tournament}\label{sec:noise}
 
@@
         of top 15 strategies (ranked by median wins over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{tbl:noisy_wins_top_winners}
@@
 The players used for this study are from Axelrod version 2.13.0
-\cite{axelrodproject}. The starred $*$
-strategies indicate those that have been trained using reinforcement learning
-algorithms.
+\cite{axelrodproject}.
 

### 2017-07-08 main.tex
Up size of one of the FSM diagrams slightly.
Add brief description of previous tournaments.
Please modify etc.

@@
 
-% TODO: discuss earlier tournaments
+Since Robert Axelrod's seminal tournament \cite{Axelrod1980a}, a number of
+IPD\@ tournaments have been undertaken and are summarised in
+Table~\ref{tbl:tournaments}. Further to the work described in
+\cite{knight2016open} a regular set of standard, noisy and probabilistic ending
+tournaments are carried out as more strategies are added to the Axelrod library.
+Details and results are available here:
+\url{http://axelrod-tournament.readthedocs.io}. This work presents a detailed
+analysis of a tournament with 176 strategies, more details about this are given
+in Section~\ref{sec:results}.
+
+\begin{table}[!hbtp]
+    \begin{center}
+        \begin{tabular}{ccccc}
+            \toprule
+            Year     & Reference                  & Number of Strategies & Type     & Source Code\\
+            \midrule
+            1979     & \cite{Axelrod1980a}        & 13                   & Standard & Not immediately available\\
+            1979     & \cite{Axelrod1980b}        & 64                   & Standard & Available in FORTRAN\\
+            1991     & \cite{Bendor1991}          & 13                   & Noisy    & Not immediately available\\
+            2002     & \cite{Stephens2002}        & 16                   & Wildlife & Not applicable\\
+            2005     & \cite{kendall2007iterated} & 223                  & Varied   & Not available \\
+            2012     & \cite{Stewart2012}         & 13                   & Standard & Not fully available \\
+            2016     & \cite{knight2016open}       & 129                  & Standard & Fully available \\
+            \bottomrule
+        \end{tabular}
+    \end{center}
+    \caption{An overview of a selection of published tournaments. Not all
+             tournaments were `standard' round robins; for more details
+             see the indicated references.}\label{tbl:tournaments}
+\end{table}
 
@@
 have been used to train new strategies specifically to win IPD tournaments.
-These strategies are trained using generic strategy archetypes based on e.g.
+These strategies are trained using generic strategy archetypes based on e.g.\
 finite state
@@
         \centering
-        \includestandalone[height=.3\textheight]{./assets/FSM16noise}
+        \includestandalone[height=.35\textheight]{./assets/FSM16noise}
         \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_EvolvedLookerUp2_2_2_array.pdf}
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_EvolvedLookerUp2_2_2_array.pdf}
         \caption{Cooperation rate per round for EvolvedLookerUp\_2\_2\_2 (over
-        20 repetitions)}
+        1000 repetitions)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_HMM_5_array.pdf}
-        \caption{Cooperation rate per round for Evolved\_HMM\_5 (over 20
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_Evolved_HMM_5_array.pdf}
+        \caption{Cooperation rate per round for Evolved\_HMM\_5 (over 1000
         repetitions)}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_FSM_16_array.pdf}
-        \caption{Cooperation rate per round for Evolved\_FSM\_16 (over 20
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_Evolved_FSM_16_array.pdf}
+        \caption{Cooperation rate per round for Evolved\_FSM\_16 (over 1000
         repetitions)}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_DBS_0-75_3_4_3_5_array.pdf}
-        \caption{Cooperation rate per round for DBS (over 20 repetitions)}
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_DBS_0-75_3_4_3_5_array.pdf}
+        \caption{Cooperation rate per round for DBS (over 1000 repetitions)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_ANN_5_Noise_05_array.pdf}
-        \caption{Cooperation rate per round for Evolved\_ANN\_5\_Noise\_05 (over 20
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_Evolved_ANN_5_Noise_05_array.pdf}
+        \caption{Cooperation rate per round for Evolved\_ANN\_5\_Noise\_05 (over 1000
         repetitions)}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_FSM_16_Noise_05_array.pdf}
-        \caption{Cooperation rate per round for Evolved\_FSM\_16\_Noise\_05 (over 20
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_Evolved_FSM_16_Noise_05_array.pdf}
+        \caption{Cooperation rate per round for Evolved\_FSM\_16\_Noise\_05 (over 1000
         repetitions)}

### 2017-07-08 main.tex
Add more discussion to the results section.

@@
 
+The iterated prisoner's dilemma (IPD) is an area of game theoretic research
+aiming to understand the evolution of cooperative behaviour from complex
+dynamics \cite{Axelrod1984}.
+
 The Axelrod library \cite{axelrodproject, knight2016open} is an open source
-software for conducting iterated prisoner's dilemma (IPD) research with
+software for conducting IPD research with
 reproducibility as a principal goal. Written in the Python programming language,
@@
 Section~\ref{sec:standard} is concerned with the standard tournament with 200
-turns whereas in Section~\ref{sec:noisy} a tournament with 5\% noise is
+turns whereas in Section~\ref{sec:noise} a tournament with 5\% noise is
 discussed. Due to the inherent stochasticity of these IPD tournaments, these
@@
 
+The utilities used are \((R, P, T, S)=(3, 1, 5, 0)\) thus the specific
+Prisoner's Dilemma being played is:
+
+\begin{equation}\label{equ:pd}
+    \begin{pmatrix}
+        (3, 3) & (0, 5)\\
+        (5, 0) & (1, 1)
+    \end{pmatrix}
+\end{equation}
+
 \subsection{Standard Tournament}\label{sec:standard}
@@
         \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).
-        The leaderboard is dominated by the trained strategies. Starred
-        strategies $^{*}$
-        indicates that the strategy was trained.}
+        The leaderboard is dominated by the trained strategies (indicated by a
+        $^{*}$}
         \label{tbl:standard_score}
@@
 
-Violin plots showing the distribution of the scores of each strategy (again
-ranked by median score) are shown in Figure~\ref{fig:standard_boxplot}.
+For completeness, violin plots showing the distribution of the scores of each
+strategy (again ranked by median score) are shown in
+Figure~\ref{fig:standard_boxplot}.
 
@@
 Pairwise payoff results are given as a heatmap (Figure~\ref{fig:standard_heatmap})
-which shows that many strategies achieve mutual cooperation. The top performing
+which shows that many strategies achieve mutual cooperation (obtaining a score of 3). The top performing
 strategies never defect first yet are able to exploit weaker strategies that
@@
 
-The strategies that win the most matches are Defector, Aggravater, followed by
-handshaking and zero determinant strategies. This includes two handshaking
-strategies that were the result of training to maximize Moran process fixation.
-No strategies were trained specifically to win matches. None of the top scoring
-strategies appear in the top 20 list of strategies ranked by match wins.
-This can be seen in Figure~\ref{fig:standard_winplot} where the distribution of
-the number of wins of each strategy is shown.
+The strategies that win the most matches
+(Table~\ref{tbl:standard_wins_top_winners} are Defector and Aggravater, followed
+by handshaking and zero determinant strategies. This includes two handshaking
+strategies that were the result of training to maximize Moran process fixation
+(TF1 and TF2). No strategies were trained specifically to win matches. None of
+the top scoring strategies appear in the top 15 list of strategies ranked by
+match wins. This can be seen in Figure~\ref{fig:standard_winplot} where the
+distribution of the number of wins of each strategy is shown.
+
+\begin{table}[!hbtp]
+    \centering
+        \input{./assets/standard_top_15_winners_wins_summary.tex}
+        \caption{Standard Tournament: Number of wins per tournament
+        of top 15 strategies (ranked by median wins over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \label{tbl:standard_wins_top_winners}
+\end{table}
 
@@
         \label{tbl:standard_wins}
-\end{table}
-
-Table~\ref{tbl:standard_wins_top_winners} shows the same information as
-Table~\ref{tbl:standard_wins} but for the top 15 strategies who win the most
-head to head matches.
-% TODO Add more discussion?
-
-\begin{table}[!hbtp]
-    \centering
-        \input{./assets/standard_top_15_winners_wins_summary.tex}
-        \caption{Standard Tournament: Number of wins per tournament
-        of top 15 strategies (ranked by median wins over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
-        \label{tbl:standard_wins_top_winners}
 \end{table}
@@
 Figure~\ref{fig:comparison_cooperation_heatmaps_standard} shows the rate of
-cooperation in each round for the top three strategies.
-% TODO Discuss more? (If we want to keep this)
+cooperation in each round for the top three strategies. The opponents in these
+figures are ordered according to performance by median score. It is evident that
+the high performing strategies share a common thread against the top strategies:
+they do not defect first and achieve mutual cooperation. Against the lower
+strategies they also do not defect first (a mean cooperation rate of 1 in the
+first round) but do learn to quickly retaliate.
 
@@
 
-% TODO Update these with 10k repetition version
+% TODO Update these with 10k repetition version? (I have these for all but DBS)
 
@@
 
-We also ran noisy tournaments in which there is a 5\% chance that an action is
-flipped. As shown in Table~\ref{tbl:noisy_score} and
+Noisy tournaments in which there is a 5\% chance that an action is
+flipped are now described. As shown in Table~\ref{tbl:noisy_score} and
 Figure~\ref{fig:noisy_score}, the best performing strategies in median payoff
@@
 
-The strategies trained in the presence of noise are also among the best
-performers in the absence of noise. As shown in Figure~\ref{fig:noisy_heatmap}
-the cluster of mutually cooperative strategies is broken by the noise at 5\%. A
-similar collection of players excels at winning matches but again they have a
-poor total payoff.
+Recalling Table~\ref{tbl:standard_score}, the strategies trained in the presence
+of noise are also among the best performers in the absence of noise. As shown in
+Figure~\ref{fig:noisy_heatmap} the cluster of mutually cooperative strategies is
+broken by the noise at 5\%. A similar collection of players excels at winning
+matches but again they have a poor total payoff.
 
@@
 
-As shown in Figure~\ref{fig:noisy_winplot} the strategies tallying the most wins
-are somewhat similar, with Defector, the handshaking CollectiveStrategy, and
+As shown in Table~\ref{tbl_noisy_wins_top_winners} and
+Figure~\ref{fig:noisy_winplot} the strategies tallying the most wins are
+somewhat similar, with Defector, the handshaking CollectiveStrategy, and
 Aggravate appearing as the top three again.
+
+\begin{table}[!hbtp]
+    \centering
+        \input{./assets/noisy_top_15_winners_wins_summary.tex}
+        \caption{Noisy (5\%) Tournament: Number of wins per tournament
+        of top 15 strategies (ranked by median wins over
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
+        \label{tbl:noisy_wins_top_winners}
+\end{table}
 
@@
         \label{tbl:noisy_wins}
-\end{table}
-
-Table~\ref{tbl:noisy_wins_top_winners} shows the same information as
-Table~\ref{tbl:noisy_wins} but for the top 15 strategies who win the most
-head to head matches.
-% TODO Add more discussion?
-
-\begin{table}[!hbtp]
-    \centering
-        \input{./assets/noisy_top_15_winners_wins_summary.tex}
-        \caption{Noisy (5\%) Tournament: Number of wins per tournament
-        of top 15 strategies (ranked by median wins over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
-        \label{tbl:noisy_wins_top_winners}
 \end{table}
@@
 
-Again we compare the fingerprints. For the top performing noisy strategies
-(Figure~\ref{fig:comparison_fingerprint_noisy}) there
-is a striking similarity in the fingerprints which indicates that the strategies
+Similarly to Section~\ref{sec:standard} the top performing noisy strategies
+(Figure~\ref{fig:comparison_fingerprint_noisy}) have
+a striking similarity in the fingerprints which indicates that the strategies
 may behave similarly in principle.
@@
 Figure~\ref{fig:comparison_cooperation_heatmaps_noisy} shows the rate of
-cooperation in each round for the top three strategies.
-% TODO Add more discussion
+cooperation in each round for the top three strategies and just as for the top
+performing strategies in the standard tournament
+(Figure~\ref{fig:comparison_cooperation_heatmaps_standard}) it is evident that
+the strategies never defect first and learn to quickly punish poorer strategies.
 

### 2017-07-08 main.tex
Remove duplicates from bibliography.

@@
 previous tournament winners such as OmegaTFT \cite{slany2007some}, Adaptive
-Pavlov \cite{li2007design}, and ZDGTFT2 \cite{stewart2012extortion}.
+Pavlov \cite{li2007design}, and ZDGTFT2 \cite{Stewart2012}.
 
@@
 evolve IPD strategies in various circumstances
-\cite{ashlock2006training, ashlock2015multiple, ashlock2006changes,
-      ashlock2014shaped, ashlock2014evolution, barlow2015varying,
+\cite{ashlock2006training, Ashlock2015, Ashlock2006,
+      ashlock2014shaped, Ashlock2014, barlow2015varying,
       fogel1993evolving, marks1989niche, sudo2015effects,
-      vassiliades2010multiagent}. See also \cite{gaudesi2016exploiting} for a
+      vassiliades2010multiagent}. See also \cite{Gaudesi2016} for a
 strategy trained to win against a collection of well-known IPD opponents and see
@@
 Using a numerical method of fingerprinting based on
-\cite{ashlock2008fingerprinting, ashlock2009fingerprint} we can compare
+\cite{Ashlock2008, ashlock2009fingerprint} we can compare
 strategies. The fingerprints of the top performing standard strategies are shown

### 2017-07-08 main.tex
Modify the discussion.
I've changed this slightly based on our discussion.

The Lookerup and Gambler strategies don't do well in Noise so I think
there's something to be said there about the dimensions captured by the
various archetypes.

@@
 
-\subsection{LookerUp}
+\subsection{LookerUp}\label{sec:lookerup}
 
@@
 
-\subsection{Gambler}
+\subsection{Gambler}\label{sec:gambler}
 
@@
 
-\subsection{Finite State Machines}
+\subsection{Finite State Machines}\label{sec:fsm}
 
@@
 critical -- strategies based on lookup tables, finite state machines, and stochastic
-variants all performed well. Single layer neural networks also performed well
+variants all performed well for standard tournaments.
+Single layer neural networks (Section~\ref{sec:ann}) performed well in both
+noisy and standard
+tournaments
 though these had some aspect of human involvement in the selection of features.
-% TODO Question: is this arguably just as much human involvement in the design
-% of the lookup tables etc? We could use a lookup table that also picks out the
-% action from the middle round, however we have chosen not too.
-The success of the other strategy types suggests that a deeper network that
-incorporates feature engineering would likely also perform well.
+This is in line with the other strategies also where human decisions are made
+regarding the structure. For the LookerUp and Gambler archetypes
+(Sections~\ref{sec:lookerup} and~\ref{sec:gambler})
+a decision has to be made
+regarding the number of turns of history and initial play that are to be used.
+Whilst, the Finite state machines and Hidden Markov models
+(Sections\ref{sec:fsm} and~\ref{sec:hmm}) also need input from a
+human as to the number of states to use they are much more of a black box and
+thus offer wider adaptability.
+
+A lot of strategies could be represented by many archetypes, however some
+archetypes will be far more efficient in doing so than
+others. The fact that the Lookerup strategy does the best for the standard
+tournament indicates that it represents an efficient reduction of
+dimension which in turn makes its training more efficient. For the noisy
+tournament however the dimension reduction represented by some archetypes
+indicates that sufficient features are not captured by the Lookup tables whilst
+they are by the
+neural network and the finite state machine allowing them to adapt to the noisy
+environment.
 

### 2017-07-09 main.tex
Add a place holder for when the data is archived.
Update with final data.
Include some minor tweaks.

@@
     the trained strategies win standard tournaments against the total collection
-    of other opponents. We also trained variants to win noisy tournaments.
+    of other opponents. Variants were also trained to win noisy tournaments.
 \end{abstract}
@@
 
+All data generated for this work is archived and available...
+% TODO Add details once data is archived.
+
 \subsection{Standard Tournament}\label{sec:standard}
@@
 The top 11 performing strategies by median payoff are all strategies trained to maximize
-% TODO Potentially modify this as more repetitions are analysed.
 total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
@@
 
-% Table of best strategies
 \begin{table}[!hbtp]
@@
 (\(60/175\approx34\%\)) matches in a given tournament.
-% TODO Update this when more data comes in.
 
@@
         \includegraphics[width=\textwidth]{./assets/EvolvedLookerUp2_2_2.png}
-        \caption{Fingerprint for EvolvedLookerUp\_2\_2\_2}
+        \caption{EvolvedLookerUp\_2\_2\_2}
     \end{subfigure}%
@@
         \includegraphics[width=\textwidth]{./assets/Evolved_HMM_5.png}
-        \caption{Fingerprint for Evolved\_HMM\_5}
+        \caption{Evolved\_HMM\_5}
     \end{subfigure}%
@@
         \includegraphics[width=\textwidth]{./assets/Evolved_FSM_16.png}
-        \caption{Fingerprint for Evolved\_FSM\_16}
+        \caption{Evolved\_FSM\_16}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_EvolvedLookerUp2_2_2_array.pdf}
-        \caption{Cooperation rate per round for EvolvedLookerUp\_2\_2\_2 (over
-        1000 repetitions)}
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.pdf}
+        \caption{EvolvedLookerUp\_2\_2\_2}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_Evolved_HMM_5_array.pdf}
-        \caption{Cooperation rate per round for Evolved\_HMM\_5 (over 1000
-        repetitions)}
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_HMM_5_array.pdf}
+        \caption{Evolved\_HMM\_5}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_Evolved_FSM_16_array.pdf}
-        \caption{Cooperation rate per round for Evolved\_FSM\_16 (over 1000
-        repetitions)}
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_FSM_16_array.pdf}
+        \caption{Evolved\_FSM\_16}
     \end{subfigure}%
 
-    \caption{Comparison of collaboration rates for Standard Tournament Top 3}
+    \caption{Comparison of collaboration rates for Standard Tournament Top 3
+    (over 10000 repetitions)}
     \label{fig:comparison_cooperation_heatmaps_standard}
 \end{figure}
-
-% TODO Update these with 10k repetition version? (I have these for all but DBS)
 
@@
 
-As shown in Table~\ref{tbl_noisy_wins_top_winners} and
+As shown in Table~\ref{tbl:noisy_wins_top_winners} and
 Figure~\ref{fig:noisy_winplot} the strategies tallying the most wins are
-somewhat similar, with Defector, the handshaking CollectiveStrategy, and
-Aggravate appearing as the top three again.
+somewhat similar to the Standard tournaments, with Defector, the handshaking
+CollectiveStrategy, and Aggravate appearing as the top three again.
 
@@
         \includegraphics[width=\textwidth]{./assets/DBS.png}
-        \caption{Fingerprint for DBS}
+        \caption{DBS}
     \end{subfigure}%
@@
         \includegraphics[width=\textwidth]{./assets/Evolved_ANN_5_Noise_05.png}
-        \caption{Fingerprint for Evolved\_ANN\_5\_Noise\_05}
+        \caption{Evolved\_ANN\_5\_Noise\_05}
     \end{subfigure}%
@@
         \includegraphics[width=\textwidth]{./assets/Evolved_FSM_16_Noise_05.png}
-        \caption{Fingerprint for Evolved\_FSM\_16\_Noise\_05}
+        \caption{Evolved\_FSM\_16\_Noise\_05}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_DBS_0-75_3_4_3_5_array.pdf}
-        \caption{Cooperation rate per round for DBS (over 1000 repetitions)}
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.pdf}
+        \caption{DBS}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_Evolved_ANN_5_Noise_05_array.pdf}
-        \caption{Cooperation rate per round for Evolved\_ANN\_5\_Noise\_05 (over 1000
-        repetitions)}
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.pdf}
+        \caption{Evolved\_ANN\_5\_Noise\_05}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_1000_Evolved_FSM_16_Noise_05_array.pdf}
-        \caption{Cooperation rate per round for Evolved\_FSM\_16\_Noise\_05 (over 1000
-        repetitions)}
+        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.pdf}
+        \caption{Evolved\_FSM\_16\_Noise\_05}
     \end{subfigure}%
 
-    \caption{Comparison of collaboration rates for Noisy (5\%) Tournament Top 3}
+    \caption{Comparison of collaboration rates for Noisy (5\%) Tournament Top 3
+    (over 10000 tournaments)}
     \label{fig:comparison_cooperation_heatmaps_noisy}
 \end{figure}
-
-% TODO Update these with 10k repetition version
 

### 2017-07-09 main.tex
Add a todo.
Various edits

@@
 reproducibility as a principal goal. Written in the Python programming language,
-to date over the library contains source code contributed by over 50 individuals
+to date the library contains source code contributed by over 50 individuals
 from a variety of geographic locations and technical backgrounds. The library
@@
 are correctly implemented, tested and documented.
-Moreover, as of the time of writing,
-we claim that this work contains the best known strategies for the iterated
-prisoner's dilemma.
+Moreover, as of the time of writing, we claim that this work contains the best
+performing strategies for the iterated prisoner's dilemma.
 
@@
 Training of these strategies will be discussed in Section~\ref{sec:methods}.
-
 These strategies can encode a variety
@@
 an opponent defection.
-
-The various archetypes will be described in the following sections.
 
@@
 
-Training of this strategy corresponds to finding maps from histories to either a
-cooperation or a defection.
-
-Although various
+Training of this strategy corresponds to finding maps from partial histories to
+either a cooperation or a defection. Although various
 combinations of $n_1, m_1,$ and $m_2$ have been tried, the best performance at
@@
 Training of this strategy corresponds to finding maps from histories to
-a probability of cooperation.
-
-The library includes a strategy trained
+a probability of cooperation. The library includes a strategy trained
 with $n_1 = m_1 = m_2 = 2$ that is \emph{mostly deterministic}, with most of the
@@
 
-\subsection{ANN: Single Layer Artificial Neural Network}
+\subsection{ANN: Single Hidden Layer Artificial Neural Network}
 
@@
 Training of this strategy corresponds to finding parameters of the neural
-network.
-
-An inner layer with just five nodes performs quite well in both deterministic and
+network. An inner layer with just five nodes performs quite well in both deterministic and
 noisy tournaments. The output of the ANN used in this work is deterministic;
@@
 probabilities at each state. This is
-shown diagrammatically in Figure~\ref{fig:hmm}.
+shown diagrammatically in Figure~\ref{fig:hmm}. Training this strategy
+corresponds to finding mappings of states and histories to probabilities of
+cooperating as well as probabilities of the next internal state.
 
@@
 
-Training this strategy corresponds to finding mappings of states and histories
-to probabilities of cooperating as well as probabilities of the next internal
-state.
-
-These are the best performing stochastic strategies
-in the library but take longer to train due to their stochasticity.
-
 \subsection{Meta Strategies}
 
-Last but not least there are several strategies based on ensemble methods that
+There are several strategies based on ensemble methods that
 are common in machine learning called Meta strategies. These strategies are
@@
 in the case of MetaWinner. These strategies were among the best in the library
-before the inclusion of those trained by reinforcement learning.
+before the inclusion of those trained by reinforcement learning. The library
+contains strategies containing teams of all the deterministic players, all the
+memory-one players, and some others.
 
@@
 on which they are based, including using the match length to defect on the last
-rounds of play, not all of these strategies were included in results of this
-paper.
+round(s) of play, not all of these strategies were included in results of this
+paper. These strategies do not typically outperform the trained strategies
+described above.
 
@@
 % TODO Add details once data is archived.
+% TODO Include url to repo etc.
 
@@
         The leaderboard is dominated by the trained strategies (indicated by a
-        $^{*}$}
+        $^{*}$)}
         \label{tbl:standard_score}
@@
 opponents. An evolutionary algorithm produces strategies based on multiple
-standard machine learning techniques that are able to achieve a higher average
+generic archetypes that are able to achieve a higher average
 score than any other known opponent in a standard tournament. Most of the trained
 strategies use multiple rounds of the history of play (some using all of it) and
-outperform memory-one strategies (though the trained memory one strategy performs
-well). The generic structure of the trained strategies did not appear to be
-critical -- strategies based on lookup tables, finite state machines, and stochastic
-variants all performed well for standard tournaments.
+outperform memory-one strategies from the literature. Interestingly, a trained
+memory one strategy produced by a particle swarm algorithm performs well, better
+than human designed strategies such as Win Stay Lose Shift and zero determinant
+strategies (which enforce a payoff difference rather than maximize total payoff).
+The generic structure of the trained strategies did not appear to be
+critical for the standard tournament -- strategies based on lookup tables,
+finite state machines, neural networks, and stochastic variants all performed well.
 Single layer neural networks (Section~\ref{sec:ann}) performed well in both
-noisy and standard
-tournaments
+noisy and standard tournaments
 though these had some aspect of human involvement in the selection of features.
-This is in line with the other strategies also where human decisions are made
+This is in line with the other strategies also where some human decisions are made
 regarding the structure. For the LookerUp and Gambler archetypes
@@
 regarding the number of turns of history and initial play that are to be used.
-Whilst, the Finite state machines and Hidden Markov models
-(Sections\ref{sec:fsm} and~\ref{sec:hmm}) also need input from a
-human as to the number of states to use they are much more of a black box and
-thus offer wider adaptability.
+In contrast, the finite state machines and hidden Markov models
+(Sections\ref{sec:fsm} and~\ref{sec:hmm}) required only a choice of the number
+of states, and the training algorithm can eliminate unneeded states in the case
+of finite state machines (evidenced by the unconnected nodes in the diagrams
+for the included representations).
 
-A lot of strategies could be represented by many archetypes, however some
-archetypes will be far more efficient in doing so than
-others. The fact that the Lookerup strategy does the best for the standard
+Many strategies can be represented by multiple archetypes, however some
+archetypes will be more efficient in encoded the patterns present in the data.
+The fact that the Lookerup strategy does the best for the standard
 tournament indicates that it represents an efficient reduction of
-dimension which in turn makes its training more efficient. For the noisy
+dimension which in turn makes its training more efficient. In particular the
+first rounds of play were valuable bit of information. For the noisy
 tournament however the dimension reduction represented by some archetypes
-indicates that sufficient features are not captured by the Lookup tables whilst
-they are by the
-neural network and the finite state machine allowing them to adapt to the noisy
-environment.
+indicates that some features of the data are not captured by the lookup
+tables while they are by the neural network and the finite state machine,
+allowing them to adapt better to the noisy environment. Intuitively, a noisy
+environment can significantly affect a lookup table based on the last two rounds
+of play since these action pairs compete with probing defections, apologies, and
+retaliations. Accordingly, it is not surprising that additional parameter space
+is needed to adapt to a noisy environment.
 
@@
 our results show that complex strategies can be very effective for the
-IPD\@. It is not the complexity of strategies that is disadvantageous; rather that directly
-designing a broadly effective strategy is no easy task. Of all the human-designed
+IPD\@. Designing complex strategies for the prisoner's dilemma appears to be
+difficult for humans. Of all the human-designed
 strategies in the library, only DBS consistently performs well, and it is
@@
 DBS and OmegaTFT, perform well and only DBS performs better than the trained
-strategies and \textbf{only} in the noisy context.
+strategies and \textbf{only} in some noisy contexts. Empirically we find that
+DBS (with its default parameters) does not win tournaments at 1% noise.
+However DBS has a parameter that accounts for the expected amount of noise and a
+followup study with various noise levels could make a more complete study of
+the performance of DBS and strategies trained at various noise levels.
 
-Of the strategies trained to maximize their average score all are generally
-cooperative, not defecting until the opponent defects. Maximizing for individual
+The strategies trained to maximize their average score are generally
+cooperative and do not defect first. Maximizing for individual
 performance across a collection of opponents leads to mutual cooperation despite
@@
 payoff does not lead to exploitative zero determinant strategies, which may also
-be a result of the collection of training strategies, of which several retaliate harshly.
+be a result of the collection of training strategies, of which several retaliate
+harshly. Training with the objective of maximizing payoff difference may
+produce strategies more like zero determinant strategies.
 
-We take the liberty of generalizing from the results of this study. For the trained
+For the trained
 strategies utilizing look up tables we generally found those that incorporate
@@
 that first impressions matter in the IPD\@. The best strategies are nice (never
-defecting first) and this property could be further investigated with the
-Axelrod library
+defecting first) and the impact of the first rounds of play could be further
+investigated with the Axelrod library
 in future work by e.g.\ forcing all strategies to defect on the first round.
@@
 Finally, we note that as the library grows, the top performing strategies
-sometimes shuffle, and are not retrained regularly. Most of the strategies were
+sometimes shuffle, and are not retrained automatically. Most of the strategies were
 trained on an earlier version of the library (v2.2.0: \cite{axelrodproject2.2})
@@
 machines with fewer states may suffice. See \cite{ashlock2013impact} for
-discussion of resource availability for IPD strategies. It may be possible to
-train strategies more effective in noisy tournaments than DBS.
-
-Future work:
-% TODO Write the future work section
-%* spatial tournaments and other variants
-%* Additional strategy archetypes by the Ashlocks, e.g. function stacks, binary
-%decision players
-%* further refine features and training parameters
+discussion of resource availability for IPD strategies.
 

### 2017-07-10 main.tex

@@
 Many strategies can be represented by multiple archetypes, however some
-archetypes will be more efficient in encoded the patterns present in the data.
+archetypes will be more efficient in encoding the patterns present in the data.
 The fact that the Lookerup strategy does the best for the standard

### 2017-07-10 main.tex
Use plasma colormap for heatmaps.
Closes #7.
Add co authors.
I haven't removed the TODO, just waiting on Owen to confirm he's OK to
be named as an author.
Remove fingerprints.
We were not saying much about these and they were not offering much
because of the difficulty of interpretation. I think the collaboration
heatmaps are better.

@@
 Iterated Prisoner's Dilemma}
-\author{Marc Harper \and Vincent Knight} % TODO Authors
+\author{Marc Harper \and
+        Vincent Knight \and
+        Martin Jones \and
+        Georgios Koutsovoulos \and
+        Nikoleta Glynatsi} % TODO Authors
 \date{}
@@
 
-Using a numerical method of fingerprinting based on
-\cite{Ashlock2008, ashlock2009fingerprint} we can compare
-strategies. The fingerprints of the top performing standard strategies are shown
-in Figures~\ref{fig:comparison_fingerprint_standard}. There is a striking
-similarity in the fingerprints.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./assets/EvolvedLookerUp2_2_2.png}
-        \caption{EvolvedLookerUp\_2\_2\_2}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./assets/Evolved_HMM_5.png}
-        \caption{Evolved\_HMM\_5}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./assets/Evolved_FSM_16.png}
-        \caption{Evolved\_FSM\_16}
-    \end{subfigure}%
-
-    \caption{Comparison of Fingerprints for Standard Tournament Top 3}
-    \label{fig:comparison_fingerprint_standard}
-\end{figure}
-
 Figure~\ref{fig:comparison_cooperation_heatmaps_standard} shows the rate of
@@
 
-Similarly to Section~\ref{sec:standard} the top performing noisy strategies
-(Figure~\ref{fig:comparison_fingerprint_noisy}) have
-a striking similarity in the fingerprints which indicates that the strategies
-may behave similarly in principle.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./assets/DBS.png}
-        \caption{DBS}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./assets/Evolved_ANN_5_Noise_05.png}
-        \caption{Evolved\_ANN\_5\_Noise\_05}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./assets/Evolved_FSM_16_Noise_05.png}
-        \caption{Evolved\_FSM\_16\_Noise\_05}
-    \end{subfigure}%
-
-    \caption{Comparison of Fingerprints for Noisy (5\%) Tournament Top 3}
-    \label{fig:comparison_fingerprint_noisy}
-\end{figure}
-
 Figure~\ref{fig:comparison_cooperation_heatmaps_noisy} shows the rate of
@@
 
-    \caption{Comparison of collaboration rates for Noisy (5\%) Tournament Top 3
-    (over 10000 tournaments)}
+    \caption{Comparison of collaboration rates for the Noisy (5\%) Tournament Top 3
+    (over 10000 standard tournaments)}
     \label{fig:comparison_cooperation_heatmaps_noisy}
@@
 
+% TODO Add citations to software used.
+
 \printbibliography

### 2017-07-10 main.tex
Address @mojones comments.
Note I did not address:

>  page 3 "parameters of the neural network" should this be "weights of
the neural network" to match convention

I feel that parameters is fine but I'm easy.

@@
 
-The LookerUp strategy is based on a lookup tables and  encodes a set of
+The LookerUp strategy is based on a lookup table and  encodes a set of
 deterministic responses based on the opponent's first $n_1$ moves, the
 opponent's last $m_1$ moves, and the players last $m_2$ moves. If $n_1 > 0$ then
-the player has infinite memory depth, otherwise it has depth $\max{m_1, m_2}$.
+the player has infinite memory depth, otherwise it has depth $\max(m_1, m_2)$.
 This is illustrated diagrammatically in Figure~\ref{fig:lookerup}.
@@
 This strategy type can be used to train arbitrary memory-$n$ strategies. A
-memory one strategy called PSO Gambler Mem 1 was trained, with
+memory one strategy called PSOGamblerMem1 was trained, with
 probabilities $(\text{Pr}(\text{C}\;|\;\text{CC}),
@@
 Training this strategy corresponds to finding mappings of states and histories
-to an action and a state. Figure~\ref{fig:fsm_images} show two of the trained
+to an action and a state. Figure~\ref{fig:fsm_images} shows two of the trained
 finite state machines. The layout of state nodes is kept the same between
@@
     \begin{subfigure}[t]{.5\textwidth}
-        \includestandalone[height=.3\textheight]{./assets/FSM16}
+        \includegraphics[height=.3\textheight]{./assets/FSM16.pdf}
         \caption{Evolved\_FSM\_16: trained to maximise score in a standard
@@
         \centering
-        \includestandalone[height=.35\textheight]{./assets/FSM16noise}
+        \includegraphics[height=.35\textheight]{./assets/FSM16noise.pdf}
         \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
@@
 (HMMs). Like the strategies based on finite state machines, these strategies
-also encode an internal state however use probabilistic transitions based on the
+also encode an internal state. However, they use probabilistic transitions based on the
 prior round of play to other states and cooperate or defect with various
@@
 
-    \caption{Comparison of collaboration rates for Standard Tournament Top 3
+    \caption{Comparison of cooperation rates for Standard Tournament Top 3
     (over 10000 repetitions)}
@@
 of each strategy over the repeated tournaments. We see that the stochasticity
-of the ranks understandably increases the DBS strategy never ranks lower than
+of the ranks understandably increases relative to the Standard tournament. An
+exception is the top three strategies, for example, the DBS strategy never ranks
+lower than
 second and wins 75\% of the time. The two strategies trained for noisy
@@
 
-    \caption{Comparison of collaboration rates for the Noisy (5\%) Tournament Top 3
+    \caption{Comparison of cooperation rates for the Noisy (5\%) Tournament Top 3
     (over 10000 standard tournaments)}
@@
 The trained strategies (denoted by a \(^{*}\) in
-Appendix~\ref{app:list_of_players} were trained using reinforcement
+Appendix~\ref{app:list_of_players}) were trained using reinforcement
 learning algorithms. The ideas of reinforcement learning can be attributed to

### 2017-07-11 main.tex
Edit abstract

@@
     trained to perform well against a corpus of over 170 distinct
-    opponents, including many well-known strategies from the literature. All
+    opponents, including many well-known and classic strategies. All
     the trained strategies win standard tournaments against the total collection
-    of other opponents. Variants were also trained to win noisy tournaments.
+    of other opponents. Variants are also trained to win noisy tournaments.
 \end{abstract}

### 2017-07-11 main.tex
Various Minor Edits

@@
 
-The iterated prisoner's dilemma (IPD) is an area of game theoretic research
-aiming to understand the evolution of cooperative behaviour from complex
+The iterated prisoner's dilemma (IPD) is a common model in game theory,
+frequently used  to understand the evolution of cooperative behaviour from complex
 dynamics \cite{Axelrod1984}.
 
-The Axelrod library \cite{axelrodproject, knight2016open} is an open source
-software for conducting IPD research with
+In this manuscript we use the Axelrod library \cite{axelrodproject, knight2016open},
+open source software for conducting IPD research with
 reproducibility as a principal goal. Written in the Python programming language,
@@
 is supported by a comprehensive test suite that covers all the intended
-behaviors of the strategies in the library, as well as the features that
+behaviors of all of the strategies in the library, as well as the features that
 conduct matches, tournaments, and population dynamics.
@@
 \url{http://axelrod-tournament.readthedocs.io}. This work presents a detailed
-analysis of a tournament with 176 strategies, more details about this are given
-in Section~\ref{sec:results}.
+analysis of a tournament with 176 strategies (details given
+in Section~\ref{sec:results}).
 
@@
 \cite{franken2005particle} for a prior use of particle swarm algorithms. Our
-results are unique in that we are able to train against a large collection of
-well-known strategies available in the scientific literature. Crucially, the
+results are unique in that we are able to train against a large and diverse
+collection of strategies available from the scientific literature.
+Crucially, the
 software used in this work is openly available and can be used to train strategies
@@
 Training of this strategy corresponds to finding maps from partial histories to
-either a cooperation or a defection. Although various
+actions, either a cooperation or a defection. Although various
 combinations of $n_1, m_1,$ and $m_2$ have been tried, the best performance at
@@
 parameters $n_1=0$ and $m_1=m_2=n$. For $n=1$, the resulting strategy cooperates
-if the last round was mutual cooperation and defects otherwise.
+if the last round was mutual cooperation and defects otherwise, known as Grim or
+Grudger.
 
@@
 a probability of cooperation. The library includes a strategy trained
-with $n_1 = m_1 = m_2 = 2$ that is \emph{mostly deterministic}, with most of the
+with $n_1 = m_1 = m_2 = 2$ that is \emph{mostly deterministic}, with 12 of the 64
 probabilities being 0 or 1. At one time this strategy outperformed
@@
 Table~\ref{tbl:standard_score})
-it is not as good as the longer memory strategies, and is bested by a similar
+it does not outperform the longer memory strategies, and is bested by a similar
 strategy that also uses the first round of play: PSOGambler\_1\_1\_1.
@@
 Because these strategies inherit many of the properties of the strategies
-on which they are based, including using the match length to defect on the last
-round(s) of play, not all of these strategies were included in results of this
+on which they are based, including using knowledge of the match length to defect
+on the last round(s) of play, not all of these
+strategies were included in results of this
 paper. These strategies do not typically outperform the trained strategies
@@
 Pairwise payoff results are given as a heatmap (Figure~\ref{fig:standard_heatmap})
-which shows that many strategies achieve mutual cooperation (obtaining a score of 3). The top performing
+which shows that many strategies achieve mutual cooperation (obtaining a score
+of 3). The top performing
 strategies never defect first yet are able to exploit weaker strategies that
@@
 stochasticity, the top three strategies almost always rank in the top three. For
-example, the worst that the Evolved Lookerup 2 2 2 ranks in a given tournament
+example, the worst that the Evolved Lookerup 2 2 2 ranks in any tournament
 is 8th.
@@
 Figure~\ref{fig:noisy_score}, the best performing strategies in median payoff
-are DBS, designed to correct for noise, followed by two strategies trained in
+are DBS, designed to account for noise, followed by two strategies trained in
 the presence of noise and three trained strategies trained without noise. One of
@@
 Figure~\ref{fig:noisy_winplot} the strategies tallying the most wins are
-somewhat similar to the Standard tournaments, with Defector, the handshaking
+somewhat similar to the standard tournaments, with Defector, the handshaking
 CollectiveStrategy, and Aggravate appearing as the top three again.
@@
 of each strategy over the repeated tournaments. We see that the stochasticity
-of the ranks understandably increases relative to the Standard tournament. An
+of the ranks understandably increases relative to the standard tournament. An
 exception is the top three strategies, for example, the DBS strategy never ranks
@@
 Figure~\ref{fig:comparison_cooperation_heatmaps_noisy} shows the rate of
-cooperation in each round for the top three strategies and just as for the top
-performing strategies in the standard tournament
+cooperation in each round for the top three strategies (in the absense of noise)
+and just as for the top performing strategies in the standard tournament
 (Figure~\ref{fig:comparison_cooperation_heatmaps_standard}) it is evident that
@@
 
-The Particle Swarm Algorithm is implemented using the Python library:
+The Particle Swarm Algorithm is implemented using the pyswarm library:
 \url{https://pypi.python.org/pypi/pyswarm}. This algorithm was used only to
@@
 further modified to suit other purposes. New strategies could be trained with
-variations including spatial structure, and probabilistically ending matches.
+variations including spatial structure and probabilistically ending matches.
 
@@
 a decision has to be made
-regarding the number of turns of history and initial play that are to be used.
+regarding the number of rounds of history and initial play that are to be used.
 In contrast, the finite state machines and hidden Markov models
@@
 dimension which in turn makes its training more efficient. In particular the
-first rounds of play were valuable bit of information. For the noisy
+first rounds of play were valuable bits of information. For the noisy
 tournament however the dimension reduction represented by some archetypes
 indicates that some features of the data are not captured by the lookup
-tables while they are by the neural network and the finite state machine,
-allowing them to adapt better to the noisy environment. Intuitively, a noisy
+tables while they are by the neural networks and the finite state machines,
+allowing the latter to adapt better to the noisy environment. Intuitively, a noisy
 environment can significantly affect a lookup table based on the last two rounds
@@
 that are optimal will depend on the pool of opponents. Moreover we have not
-extensively trained strategies to determine the minimum parameters that are
+extensively trained strategies to determine the minimum parameter spaces that are
 sufficient -- neural networks with fewer nodes and features and finite state

### 2017-07-11 main.tex
Add acknowledgements to other libraries.

@@
 a probability of cooperation. The library includes a strategy trained
-with $n_1 = m_1 = m_2 = 2$ that is \emph{mostly deterministic}, with 12 of the 64
+with $n_1 = m_1 = m_2 = 2$ that is \emph{mostly deterministic}, with 52 of the 64
 probabilities being 0 or 1. At one time this strategy outperformed
@@
 
-% TODO Add citations to software used.
+A variety of software libraries have been used in this work:
+
+\begin{itemize}
+    \item The Axelrod library (IPD strategies and Tournaments)
+        \cite{axelrodproject}.
+    \item The matplotlib library (visualisation) \cite{hunter2007matplotlib}.
+    \item The pandas and numpy libraries (data manipulation)
+        \cite{mckinney2010data, walt2011numpy}.
+\end{itemize}
 

### 2017-07-11 src/players.py
Correct Grudger mem length in src.

@@ -1,5 +1,7 @@
 import axelrod as axl
 
+axl.Grudger.classifier["memory_depth"] = 1
+
 players = [s() for s in axl.strategies if "length"
            not in s.classifier["makes_use_of"]]
 parameterized_players = [axl.Random(0.1), axl.Random(0.3), axl.Random(0.7),

### 2017-07-12 main.tex

@@
         Georgios Koutsovoulos \and
-        Nikoleta Glynatsi} % TODO Authors
+        Nikoleta Glynatsi \and
+        Owen Campbell}
 \date{}
@@
 Spiteful TFT (TFT but defects indefinitely if the opponent defects twice
-consecutively) and OmegaTFT (also designed to handle noise).
+consecutively) and OmegaTFT (also designed to handle noise). While DBS is the clear
+winner, it comes at a 6x increased run time over Evolved FSM 16 Noise 05.
 

### 2017-07-14 main.tex
Update minor things.
- Fix percentage not appearing
- Tweak the abstract
- Consistant IPD
- Include some more references.

@@
     the trained strategies win standard tournaments against the total collection
-    of other opponents. Variants are also trained to win noisy tournaments.
+    of other opponents. The trained strategies and one particular human made
+    designed strategy are the top performers in noisy tournaments also.
 \end{abstract}
@@
 
-The iterated prisoner's dilemma (IPD) is a common model in game theory,
+The Iterated Prisoner's Dilemma (IPD) is a common model in game theory,
 frequently used  to understand the evolution of cooperative behaviour from complex
@@
 
-In this manuscript we use the Axelrod library \cite{axelrodproject, knight2016open},
+In this manuscript the Axelrod library \cite{knight2016open, axelrodproject},
 open source software for conducting IPD research with
-reproducibility as a principal goal. Written in the Python programming language,
+reproducibility as a principal goal, is used. Written in the Python programming language,
 to date the library contains source code contributed by over 50 individuals
@@
 Moreover, as of the time of writing, we claim that this work contains the best
-performing strategies for the iterated prisoner's dilemma.
+performing strategies for the Iterated Prisoner's Dilemma.
 
@@
 These strategies can encode a variety
-of other strategies, including classic strategies like Tit For Tat,
+of other strategies, including classic strategies like Tit For Tat
+\cite{Axelrod1980},
 handshake strategies, and grudging strategies that always defect after
@@
 strategies from the Axelrod library, including some additional parametrized
-strategies (e.g.\ various parameter choices for Generous Tit For Tat). These are
+strategies (e.g.\ various parameter choices for Generous Tit For Tat
+\cite{Gaudesi2016}). These are
 listed in Appendix~\ref{app:list_of_players}.
@@
 accordingly. The next two strategies are Winner12, based on a lookup table,
-Fool Me Once, a grudging strategy that defects indefinitely on
+Fool Me Once \cite{axelrodproject}, a grudging strategy that defects indefinitely on
 the second defection, and Omega Tit For Tat \cite{kendall2007iterated}.
@@
 tournaments rank in the top three 95\% of the time.
-% TODO Possibly update this with more data.
 
@@
 strategies and \textbf{only} in some noisy contexts. Empirically we find that
-DBS (with its default parameters) does not win tournaments at 1% noise.
+DBS (with its default parameters) does not win tournaments at 1\% noise.
 However DBS has a parameter that accounts for the expected amount of noise and a

### 2017-07-14 main.tex
abstract suggestion
add citation
Add reference for noisy and probabilistic ending.

@@
     of other opponents. The trained strategies and one particular human made
-    designed strategy are the top performers in noisy tournaments also.
+    designed strategy are the top performers in tournaments where also noise is introduced.
 \end{abstract}
@@
 Table~\ref{tbl:tournaments}. Further to the work described in
-\cite{knight2016open} a regular set of standard, noisy and probabilistic ending
-tournaments are carried out as more strategies are added to the Axelrod library.
+\cite{knight2016open} a regular set of standard, noisy~\cite{Bendor1991} and 
+probabilistic ending~\cite{Axelrod1980b} tournaments are carried out as more 
+strategies are added to the Axelrod library.
 Details and results are available here:

### 2017-07-14 main.tex
typos
corrected typos and mainly added `.` at the
figure/table captions.

@@
 \cite{Axelrod1980},
-handshake strategies, and grudging strategies that always defect after
+handshake strategies, and grudging strategies, that always defect after
 an opponent defection.
@@
     \includestandalone[height=.3\textheight]{./assets/lookerup}
-    \caption{Diagrammatic representation of the Looker up Archetype}
+    \caption{Diagrammatic representation of the Looker up Archetype.}
     \label{fig:lookerup}
@@
     \includestandalone[height=.3\textheight]{./assets/gambler}
-    \caption{Diagrammatic representation of the Gambler Archetype}
+    \caption{Diagrammatic representation of the Gambler Archetype.}
     \label{fig:gambler}
@@
     \includestandalone[height=.3\textheight]{./assets/ann}
-    \caption{Diagrammatic representation of the ANN Archetype}
+    \caption{Diagrammatic representation of the ANN Archetype.}
     \label{fig:ann}
@@
     \includestandalone[height=.3\textheight]{./assets/fsm}
-    \caption{Diagrammatic representation of the Finite state machine Archetype}
+    \caption{Diagrammatic representation of the Finite state machine Archetype.}
     \label{fig:fsm}
@@
     \end{subfigure}%
-    \caption{Trained sixteen state finite state machine players}
+    \caption{Trained sixteen state finite state machine players.}
     \label{fig:fsm_images}
@@
     \includestandalone[height=.3\textheight]{./assets/hmm}
-    \caption{Diagrammatic representation of the Hidden Markov Model Archetype}
+    \caption{Diagrammatic representation of the Hidden Markov Model Archetype.}
     \label{fig:hmm}
@@
 \begin{itemize}
-  \item Players are unaware of the number of turns in a match
-  \item Players carry no acquired state between matches
-  \item Players cannot observe the outcome of other matches
-  \item Players cannot identify their opponent by any label or identifier
-  \item Players cannot manipulate or inspect their opponents in any way
+  \item Players are unaware of the number of turns in a match.
+  \item Players carry no acquired state between matches.
+  \item Players cannot observe the outcome of other matches.
+  \item Players cannot identify their opponent by any label or identifier.
+  \item Players cannot manipulate or inspect their opponents in any way.
 \end{itemize}
@@
 total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
-The next strategy is Desired Belief Strategy (DBS) \cite{Au2006}.
+The next strategy is Desired Belief Strategy (DBS) \cite{Au2006},
 which actively analyzes the opponent and responds
@@
         The leaderboard is dominated by the trained strategies (indicated by a
-        $^{*}$)}
+        $^{*}$).}
         \label{tbl:standard_score}
@@
         over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
         \label{fig:standard_boxplot}
@@
     column players (ranked by median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
     \label{fig:standard_heatmap}
@@
 The strategies that win the most matches
-(Table~\ref{tbl:standard_wins_top_winners} are Defector and Aggravater, followed
-by handshaking and zero determinant strategies. This includes two handshaking
+(Table~\ref{tbl:standard_wins_top_winners}) are Defector~\cite{Axelrod1984} and Aggravater~\cite{axelrodproject}, followed
+by handshaking and zero determinant strategies~\cite{Press2012}. 
+This includes two handshaking
 strategies that were the result of training to maximize Moran process fixation
@@
         of top 15 strategies (ranked by median wins over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
         \label{tbl:standard_wins_top_winners}
@@
         median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
         \label{fig:standard_winplot}
@@
 
-The number of wins of the top strategies of Table~\ref{tbl:standard_wins} are
+The number of wins of the top strategies of Table~\ref{tbl:standard_wins_top_winners} are
 shown in Table~\ref{tbl:standard_wins}. It is evident that although these
@@
         of top 15 strategies (ranked by median score over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
         \label{tbl:standard_wins}
@@
         of top 15 strategies (ranked by median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
         \label{tbl:standard_ranks}
@@
         median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
         \label{fig:standard_ranks_boxplot}
@@
     \caption{Comparison of cooperation rates for Standard Tournament Top 3
-    (over 10000 repetitions)}
+    (over 10000 repetitions).}
     \label{fig:comparison_cooperation_heatmaps_standard}
@@
         over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
         \label{fig:noisy_score}
@@
     column players (ranked by median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
     \label{fig:noisy_heatmap}
@@
 somewhat similar to the standard tournaments, with Defector, the handshaking
-CollectiveStrategy, and Aggravate appearing as the top three again.
+CollectiveStrategy~\cite{Li2009}, and Aggravate appearing as the top three again.
 
@@
         of top 15 strategies (ranked by median wins over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
         \label{tbl:noisy_wins_top_winners}
@@
         median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
         \label{fig:noisy_winplot}
@@
 As shown in Table~\ref{tbl:noisy_wins}, the top ranking strategies win a larger
-number of matches in the presence of noise. For example Spiteful Tit For Tat in
-one tournament won almost all its matches (167).
+number of matches in the presence of noise. For example Spiteful Tit For Tat~\cite{Prison1998} 
+in one tournament won almost all its matches (167).
 
@@
         of top 15 strategies (ranked by median score over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
         \label{tbl:noisy_wins}
@@
         of top 15 strategies (ranked by median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
         \label{tbl:noisy_ranks}
@@
         median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
         \label{fig:noisy_ranks_boxplot}
@@
     \caption{Comparison of cooperation rates for the Noisy (5\%) Tournament Top 3
-    (over 10000 standard tournaments)}
+    (over 10000 standard tournaments).}
     \label{fig:comparison_cooperation_heatmaps_noisy}

### 2017-07-14 main.tex
swap item in list.
In the text swarm algorithm is explained first and then
evolutionary. I think the list should follow the same
order, the reading flow is better.
corrections
Typos and fix labels for chapters 4 and 5.

@@
 
-\subsection{ANN: Single Hidden Layer Artificial Neural Network}
+\subsection{ANN: Single Hidden Layer Artificial Neural Network}\label{sec:ann}
 
@@
 
-\subsection{Hidden Markov Models}
+\subsection{Hidden Markov Models}\label{sec:hmm}
 
@@
 \begin{itemize}
+    \item Particle Swarm Algorithm: \cite{imran2013overview}.
     \item Evolutionary algorithm: \cite{moriarty1999evolutionary}.
-    \item Particle Swarm Algorithm: \cite{imran2013overview}.
 \end{itemize}
@@
 \begin{itemize}
- \item total or mean payoff
- \item total or mean payoff difference (unused in this work)
+ \item total or mean payoff,
+ \item total or mean payoff difference (unused in this work),
  \item total Moran process wins (fixation probability). This lead to the
@@
 
-These can be used in Noisy or Standard environments (as evidenced by
-Sections~\ref{sec:standard} and~\ref{sec:noisy}). These objectives can be
+These can be used in noisy or standard environments (as evidenced by
+Sections~\ref{sec:standard} and~\ref{sec:noise}). These objectives can be
 further modified to suit other purposes. New strategies could be trained with

### 2017-07-14 main.tex
correct my name
vince corrections

@@
         Georgios Koutsovoulos \and
-        Nikoleta Glynatsi \and
+        Nikoleta E. Glynatsi \and
         Owen Campbell}
@@
     of other opponents. The trained strategies and one particular human made
-    designed strategy are the top performers in tournaments where also noise is introduced.
+    designed strategy are the top performers in noisy tournaments also.
 \end{abstract}
@@
 The strategies that win the most matches
-(Table~\ref{tbl:standard_wins_top_winners}) are Defector~\cite{Axelrod1984} and Aggravater~\cite{axelrodproject}, followed
+(Table~\ref{tbl:standard_score}) are Defector~\cite{Axelrod1984} and Aggravater~\cite{axelrodproject}, followed
 by handshaking and zero determinant strategies~\cite{Press2012}. 

### 2017-07-14 main.tex

@@
 The strategies that win the most matches
-(Table~\ref{tbl:standard_score}) are Defector~\cite{Axelrod1984} and Aggravater~\cite{axelrodproject}, followed
+(Table~\ref{tbl:standard_wins_top_winners}) are Defector~\cite{Axelrod1984} and Aggravater~\cite{axelrodproject}, followed
 by handshaking and zero determinant strategies~\cite{Press2012}. 
@@
 
-The number of wins of the top strategies of Table~\ref{tbl:standard_wins_top_winners} are
+The number of wins of the top strategies of Table~\ref{tbl:standard_score} are
 shown in Table~\ref{tbl:standard_wins}. It is evident that although these

### 2017-07-14 main.tex
Address Marc's comments.

@@
         Georgios Koutsovoulos \and
-        Nikoleta E. Glynatsi \and
+        Nikoleta Glynatsi \and
         Owen Campbell}
@@
 
-In this manuscript the Axelrod library \cite{knight2016open, axelrodproject},
+This manuscript uses the Axelrod library \cite{knight2016open, axelrodproject},
 open source software for conducting IPD research with
-reproducibility as a principal goal, is used. Written in the Python programming language,
+reproducibility as a principal goal. Written in the Python programming language,
 to date the library contains source code contributed by over 50 individuals
@@
 Table~\ref{tbl:tournaments}. Further to the work described in
-\cite{knight2016open} a regular set of standard, noisy~\cite{Bendor1991} and 
-probabilistic ending~\cite{Axelrod1980b} tournaments are carried out as more 
-strategies are added to the Axelrod library.
+\cite{knight2016open} a regular set of standard, noisy and probabilistic ending
+tournaments are carried out as more strategies are added to the Axelrod library.
 Details and results are available here:
@@
 \cite{Axelrod1980},
-handshake strategies, and grudging strategies, that always defect after
+handshake strategies, and grudging strategies that always defect after
 an opponent defection.
@@
     \includestandalone[height=.3\textheight]{./assets/lookerup}
-    \caption{Diagrammatic representation of the Looker up Archetype.}
+    \caption{Diagrammatic representation of the Looker up Archetype}
     \label{fig:lookerup}
@@
     \includestandalone[height=.3\textheight]{./assets/gambler}
-    \caption{Diagrammatic representation of the Gambler Archetype.}
+    \caption{Diagrammatic representation of the Gambler Archetype}
     \label{fig:gambler}
@@
 
-\subsection{ANN: Single Hidden Layer Artificial Neural Network}\label{sec:ann}
+\subsection{ANN: Single Hidden Layer Artificial Neural Network}
 
@@
     \includestandalone[height=.3\textheight]{./assets/ann}
-    \caption{Diagrammatic representation of the ANN Archetype.}
+    \caption{Diagrammatic representation of the ANN Archetype}
     \label{fig:ann}
@@
     \includestandalone[height=.3\textheight]{./assets/fsm}
-    \caption{Diagrammatic representation of the Finite state machine Archetype.}
+    \caption{Diagrammatic representation of the Finite State Machine Archetype}
     \label{fig:fsm}
@@
     \end{subfigure}%
-    \caption{Trained sixteen state finite state machine players.}
+    \caption{Trained sixteen state Finite State Machine players}
     \label{fig:fsm_images}
@@
 
-\subsection{Hidden Markov Models}\label{sec:hmm}
+\subsection{Hidden Markov Models}
 
@@
     \includestandalone[height=.3\textheight]{./assets/hmm}
-    \caption{Diagrammatic representation of the Hidden Markov Model Archetype.}
+    \caption{Diagrammatic representation of the Hidden Markov Model Archetype}
     \label{fig:hmm}
@@
 \begin{itemize}
-  \item Players are unaware of the number of turns in a match.
-  \item Players carry no acquired state between matches.
-  \item Players cannot observe the outcome of other matches.
-  \item Players cannot identify their opponent by any label or identifier.
-  \item Players cannot manipulate or inspect their opponents in any way.
+  \item Players are unaware of the number of turns in a match
+  \item Players carry no acquired state between matches
+  \item Players cannot observe the outcome of other matches
+  \item Players cannot identify their opponent by any label or identifier
+  \item Players cannot manipulate or inspect their opponents in any way
 \end{itemize}
@@
 total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
-The next strategy is Desired Belief Strategy (DBS) \cite{Au2006},
+The next strategy is Desired Belief Strategy (DBS) \cite{Au2006}.
 which actively analyzes the opponent and responds
@@
         The leaderboard is dominated by the trained strategies (indicated by a
-        $^{*}$).}
+        $^{*}$)}
         \label{tbl:standard_score}
@@
         over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{fig:standard_boxplot}
@@
     column players (ranked by median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
     \label{fig:standard_heatmap}
@@
 The strategies that win the most matches
-(Table~\ref{tbl:standard_wins_top_winners}) are Defector~\cite{Axelrod1984} and Aggravater~\cite{axelrodproject}, followed
-by handshaking and zero determinant strategies~\cite{Press2012}. 
-This includes two handshaking
+(Table~\ref{tbl:standard_wins_top_winners} are Defector and Aggravater, followed
+by handshaking and zero determinant strategies. This includes two handshaking
 strategies that were the result of training to maximize Moran process fixation
@@
         of top 15 strategies (ranked by median wins over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{tbl:standard_wins_top_winners}
@@
         median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{fig:standard_winplot}
@@
 
-The number of wins of the top strategies of Table~\ref{tbl:standard_score} are
+The number of wins of the top strategies of Table~\ref{tbl:standard_wins} are
 shown in Table~\ref{tbl:standard_wins}. It is evident that although these
@@
         of top 15 strategies (ranked by median score over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{tbl:standard_wins}
@@
         of top 15 strategies (ranked by median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{tbl:standard_ranks}
@@
         median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
         \label{fig:standard_ranks_boxplot}
@@
     \caption{Comparison of cooperation rates for Standard Tournament Top 3
-    (over 10000 repetitions).}
+    (over 10000 repetitions)}
     \label{fig:comparison_cooperation_heatmaps_standard}
@@
         over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{fig:noisy_score}
@@
     column players (ranked by median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
     \label{fig:noisy_heatmap}
@@
 somewhat similar to the standard tournaments, with Defector, the handshaking
-CollectiveStrategy~\cite{Li2009}, and Aggravate appearing as the top three again.
+CollectiveStrategy, and Aggravate appearing as the top three again.
 
@@
         of top 15 strategies (ranked by median wins over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{tbl:noisy_wins_top_winners}
@@
         median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{fig:noisy_winplot}
@@
 As shown in Table~\ref{tbl:noisy_wins}, the top ranking strategies win a larger
-number of matches in the presence of noise. For example Spiteful Tit For Tat~\cite{Prison1998} 
-in one tournament won almost all its matches (167).
+number of matches in the presence of noise. For example Spiteful Tit For Tat in
+one tournament won almost all its matches (167).
 
@@
         of top 15 strategies (ranked by median score over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{tbl:noisy_wins}
@@
         of top 15 strategies (ranked by median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{tbl:noisy_ranks}
@@
         median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
         \label{fig:noisy_ranks_boxplot}
@@
     \caption{Comparison of cooperation rates for the Noisy (5\%) Tournament Top 3
-    (over 10000 standard tournaments).}
+    (over 10000 standard tournaments)}
     \label{fig:comparison_cooperation_heatmaps_noisy}
@@
 \begin{itemize}
+    \item Evolutionary algorithm: \cite{moriarty1999evolutionary}.
     \item Particle Swarm Algorithm: \cite{imran2013overview}.
-    \item Evolutionary algorithm: \cite{moriarty1999evolutionary}.
 \end{itemize}
@@
 \begin{itemize}
- \item total or mean payoff,
- \item total or mean payoff difference (unused in this work),
+ \item total or mean payoff
+ \item total or mean payoff difference (unused in this work)
  \item total Moran process wins (fixation probability). This lead to the
@@
 
-These can be used in noisy or standard environments (as evidenced by
-Sections~\ref{sec:standard} and~\ref{sec:noise}). These objectives can be
+These can be used in Noisy or Standard environments (as evidenced by
+Sections~\ref{sec:standard} and~\ref{sec:noisy}). These objectives can be
 further modified to suit other purposes. New strategies could be trained with

### 2017-07-15 main.tex

--- 2017-07-14 main.tex
@@
     \includestandalone[height=.3\textheight]{./assets/fsm}
-    \caption{Diagrammatic representation of the Finite state machine Archetype.}
+    \caption{Diagrammatic representation of the Finite State Machine Archetype.}
     \label{fig:fsm}
@@
     \end{subfigure}%
-    \caption{Trained sixteen state finite state machine players.}
+    \caption{Trained sixteen state Finite State Machine players.}
     \label{fig:fsm_images}

### 2017-07-19 main.tex
Add affiliation and links to data.
Closes #13

@@
 \usepackage{fancyvrb}
+\usepackage{authblk}
 
@@
 Iterated Prisoner's Dilemma}
-\author{Marc Harper \and
-        Vincent Knight \and
-        Martin Jones \and
-        Georgios Koutsovoulos \and
-        Nikoleta E. Glynatsi \and
-        Owen Campbell}
+\author[1]{Marc Harper}
+\author[2]{Vincent Knight}
+\author[3]{Martin Jones}
+\author[4]{Georgios Koutsovoulos}
+\author[2]{Nikoleta E. Glynatsi}
+\author[3]{Owen Campbell}
+
+\affil[1]{Google Inc., Mountain View, CA, USA}
+\affil[2]{Cardiff University, School of Mathematics, UK}
+\affil[3]{Not affiliated}
+\affil[4]{INRA, Université Côte d‘Azur, CNRS, ISA, France}
 \date{}
@@
 
-All data generated for this work is archived and available...
-% TODO Add details once data is archived.
-% TODO Include url to repo etc.
+All data generated for this work is archived and available at~\cite{data}.
 

### 2017-07-28 main.tex
Add updated citation for dojo.
Move back to bibtex.
The biblatex version has been updated on arxiv and this is incompatible
with the default/current texlive version on ubuntu. I struggled and have
given up :)
Prepare manuscript for ECJ.

--- 2017-07-15 main.tex
@@
 \documentclass{article}
+\usepackage{ecj,palatino,epsfig,latexsym,natbib}
 
@@
 
-\usepackage[backend=biber, firstinits=false, backref=false, url=true,
-            isbn=true, style=numeric]{biblatex}
-\addbibresource{bibliography.bib}
-
 % Title
@@
        Iterated Prisoner's Dilemma}
-\author{Marc Harper \and
-        Vincent Knight \and
-        Martin Jones \and
-        Georgios Koutsovoulos \and
-        Nikoleta E. Glynatsi \and
-        Owen Campbell}
+
+\author{
+		\name{\bf Marc Harper} \hfill \addr{marcharper@gmail.com}\\
+        \addr{Google Inc., Mountain View, CA, USA}
+\AND
+		\name{\bf Vincent Knight} \hfill \addr{knightva@cardiff.ac.uk}\\
+        \addr{Cardiff University, School of Mathematics, UK}
+\AND
+		\name{\bf Martin Jones} \hfill \addr{martin@pythonforbiologists.com}\\
+        \addr{Not affiliated}
+\AND
+		\name{\bf Georgios Koutsovoulos} \hfill \addr{georgios.koutsovoulos@inra.fr}\\
+        \addr{INRA, Université Côte d‘Azur, CNRS, ISA, France}
+\AND
+		\name{\bf Nikoleta E. Glynatsi} \hfill \addr{glynatsiNE@cardiff.ac.uk}\\
+        \addr{Cardiff University, School of Mathematics, UK}
+\AND
+		\name{\bf Owen Campbell} \hfill \addr{owen.campbell@tanti.org.uk}\\
+        \addr{Not affiliated}
+}
 \date{}
@@
 \end{abstract}
+
+\begin{keywords}
+    Game Theory,
+    Genetic algorithms,
+    Prisoners dilemma,
+\end{keywords}
 
@@
 A total of \input{./assets/number_of_players.tex}are included, of which
-\input{./assets/number_of_stochastic_players.tex}are stochastic.  In
+\input{./assets/number_of_stochastic_players.tex}are stochastic.
 Section~\ref{sec:standard} is concerned with the standard tournament with 200
@@
 discussed. Due to the inherent stochasticity of these IPD tournaments, these
-tournament were repeated \input{./assets/standard_number_of_repetitions.tex}
+tournaments were repeated \input{./assets/standard_number_of_repetitions.tex}
 times. This allows for a detailed and confident analysis of the performance of
@@
 Figure~\ref{fig:tit_for_tat_ranks} shows the ranks of of Tit For Tat for each
-repetition (we note that it never wins a tournament). Finally
+repetition. (We note that it never wins a tournament). Finally
 Figure~\ref{fig:tit_for_tat_wins} shows the number of opponents beaten in any given
-tournament: Tit For Tat does not win any match (this is due to the fact that it
+tournament: Tit For Tat does not win any match. (This is due to the fact that it
 will either draw with mutual cooperation or defect second).
@@
 somewhat similar to the standard tournaments, with Defector, the handshaking
-CollectiveStrategy~\cite{Li2009}, and Aggravate appearing as the top three again.
+CollectiveStrategy~\cite{Li2009}, and Aggravater appearing as the top three again.
 
@@
 All implementations of these algorithms are archived at
-\cite{marc_harper_2017_824264}. This software is (similarly to the Axelrod
+\cite{dojo}. This software is (similarly to the Axelrod
 library) available on github
@@
 
-\printbibliography
+\bibliographystyle{plain}
+\bibliography{bibliography.bib}
 

### 2017-07-28 main.tex
Fix typos

@@
 \documentclass{article}
-\usepackage{ecj,palatino,epsfig,latexsym,natbib}
 
@@
 Iterated Prisoner's Dilemma}
+\author[1]{Marc Harper}
+\author[2]{Vincent Knight}
+\author[3]{Martin Jones}
+\author[4]{Georgios Koutsovoulos}
+\author[2]{Nikoleta E. Glynatsi}
+\author[3]{Owen Campbell}
 
-\author{
-		\name{\bf Marc Harper} \hfill \addr{marcharper@gmail.com}\\
-        \addr{Google Inc., Mountain View, CA, USA}
-\AND
-		\name{\bf Vincent Knight} \hfill \addr{knightva@cardiff.ac.uk}\\
-        \addr{Cardiff University, School of Mathematics, UK}
-\AND
-		\name{\bf Martin Jones} \hfill \addr{martin@pythonforbiologists.com}\\
-        \addr{Not affiliated}
-\AND
-		\name{\bf Georgios Koutsovoulos} \hfill \addr{georgios.koutsovoulos@inra.fr}\\
-        \addr{INRA, Université Côte d‘Azur, CNRS, ISA, France}
-\AND
-		\name{\bf Nikoleta E. Glynatsi} \hfill \addr{glynatsiNE@cardiff.ac.uk}\\
-        \addr{Cardiff University, School of Mathematics, UK}
-\AND
-		\name{\bf Owen Campbell} \hfill \addr{owen.campbell@tanti.org.uk}\\
-        \addr{Not affiliated}
-}
+\affil[1]{Google Inc., Mountain View, CA, USA}
+\affil[2]{Cardiff University, School of Mathematics, UK}
+\affil[3]{Not affiliated}
+\affil[4]{INRA, Université Côte d‘Azur, CNRS, ISA, France}
 \date{}
@@
 \end{abstract}
-
-\begin{keywords}
-    Game Theory,
-    Genetic algorithms,
-    Prisoners dilemma,
-\end{keywords}
 

### 2017-08-10 plos_latex_template.tex
Write plos style version of the paper.
Restructure of file system is still needed:

- Copy tex tables in to document;
- Copy appendix in to document;
- Move images to root level.

--- 2017-07-28 main.tex
@@
-\documentclass{article}
+% Template for PLoS
+% Version 3.4 January 2017
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended
+% to minimize problems and delays during our production
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% Once your paper is accepted for publication,
+% PLEASE REMOVE ALL TRACKED CHANGES in this file
+% and leave only the final text of your manuscript.
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+% TODO Move copy all the tables in to the file (JEEEEEEZ)
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file.
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column.
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
 
-% Packages
-\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
-\usepackage{hyperref}
-\usepackage{multicol}
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace}
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Leave date blank
+\date{}
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+\setlength{\headheight}{27.023pt}
+\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\sf PLOS}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%% END MACROS SECTION
+
 \usepackage{booktabs}
-\usepackage{xstring}
-\usepackage{subcaption}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{standalone}
-\usepackage{fancyvrb}
-\usepackage{authblk}
-
 \usepackage{pdflscape}
 
-\usepackage{tikz}
-\usetikzlibrary{calc, shapes, patterns}
+\begin{document}
+\vspace*{0.2in}
 
-% Title
-\title{Reinforcement Learning Produces Dominant Strategies for the
-Iterated Prisoner's Dilemma}
-\author[1]{Marc Harper}
-\author[2]{Vincent Knight}
-\author[3]{Martin Jones}
-\author[4]{Georgios Koutsovoulos}
-\author[2]{Nikoleta E. Glynatsi}
-\author[3]{Owen Campbell}
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline
+{ Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma }
+% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Marc Harper\textsuperscript{1\Yinyang},
+Vincent Knight\textsuperscript{2*\Yinyang},
+Martin Jones\textsuperscript{3\ddag},
+Georgios Koutsovoulos\textsuperscript{4\ddag},
+Nikoleta E. Glynatsi\textsuperscript{2\ddag},
+Owen Campbell\textsuperscript{3\ddag},
+\\
+\bigskip
+\textbf{1} Affiliation Google Inc., Mountain View, CA, USA
+\\
+\textbf{2} Affiliation Cardiff University, School of Mathematics, UK
+\\
+\textbf{3} Not affiliated
+\\
+\textbf{4} INRA, Université Côte d‘Azur, CNRS, ISA, France
+\\
+\bigskip
 
-\affil[1]{Google Inc., Mountain View, CA, USA}
-\affil[2]{Cardiff University, School of Mathematics, UK}
-\affil[3]{Not affiliated}
-\affil[4]{INRA, Université Côte d‘Azur, CNRS, ISA, France}
-\date{}
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+%
+% Remove or comment out the author notes below if they aren't used.
+%
+% Primary Equal Contribution Note
+\Yinyang These authors contributed equally to this work.
 
-\begin{document}
+% Additional Equal Contribution Note
+% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
+\ddag These authors also contributed equally to this work.
 
-\maketitle
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* knightva@cardiff.ac.uk
 
-\begin{abstract}
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
     We present tournament results and several powerful strategies for the Iterated
@@
     designed strategy are the top performers in noisy tournaments also.
-\end{abstract}
+\linenumbers
 
-\section{Introduction}\label{sec:introduction}
+\section*{Introduction}
 
@@
 \url{http://axelrod-tournament.readthedocs.io}. This work presents a detailed
-analysis of a tournament with 176 strategies (details given
-in Section~\ref{sec:results}).
+analysis of a tournament with 176 strategies.
 
 \begin{table}[!hbtp]
+    \caption{\bf An overview of a selection of published tournaments. Not all
+             tournaments were `standard' round robins; for more details
+             see the indicated references.}\label{tbl:tournaments}
     \begin{center}
@@
     \end{center}
-    \caption{An overview of a selection of published tournaments. Not all
-             tournaments were `standard' round robins; for more details
-             see the indicated references.}\label{tbl:tournaments}
 \end{table}
@@
 
-\section{The Strategy Archetypes}
+\section*{Materials and methods}
+\subsection*{The Strategy Archetypes}
 
@@
 methods. Most are deterministic, use many rounds of memory, and perform
-extremely well in tournaments as will be discussed in Section~\ref{sec:results}.
-Training of these strategies will be discussed in Section~\ref{sec:methods}.
+extremely well in tournaments as will be discussed in the results Section.
+Training will be discussed in a later section.
 These strategies can encode a variety
@@
 
-\subsection{LookerUp}\label{sec:lookerup}
+\subsubsection*{LookerUp}\label{sec:lookerup}
 
@@
 the player has infinite memory depth, otherwise it has depth $\max(m_1, m_2)$.
-This is illustrated diagrammatically in Figure~\ref{fig:lookerup}.
+This is illustrated diagrammatically in Fig~\ref{fig:lookerup}.
 
@@
     \centering
-    \includestandalone[height=.3\textheight]{./assets/lookerup}
-    \caption{Diagrammatic representation of the Looker up Archetype.}
+    \includegraphics[width=\textwidth]{./assets/lookerup.pdf}
+    \caption{\bf Diagrammatic representation of the Looker up Archetype.}
     \label{fig:lookerup}
@@
 
-\subsection{Gambler}\label{sec:gambler}
+\subsubsection*{Gambler}\label{sec:gambler}
 
@@
 used to choose cooperation or defection.
-This is illustrated diagrammatically in Figure~\ref{fig:gambler}.
+This is illustrated diagrammatically in Fig~\ref{fig:gambler}.
 
@@
     \centering
-    \includestandalone[height=.3\textheight]{./assets/gambler}
-    \caption{Diagrammatic representation of the Gambler Archetype.}
+    \includegraphics[width=\textwidth]{./assets/gambler.pdf}
+    \caption{\bf Diagrammatic representation of the Gambler Archetype.}
     \label{fig:gambler}
@@
 
-\subsection{ANN: Single Hidden Layer Artificial Neural Network}\label{sec:ann}
+\subsubsection*{ANN: Single Hidden Layer Artificial Neural Network}\label{sec:ann}
 
@@
 
-\begin{multicols}{2}
 \begin{itemize}
@@
 \end{itemize}
-\end{multicols}
 
@@
 user-supplied width.  This is illustrated diagrammatically in
-Figure~\ref{fig:ann}.
+Fig~\ref{fig:ann}.
 
@@
     \centering
-    \includestandalone[height=.3\textheight]{./assets/ann}
-    \caption{Diagrammatic representation of the ANN Archetype.}
+    \includegraphics[width=\textwidth]{./assets/ann.pdf}
+    \caption{\bf Diagrammatic representation of the ANN Archetype.}
     \label{fig:ann}
@@
 
-\subsection{Finite State Machines}\label{sec:fsm}
+\subsubsection*{Finite State Machines}\label{sec:fsm}
 
@@
 and the opponent's last action, transitioning to a new state for the next round.
-This is illustrated diagrammatically in Figure~\ref{fig:fsm}.
+This is illustrated diagrammatically in Fig~\ref{fig:fsm}.
 
@@
     \centering
-    \includestandalone[height=.3\textheight]{./assets/fsm}
-    \caption{Diagrammatic representation of the Finite State Machine Archetype.}
+    \includegraphics[width=\textwidth]{./assets/fsm.pdf}
+    \caption{\bf Diagrammatic representation of the Finite State Machine Archetype.}
     \label{fig:fsm}
@@
 Training this strategy corresponds to finding mappings of states and histories
-to an action and a state. Figure~\ref{fig:fsm_images} shows two of the trained
+to an action and a state. Fig~\ref{fig:fsm16} and Fig~\ref{fig:fsm16noise} show
+two of the trained
 finite state machines. The layout of state nodes is kept the same between
-Figure~\ref{fig:fsm16} and~\ref{fig:fsm16noise} to highlight the effect of
+Fig~\ref{fig:fsm16} and Fig~\ref{fig:fsm16noise} to highlight the effect of
 different training environments. Note also that two of the 16 states are not
@@
     \centering
-    \begin{subfigure}[t]{.5\textwidth}
-        \includegraphics[height=.3\textheight]{./assets/FSM16.pdf}
-        \caption{Evolved\_FSM\_16: trained to maximise score in a standard
+        \includegraphics[width=.5\textwidth]{./assets/FSM16.pdf}
+        \caption{\bf Evolved\_FSM\_16: trained to maximise score in a standard
         tournament}
         \label{fig:fsm16}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\textwidth}
+\end{figure}
+
+\begin{figure}
         \centering
-        \includegraphics[height=.35\textheight]{./assets/FSM16noise.pdf}
+        \includegraphics[width=.5\textwidth]{./assets/FSM16noise.pdf}
         \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
@@
         \label{fig:fsm16noise}
-    \end{subfigure}%
-    \caption{Trained sixteen state Finite State Machine players.}
-    \label{fig:fsm_images}
 \end{figure}
 
-\subsection{Hidden Markov Models}\label{sec:hmm}
+\subsubsection*{Hidden Markov Models}\label{sec:hmm}
 
@@
 probabilities at each state. This is
-shown diagrammatically in Figure~\ref{fig:hmm}. Training this strategy
+shown diagrammatically in Fig~\ref{fig:hmm}. Training this strategy
 corresponds to finding mappings of states and histories to probabilities of
@@
     \centering
-    \includestandalone[height=.3\textheight]{./assets/hmm}
-    \caption{Diagrammatic representation of the Hidden Markov Model Archetype.}
+    \includegraphics[width=\textwidth]{./assets/hmm.pdf}
+    \caption{\bf Diagrammatic representation of the Hidden Markov Model Archetype.}
     \label{fig:hmm}
@@
 
-\subsection{Meta Strategies}
+\subsubsection*{Meta Strategies}
 
@@
 
-\section{Results}\label{sec:results}
+% Results and Discussion can be combined.
+\section*{Results}
 
@@
 \input{./assets/number_of_stochastic_players.tex}are stochastic.
-Section~\ref{sec:standard} is concerned with the standard tournament with 200
-turns whereas in Section~\ref{sec:noise} a tournament with 5\% noise is
+A standard tournament with 200
+turns and a tournament with 5\% noise is
 discussed. Due to the inherent stochasticity of these IPD tournaments, these
@@
 strategies. To illustrate the results considered,
-Figure~\ref{fig:tit_for_tat_scores} shows the distribution of the mean score per
+Fig~\ref{fig:tit_for_tat_scores} shows the distribution of the mean score per
 turn of Tit For Tat over all the repetitions. Similarly,
-Figure~\ref{fig:tit_for_tat_ranks} shows the ranks of of Tit For Tat for each
+Fig~\ref{fig:tit_for_tat_ranks} shows the ranks of of Tit For Tat for each
 repetition. (We note that it never wins a tournament). Finally
-Figure~\ref{fig:tit_for_tat_wins} shows the number of opponents beaten in any given
+Fig~\ref{fig:tit_for_tat_wins} shows the number of opponents beaten in any given
 tournament: Tit For Tat does not win any match. (This is due to the fact that it
@@
         \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
         \includegraphics[width=\textwidth]{./assets/standard_tft_scores.pdf}
-        \caption{Scores}
+        \caption{\bf Scores for Tit for Tat over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
         \label{fig:tit_for_tat_scores}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
+\end{figure}
+
+\begin{figure}[!hbtp]
         \centering
         \includegraphics[width=\textwidth]{./assets/standard_tft_ranks.pdf}
-        \caption{Ranks}
+        \caption{\bf Ranks for Tit for Tat over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
         \label{fig:tit_for_tat_ranks}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
+\end{figure}
+
+\begin{figure}[!hbtp]
         \centering
         \includegraphics[width=\textwidth]{./assets/standard_tft_wins.pdf}
-        \caption{Wins}
+        \caption{\bf Wins for Tit for Tat over
+        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
         \label{fig:tit_for_tat_wins}
-    \end{subfigure}%
-
-    \caption{Results for Tit For Tat over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
 \end{figure}
@@
 
-\subsection{Standard Tournament}\label{sec:standard}
+\subsection*{Standard Tournament}\label{sec:standard}
 
@@
         \centering
+        \footnotesize
         \input{./assets/standard_top_15_scores_summary.tex}
-        \caption{Standard Tournament: Mean score per turn of top 15 strategies
+        \caption{\bf Standard Tournament: Mean score per turn of top 15 strategies
             (ranked by median over
@@
 strategy (again ranked by median score) are shown in
-Figure~\ref{fig:standard_boxplot}.
+Fig~\ref{fig:standard_boxplot}.
 
@@
         \centering
-        \includegraphics[width=\paperwidth]{./assets/standard_scores_boxplots.pdf}
-        \caption{Standard Tournament: Mean score per turn (ranked by median
+        \includegraphics[width=.8\paperwidth]{./assets/standard_scores_boxplots.pdf}
+        \caption{\bf Standard Tournament: Mean score per turn (ranked by median
         over
@@
 
-Pairwise payoff results are given as a heatmap (Figure~\ref{fig:standard_heatmap})
+Pairwise payoff results are given as a heatmap (Fig~\ref{fig:standard_heatmap})
 which shows that many strategies achieve mutual cooperation (obtaining a score
@@
     \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
-    \caption{Standard Tournament: Mean score per turn of row players against
+    \caption{\bf Standard Tournament: Mean score per turn of row players against
     column players (ranked by median over
@@
 the top scoring strategies appear in the top 15 list of strategies ranked by
-match wins. This can be seen in Figure~\ref{fig:standard_winplot} where the
+match wins. This can be seen in Fig~\ref{fig:standard_winplot} where the
 distribution of the number of wins of each strategy is shown.
@@
         \input{./assets/standard_top_15_winners_wins_summary.tex}
-        \caption{Standard Tournament: Number of wins per tournament
+        \caption{\bf Standard Tournament: Number of wins per tournament
         of top 15 strategies (ranked by median wins over
@@
         \centering
-        \includegraphics[width=\paperwidth]{./assets/standard_wins_boxplots.pdf}
-        \caption{Standard Tournament: number of wins per tournament (ranked by
+        \includegraphics[width=.8\paperwidth]{./assets/standard_wins_boxplots.pdf}
+        \caption{\bf Standard Tournament: number of wins per tournament (ranked by
         median over
@@
 \begin{table}[!hbtp]
-    \centering
-        \input{./assets/standard_top_15_wins_summary.tex}
-        \caption{Standard Tournament: Number of wins per tournament
+    \caption{\bf Standard Tournament: Number of wins per tournament
         of top 15 strategies (ranked by median score over
@@
         \label{tbl:standard_wins}
+    \centering
+    \footnotesize
+        \input{./assets/standard_top_15_wins_summary.tex}
 \end{table}
@@
 Finally, Table~\ref{tbl:standard_ranks} and
-Figure~\ref{fig:standard_ranks_boxplot} show the ranks (based on median score)
+Fig~\ref{fig:standard_ranks_boxplot} show the ranks (based on median score)
 of each strategy over the repeated tournaments. Whilst there is some
@@
     \centering
-        \input{./assets/standard_top_15_ranks_summary.tex}
-        \caption{Standard Tournament: Rank in each tournament
+        \caption{\bf Standard Tournament: Rank in each tournament
         of top 15 strategies (ranked by median over
         \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+    \footnotesize
+        \input{./assets/standard_top_15_wins_summary.tex}
+        \input{./assets/standard_top_15_ranks_summary.tex}
         \label{tbl:standard_ranks}
@@
         \centering
-        \includegraphics[width=\paperwidth]{./assets/standard_ranks_boxplots.pdf}
-        \caption{Standard Tournament: rank in each tournament (ranked by
+        \includegraphics[width=.8\paperwidth]{./assets/standard_ranks_boxplots.pdf}
+        \caption{\bf Standard Tournament: rank in each tournament (ranked by
         median over
@@
 
-Figure~\ref{fig:comparison_cooperation_heatmaps_standard} shows the rate of
+Fig~\ref{fig:comparison_cooperation_heatmaps_standard_1}-~\ref{fig:comparison_cooperation_heatmaps_standard_3}
+    shows the rate of
 cooperation in each round for the top three strategies. The opponents in these
@@
         \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
         \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.pdf}
-        \caption{EvolvedLookerUp\_2\_2\_2}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
+        \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2 (over 10000
+        repetitions)}
+        \label{fig:comparison_cooperation_heatmaps_standard_1}
+\end{figure}
+
+\begin{figure}[!hbtp]
         \centering
         \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_HMM_5_array.pdf}
-        \caption{Evolved\_HMM\_5}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
+        \caption{\bf Cooperation rates for Evolved\_HMM\_5 (over 10000)
+        repetitions)}
+        \label{fig:comparison_cooperation_heatmaps_standard_2}
+\end{figure}
+
+\begin{figure}[!hbtp]
         \centering
         \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_FSM_16_array.pdf}
-        \caption{Evolved\_FSM\_16}
-    \end{subfigure}%
-
-    \caption{Comparison of cooperation rates for Standard Tournament Top 3
-    (over 10000 repetitions).}
-    \label{fig:comparison_cooperation_heatmaps_standard}
+        \caption{\bf Cooperation rates for Evolved\_FSM\_16 (over 10000)
+        repetitions)}
+        \label{fig:comparison_cooperation_heatmaps_standard_3}
 \end{figure}
 
-\subsection{Noisy Tournament}\label{sec:noise}
+\subsection*{Noisy Tournament}\label{sec:noise}
 
@@
 flipped are now described. As shown in Table~\ref{tbl:noisy_score} and
-Figure~\ref{fig:noisy_score}, the best performing strategies in median payoff
+Fig~\ref{fig:noisy_score}, the best performing strategies in median payoff
 are DBS, designed to account for noise, followed by two strategies trained in
@@
     \centering
-        \input{./assets/noisy_top_15_scores_summary.tex}
-        \caption{Noisy (5\%) Tournament: Mean score per turn of top 15 strategies
+        \caption{\bf Noisy (5\%) Tournament: Mean score per turn of top 15 strategies
         (ranked by median over
@@
         ~$^{*}$ indicates that the strategy was trained.}
+        \footnotesize
+        \input{./assets/noisy_top_15_scores_summary.tex}
         \label{tbl:noisy_score}
@@
         \centering
-        \includegraphics[width=\paperwidth]{./assets/noisy_scores_boxplots.pdf}
-        \caption{Noisy (5\%) Tournament: Mean score per turn (ranked by median
+        \includegraphics[width=.8\paperwidth]{./assets/noisy_scores_boxplots.pdf}
+        \caption{\bf Noisy (5\%) Tournament: Mean score per turn (ranked by median
         over
@@
 of noise are also among the best performers in the absence of noise. As shown in
-Figure~\ref{fig:noisy_heatmap} the cluster of mutually cooperative strategies is
+Fig~\ref{fig:noisy_heatmap} the cluster of mutually cooperative strategies is
 broken by the noise at 5\%. A similar collection of players excels at winning
@@
     \centering
-    \includegraphics[width=\textwidth]{./assets/noisy_scores_heatmap.pdf}
-    \caption{Noisy (5\%) Tournament: Mean score per turn of row players against
+    \includegraphics[width=.8\textwidth]{./assets/noisy_scores_heatmap.pdf}
+    \caption{\bf Noisy (5\%) Tournament: Mean score per turn of row players against
     column players (ranked by median over
@@
 As shown in Table~\ref{tbl:noisy_wins_top_winners} and
-Figure~\ref{fig:noisy_winplot} the strategies tallying the most wins are
+Fig~\ref{fig:noisy_winplot} the strategies tallying the most wins are
 somewhat similar to the standard tournaments, with Defector, the handshaking
@@
     \centering
-        \input{./assets/noisy_top_15_winners_wins_summary.tex}
-        \caption{Noisy (5\%) Tournament: Number of wins per tournament
+        \caption{\bf Noisy (5\%) Tournament: Number of wins per tournament
         of top 15 strategies (ranked by median wins over
         \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \input{./assets/noisy_top_15_winners_wins_summary.tex}
+        \footnotesize
         \label{tbl:noisy_wins_top_winners}
@@
         \centering
-        \includegraphics[width=\paperwidth]{./assets/noisy_wins_boxplots.pdf}
-        \caption{Noisy (5\%) Tournament: number of wins per tournament (ranked by
+        \caption{\bf Noisy (5\%) Tournament: number of wins per tournament (ranked by
         median over
         \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \includegraphics[width=.8\paperwidth]{./assets/noisy_wins_boxplots.pdf}
         \label{fig:noisy_winplot}
@@
     \centering
-        \input{./assets/noisy_top_15_wins_summary.tex}
-        \caption{Noisy (5\%) Tournament: Number of wins per tournament
+        \caption{\bf Noisy (5\%) Tournament: Number of wins per tournament
         of top 15 strategies (ranked by median score over
         \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \footnotesize
+        \input{./assets/noisy_top_15_wins_summary.tex}
         \label{tbl:noisy_wins}
@@
 Finally, Table~\ref{tbl:noisy_ranks} and
-Figure~\ref{fig:noisy_ranks_boxplot} show the ranks (based on median score)
+Fig~\ref{fig:noisy_ranks_boxplot} show the ranks (based on median score)
 of each strategy over the repeated tournaments. We see that the stochasticity
@@
     \centering
-        \input{./assets/noisy_top_15_ranks_summary.tex}
-        \caption{Noisy (5\%) Tournament: Rank in each tournament
+        \caption{\bf Noisy (5\%) Tournament: Rank in each tournament
         of top 15 strategies (ranked by median over
         \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        \footnotesize
+        \input{./assets/noisy_top_15_ranks_summary.tex}
         \label{tbl:noisy_ranks}
@@
         \centering
-        \includegraphics[width=\paperwidth]{./assets/noisy_ranks_boxplots.pdf}
-        \caption{Noisy (5\%) Tournament: rank in each tournament (ranked by
+        \includegraphics[width=.8\paperwidth]{./assets/noisy_ranks_boxplots.pdf}
+        \caption{\bf Noisy (5\%) Tournament: rank in each tournament (ranked by
         median over
@@
 
-Figure~\ref{fig:comparison_cooperation_heatmaps_noisy} shows the rate of
+Fig~\ref{fig:comparison_cooperation_heatmaps_noisy_1}-~\ref{fig:comparison_cooperation_heatmaps_noisy_3} shows the rate of
 cooperation in each round for the top three strategies (in the absense of noise)
 and just as for the top performing strategies in the standard tournament
-(Figure~\ref{fig:comparison_cooperation_heatmaps_standard}) it is evident that
+it is evident that
 the strategies never defect first and learn to quickly punish poorer strategies.
@@
         \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
         \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.pdf}
-        \caption{DBS}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
+        \caption{\bf Cooperation rates for DBS (over 10000 standard tournaments).}
+        \label{fig:comparison_cooperation_heatmaps_noisy_1}
+\end{figure}
+        `
+\begin{figure}[!hbtp]
         \centering
         \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.pdf}
-        \caption{Evolved\_ANN\_5\_Noise\_05}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
+        \caption{\bf Cooperation rates for Evolved\_ANN\_5\_Noise\_05 (over 10000 standard tournaments).}
+        \label{fig:comparison_cooperation_heatmaps_noisy_2}
+\end{figure}
+
+\begin{figure}[!hbtp]
         \centering
         \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.pdf}
-        \caption{Evolved\_FSM\_16\_Noise\_05}
-    \end{subfigure}%
-
-    \caption{Comparison of cooperation rates for the Noisy (5\%) Tournament Top 3
-    (over 10000 standard tournaments).}
-    \label{fig:comparison_cooperation_heatmaps_noisy}
+        \caption{\bf Cooperation rates for Evolved\_FSM\_16\_Noise\_05 (over 10000 standard tournaments).}
+        \label{fig:comparison_cooperation_heatmaps_noisy_3}
 \end{figure}
 
-\section{Methods}\label{sec:methods}
+\subsection*{Training methods}\label{sec:methods}
 
@@
 
-These can be used in noisy or standard environments (as evidenced by
-Sections~\ref{sec:standard} and~\ref{sec:noise}). These objectives can be
+These can be used in noisy or standard environments. These objectives can be
 further modified to suit other purposes. New strategies could be trained with
@@
 
-\section{Discussion}
+\section*{Discussion}
 
@@
 finite state machines, neural networks, and stochastic variants all performed well.
-Single layer neural networks (Section~\ref{sec:ann}) performed well in both
+Single layer neural networks performed well in both
 noisy and standard tournaments
@@
 regarding the structure. For the LookerUp and Gambler archetypes
-(Sections~\ref{sec:lookerup} and~\ref{sec:gambler})
 a decision has to be made
@@
 In contrast, the finite state machines and hidden Markov models
-(Sections\ref{sec:fsm} and~\ref{sec:hmm}) required only a choice of the number
+ required only a choice of the number
 of states, and the training algorithm can eliminate unneeded states in the case
@@
 
-% TODO: author contributions
-
 \section*{Acknowledgements}
@@
 
-\bibliographystyle{plain}
+\nolinenumbers
+
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+% or
+%
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for
+% step-by-step instructions.
+%
+\bibliographystyle{plos2015}
 \bibliography{bibliography.bib}
+
+\begin{thebibliography}{10}
+
+\bibitem{bib1}
+Conant GC, Wolfe KH.
+\newblock {{T}urning a hobby into a job: how duplicated genes find new
+  functions}.
+\newblock Nat Rev Genet. 2008 Dec;9(12):938--950.
+
+\bibitem{bib2}
+Ohno S.
+\newblock Evolution by gene duplication.
+\newblock London: George Alien \& Unwin Ltd. Berlin, Heidelberg and New York:
+  Springer-Verlag.; 1970.
+
+\bibitem{bib3}
+Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
+\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
+  infection through a transposon insertion followed by a {D}uplication}.
+\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
+
+\end{thebibliography}
 
@@
 
-\begin{multicols}{2}
 \begin{enumerate}
@@
 \end{enumerate}
-\end{multicols}
 

### 2017-08-11 plos/main.tex
Build paper according to plos guidelines.

--- 2017-08-10 plos_latex_template.tex
@@
 % The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-% TODO Move copy all the tables in to the file (JEEEEEEZ)
 %
@@
     \centering
-    \includegraphics[width=\textwidth]{./assets/lookerup.pdf}
+    \includegraphics[width=.7\textwidth]{lookerup.pdf}
     \caption{\bf Diagrammatic representation of the Looker up Archetype.}
@@
     \centering
-    \includegraphics[width=\textwidth]{./assets/gambler.pdf}
+    \includegraphics[width=.7\textwidth]{gambler.pdf}
     \caption{\bf Diagrammatic representation of the Gambler Archetype.}
@@
     \centering
-    \includegraphics[width=\textwidth]{./assets/ann.pdf}
+    \includegraphics[width=.9\textwidth]{ann.pdf}
     \caption{\bf Diagrammatic representation of the ANN Archetype.}
@@
     \centering
-    \includegraphics[width=\textwidth]{./assets/fsm.pdf}
+    \includegraphics[width=\textwidth]{fsm.pdf}
     \caption{\bf Diagrammatic representation of the Finite State Machine Archetype.}
@@
     \centering
-        \includegraphics[width=.5\textwidth]{./assets/FSM16.pdf}
+        \includegraphics[width=.5\textwidth]{FSM16.pdf}
         \caption{\bf Evolved\_FSM\_16: trained to maximise score in a standard
@@
         \centering
-        \includegraphics[width=.5\textwidth]{./assets/FSM16noise.pdf}
+        \includegraphics[width=.5\textwidth]{FSM16noise.pdf}
         \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
@@
     \centering
-    \includegraphics[width=\textwidth]{./assets/hmm.pdf}
+    \includegraphics[width=\textwidth]{hmm.pdf}
     \caption{\bf Diagrammatic representation of the Hidden Markov Model Archetype.}
@@
 
-A total of \input{./assets/number_of_players.tex}are included, of which
-\input{./assets/number_of_stochastic_players.tex}are stochastic.
+A total of 176 are included, of which
+53 are stochastic.
 A standard tournament with 200
@@
 discussed. Due to the inherent stochasticity of these IPD tournaments, these
-tournaments were repeated \input{./assets/standard_number_of_repetitions.tex}
+tournaments were repeated 50000
 times. This allows for a detailed and confident analysis of the performance of
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/standard_tft_scores.pdf}
+        \includegraphics[width=.5\textwidth]{standard_tft_scores.pdf}
         \caption{\bf Scores for Tit for Tat over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
+        50000 tournaments.}
         \label{fig:tit_for_tat_scores}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/standard_tft_ranks.pdf}
+        \includegraphics[width=.5\textwidth]{standard_tft_ranks.pdf}
         \caption{\bf Ranks for Tit for Tat over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
+        50000 tournaments.}
         \label{fig:tit_for_tat_ranks}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/standard_tft_wins.pdf}
+        \includegraphics[width=.5\textwidth]{standard_tft_wins.pdf}
         \caption{\bf Wins for Tit for Tat over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
+        50000 tournaments.}
         \label{fig:tit_for_tat_wins}
@@
         \footnotesize
-        \input{./assets/standard_top_15_scores_summary.tex}
+\begin{tabular}{lrrrrrrrrr}
+\toprule
+{} &   mean &    std &    min &     5\% &    25\% &    50\% &    75\% &    95\% &    max \\
+\midrule
+EvolvedLookerUp2\_2\_2$^{*}$    &  2.955 &  0.010 &  2.915 &  2.937 &  2.948 &  2.956 &  2.963 &  2.971 &  2.989 \\
+Evolved HMM 5$^{*}$           &  2.954 &  0.014 &  2.903 &  2.931 &  2.945 &  2.954 &  2.964 &  2.977 &  3.007 \\
+Evolved FSM 16$^{*}$          &  2.952 &  0.013 &  2.900 &  2.930 &  2.943 &  2.953 &  2.962 &  2.973 &  2.993 \\
+PSO Gambler 2\_2\_2$^{*}$       &  2.938 &  0.013 &  2.884 &  2.914 &  2.930 &  2.940 &  2.948 &  2.957 &  2.972 \\
+Evolved FSM 16 Noise 05$^{*}$ &  2.919 &  0.013 &  2.874 &  2.898 &  2.910 &  2.919 &  2.928 &  2.939 &  2.965 \\
+PSO Gambler 1\_1\_1$^{*}$       &  2.912 &  0.023 &  2.805 &  2.874 &  2.896 &  2.912 &  2.928 &  2.950 &  3.012 \\
+Evolved ANN 5$^{*}$           &  2.912 &  0.010 &  2.871 &  2.894 &  2.905 &  2.912 &  2.919 &  2.928 &  2.945 \\
+Evolved FSM 4$^{*}$           &  2.910 &  0.012 &  2.867 &  2.889 &  2.901 &  2.910 &  2.918 &  2.929 &  2.943 \\
+Evolved ANN$^{*}$             &  2.907 &  0.010 &  2.865 &  2.890 &  2.900 &  2.908 &  2.914 &  2.923 &  2.942 \\
+PSO Gambler Mem1$^{*}$        &  2.901 &  0.025 &  2.783 &  2.858 &  2.884 &  2.901 &  2.919 &  2.942 &  2.994 \\
+Evolved ANN 5 Noise 05$^{*}$  &  2.864 &  0.008 &  2.830 &  2.850 &  2.858 &  2.865 &  2.870 &  2.877 &  2.891 \\
+DBS                           &  2.857 &  0.009 &  2.823 &  2.842 &  2.851 &  2.857 &  2.863 &  2.872 &  2.899 \\
+Winner12                      &  2.849 &  0.008 &  2.820 &  2.836 &  2.844 &  2.850 &  2.855 &  2.862 &  2.874 \\
+Fool Me Once                  &  2.844 &  0.008 &  2.818 &  2.830 &  2.838 &  2.844 &  2.850 &  2.857 &  2.882 \\
+Omega TFT: 3, 8               &  2.841 &  0.011 &  2.800 &  2.822 &  2.833 &  2.841 &  2.849 &  2.859 &  2.882 \\
+\bottomrule
+\end{tabular}
         \caption{\bf Standard Tournament: Mean score per turn of top 15 strategies
-            (ranked by median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).
+            (ranked by median over 50000 tournaments).
         The leaderboard is dominated by the trained strategies (indicated by a
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{./assets/standard_scores_boxplots.pdf}
+        \includegraphics[width=.8\paperwidth]{standard_scores_boxplots.pdf}
         \caption{\bf Standard Tournament: Mean score per turn (ranked by median
         over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
         \label{fig:standard_boxplot}
@@
     \centering
-    \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
+    \includegraphics[width=\textwidth]{standard_scores_heatmap.pdf}
     \caption{\bf Standard Tournament: Mean score per turn of row players against
-    column players (ranked by median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+    column players (ranked by median over 50000 tournaments).}
     \label{fig:standard_heatmap}
@@
     \centering
-        \input{./assets/standard_top_15_winners_wins_summary.tex}
         \caption{\bf Standard Tournament: Number of wins per tournament
         of top 15 strategies (ranked by median wins over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
         \label{tbl:standard_wins_top_winners}
+\begin{tabular}{lrrrrrrrrr}
+\toprule
+{} &     mean &    std &  min &     5\% &    25\% &    50\% &    75\% &    95\% &  max \\
+\midrule
+Aggravater          &  161.595 &  0.862 &  160 &  160.0 &  161.0 &  162.0 &  162.0 &  163.0 &  163 \\
+Defector            &  161.605 &  0.864 &  160 &  160.0 &  161.0 &  162.0 &  162.0 &  163.0 &  163 \\
+CS                  &  159.646 &  1.005 &  155 &  158.0 &  159.0 &  160.0 &  160.0 &  161.0 &  161 \\
+ZD-Extort-4         &  150.598 &  2.662 &  138 &  146.0 &  149.0 &  151.0 &  152.0 &  155.0 &  162 \\
+Handshake           &  149.552 &  1.754 &  142 &  147.0 &  148.0 &  150.0 &  151.0 &  152.0 &  154 \\
+ZD-Extort-2         &  146.094 &  3.445 &  129 &  140.0 &  144.0 &  146.0 &  148.0 &  152.0 &  160 \\
+ZD-Extort-2 v2      &  146.291 &  3.425 &  131 &  141.0 &  144.0 &  146.0 &  149.0 &  152.0 &  160 \\
+Winner21            &  139.946 &  1.225 &  136 &  138.0 &  139.0 &  140.0 &  141.0 &  142.0 &  143 \\
+TF2                 &  138.240 &  1.700 &  130 &  135.0 &  137.0 &  138.0 &  139.0 &  141.0 &  143 \\
+TF1                 &  135.692 &  1.408 &  130 &  133.0 &  135.0 &  136.0 &  137.0 &  138.0 &  140 \\
+Naive Prober: 0.1   &  136.016 &  2.504 &  127 &  132.0 &  134.0 &  136.0 &  138.0 &  140.0 &  147 \\
+Feld: 1.0, 0.5, 200 &  136.087 &  1.696 &  130 &  133.0 &  135.0 &  136.0 &  137.0 &  139.0 &  144 \\
+Joss: 0.9           &  136.015 &  2.503 &  126 &  132.0 &  134.0 &  136.0 &  138.0 &  140.0 &  146 \\
+Predator            &  133.718 &  1.385 &  129 &  131.0 &  133.0 &  134.0 &  135.0 &  136.0 &  138 \\
+SolutionB5          &  125.843 &  1.509 &  120 &  123.0 &  125.0 &  126.0 &  127.0 &  128.0 &  131 \\
+\bottomrule
+\end{tabular}
 \end{table}
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{./assets/standard_wins_boxplots.pdf}
+        \includegraphics[width=.8\paperwidth]{standard_wins_boxplots.pdf}
         \caption{\bf Standard Tournament: number of wins per tournament (ranked by
         median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
         \label{fig:standard_winplot}
@@
         of top 15 strategies (ranked by median score over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
         \label{tbl:standard_wins}
@@
     \footnotesize
-        \input{./assets/standard_top_15_wins_summary.tex}
+\begin{tabular}{lrrrrrrrrr}
+\toprule
+{} &    mean &    std &  min &    5\% &   25\% &   50\% &   75\% &   95\% &  max \\
+\midrule
+EvolvedLookerUp2\_2\_2$^{*}$    &  48.259 &  1.336 &   43 &  46.0 &  47.0 &  48.0 &  49.0 &  50.0 &   53 \\
+Evolved HMM 5$^{*}$           &  41.358 &  1.221 &   36 &  39.0 &  41.0 &  41.0 &  42.0 &  43.0 &   45 \\
+Evolved FSM 16$^{*}$          &  56.978 &  1.099 &   51 &  55.0 &  56.0 &  57.0 &  58.0 &  59.0 &   60 \\
+PSO Gambler 2\_2\_2$^{*}$       &  40.692 &  1.089 &   36 &  39.0 &  40.0 &  41.0 &  41.0 &  42.0 &   45 \\
+Evolved FSM 16 Noise 05$^{*}$ &  40.070 &  1.673 &   34 &  37.0 &  39.0 &  40.0 &  41.0 &  43.0 &   47 \\
+PSO Gambler 1\_1\_1$^{*}$       &  45.005 &  1.595 &   38 &  42.0 &  44.0 &  45.0 &  46.0 &  48.0 &   51 \\
+Evolved ANN 5$^{*}$           &  43.224 &  0.674 &   41 &  42.0 &  43.0 &  43.0 &  44.0 &  44.0 &   47 \\
+Evolved FSM 4$^{*}$           &  37.227 &  0.951 &   34 &  36.0 &  37.0 &  37.0 &  38.0 &  39.0 &   41 \\
+Evolved ANN$^{*}$             &  43.100 &  1.021 &   40 &  42.0 &  42.0 &  43.0 &  44.0 &  45.0 &   48 \\
+PSO Gambler Mem1$^{*}$        &  43.444 &  1.837 &   34 &  40.0 &  42.0 &  43.0 &  45.0 &  46.0 &   51 \\
+Evolved ANN 5 Noise 05$^{*}$  &  33.711 &  1.125 &   30 &  32.0 &  33.0 &  34.0 &  34.0 &  35.0 &   38 \\
+DBS                           &  32.329 &  1.198 &   28 &  30.0 &  32.0 &  32.0 &  33.0 &  34.0 &   38 \\
+Winner12                      &  40.179 &  1.037 &   36 &  39.0 &  39.0 &  40.0 &  41.0 &  42.0 &   44 \\
+Fool Me Once                  &  50.121 &  0.422 &   48 &  50.0 &  50.0 &  50.0 &  50.0 &  51.0 &   52 \\
+Omega TFT: 3, 8               &  35.157 &  0.859 &   32 &  34.0 &  35.0 &  35.0 &  36.0 &  37.0 &   39 \\
+\bottomrule
+\end{tabular}
 \end{table}
@@
         of top 15 strategies (ranked by median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
     \footnotesize
-        \input{./assets/standard_top_15_wins_summary.tex}
-        \input{./assets/standard_top_15_ranks_summary.tex}
+\begin{tabular}{lrrrrrrrrr}
+\toprule
+{} &    mean &    std &  min &    5\% &   25\% &   50\% &   75\% &   95\% &  max \\
+\midrule
+EvolvedLookerUp2\_2\_2$^{*}$    &   2.173 &  1.070 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   4.0 &    8 \\
+Evolved HMM 5$^{*}$           &   2.321 &  1.275 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   5.0 &   10 \\
+Evolved FSM 16$^{*}$          &   2.489 &  1.299 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   5.0 &   10 \\
+PSO Gambler 2\_2\_2$^{*}$       &   3.961 &  1.525 &    1 &   2.0 &   3.0 &   4.0 &   5.0 &   7.0 &   10 \\
+Evolved FSM 16 Noise 05$^{*}$ &   6.300 &  1.688 &    1 &   4.0 &   5.0 &   6.0 &   7.0 &   9.0 &   11 \\
+PSO Gambler 1\_1\_1$^{*}$       &   7.082 &  2.499 &    1 &   3.0 &   5.0 &   7.0 &   9.0 &  10.0 &   17 \\
+Evolved ANN 5$^{*}$           &   7.287 &  1.523 &    2 &   5.0 &   6.0 &   7.0 &   8.0 &  10.0 &   11 \\
+Evolved FSM 4$^{*}$           &   7.527 &  1.631 &    2 &   5.0 &   6.0 &   8.0 &   9.0 &  10.0 &   12 \\
+Evolved ANN$^{*}$             &   7.901 &  1.450 &    2 &   5.0 &   7.0 &   8.0 &   9.0 &  10.0 &   12 \\
+PSO Gambler Mem1$^{*}$        &   8.222 &  2.535 &    1 &   4.0 &   6.0 &   9.0 &  10.0 &  12.0 &   20 \\
+Evolved ANN 5 Noise 05$^{*}$  &  11.362 &  0.872 &    8 &  10.0 &  11.0 &  11.0 &  12.0 &  13.0 &   16 \\
+DBS                           &  12.197 &  1.125 &    9 &  11.0 &  11.0 &  12.0 &  13.0 &  14.0 &   16 \\
+Winner12                      &  13.221 &  1.137 &    9 &  11.0 &  12.0 &  13.0 &  14.0 &  15.0 &   17 \\
+Fool Me Once                  &  13.960 &  1.083 &    9 &  12.0 &  13.0 &  14.0 &  15.0 &  15.0 &   17 \\
+Omega TFT: 3, 8               &  14.275 &  1.301 &    9 &  12.0 &  13.0 &  15.0 &  15.0 &  16.0 &   19 \\
+\bottomrule
+\end{tabular}
         \label{tbl:standard_ranks}
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{./assets/standard_ranks_boxplots.pdf}
+        \includegraphics[width=.8\paperwidth]{standard_ranks_boxplots.pdf}
         \caption{\bf Standard Tournament: rank in each tournament (ranked by
         median over
-        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
         \label{fig:standard_ranks_boxplot}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.pdf}
         \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2 (over 10000
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_HMM_5_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_HMM_5_array.pdf}
         \caption{\bf Cooperation rates for Evolved\_HMM\_5 (over 10000)
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_FSM_16_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_array.pdf}
         \caption{\bf Cooperation rates for Evolved\_FSM\_16 (over 10000)
@@
         \caption{\bf Noisy (5\%) Tournament: Mean score per turn of top 15 strategies
-        (ranked by median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)
+        (ranked by median over 50000 tournaments)
         ~$^{*}$ indicates that the strategy was trained.}
         \footnotesize
-        \input{./assets/noisy_top_15_scores_summary.tex}
+        \begin{tabular}{lrrrrrrrrr}
+        \toprule
+        {} &   mean &    std &    min &     5\% &    25\% &    50\% &    75\% &    95\% &    max \\
+        \midrule
+        DBS                              &  2.573 &  0.025 &  2.474 &  2.533 &  2.556 &  2.573 &  2.589 &  2.614 &  2.675 \\
+        Evolved ANN 5 Noise 05$^{*}$     &  2.534 &  0.025 &  2.418 &  2.492 &  2.517 &  2.534 &  2.551 &  2.575 &  2.629 \\
+        Evolved FSM 16 Noise 05$^{*}$    &  2.515 &  0.031 &  2.374 &  2.464 &  2.494 &  2.515 &  2.536 &  2.565 &  2.642 \\
+        Evolved ANN 5$^{*}$              &  2.410 &  0.030 &  2.273 &  2.359 &  2.389 &  2.410 &  2.430 &  2.459 &  2.536 \\
+        Evolved FSM 4$^{*}$              &  2.393 &  0.027 &  2.286 &  2.348 &  2.374 &  2.393 &  2.411 &  2.437 &  2.505 \\
+        Evolved HMM 5$^{*}$              &  2.392 &  0.026 &  2.289 &  2.348 &  2.374 &  2.392 &  2.409 &  2.435 &  2.493 \\
+        Level Punisher                   &  2.388 &  0.025 &  2.281 &  2.347 &  2.372 &  2.389 &  2.405 &  2.429 &  2.503 \\
+        Omega TFT: 3, 8                  &  2.387 &  0.026 &  2.270 &  2.344 &  2.370 &  2.388 &  2.405 &  2.430 &  2.498 \\
+        Spiteful Tit For Tat             &  2.383 &  0.030 &  2.259 &  2.334 &  2.363 &  2.383 &  2.403 &  2.432 &  2.517 \\
+        Evolved FSM 16$^{*}$             &  2.375 &  0.029 &  2.239 &  2.326 &  2.355 &  2.375 &  2.395 &  2.423 &  2.507 \\
+        PSO Gambler 2\_2\_2 Noise 05$^{*}$ &  2.371 &  0.029 &  2.250 &  2.323 &  2.352 &  2.371 &  2.390 &  2.418 &  2.480 \\
+        Adaptive                         &  2.369 &  0.038 &  2.217 &  2.306 &  2.344 &  2.369 &  2.395 &  2.431 &  2.524 \\
+        Evolved ANN$^{*}$                &  2.365 &  0.022 &  2.270 &  2.329 &  2.351 &  2.366 &  2.380 &  2.401 &  2.483 \\
+        Math Constant Hunter             &  2.344 &  0.022 &  2.257 &  2.308 &  2.329 &  2.344 &  2.359 &  2.382 &  2.445 \\
+        Gradual                          &  2.341 &  0.021 &  2.248 &  2.306 &  2.327 &  2.341 &  2.355 &  2.376 &  2.429 \\
+        \bottomrule
+        \end{tabular}
         \label{tbl:noisy_score}
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{./assets/noisy_scores_boxplots.pdf}
+        \includegraphics[width=.8\paperwidth]{noisy_scores_boxplots.pdf}
         \caption{\bf Noisy (5\%) Tournament: Mean score per turn (ranked by median
         over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
         \label{fig:noisy_score}
@@
     \centering
-    \includegraphics[width=.8\textwidth]{./assets/noisy_scores_heatmap.pdf}
+    \includegraphics[width=.8\textwidth]{noisy_scores_heatmap.pdf}
     \caption{\bf Noisy (5\%) Tournament: Mean score per turn of row players against
     column players (ranked by median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
     \label{fig:noisy_heatmap}
@@
         of top 15 strategies (ranked by median wins over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
-        \input{./assets/noisy_top_15_winners_wins_summary.tex}
+        50000 tournaments).}
         \footnotesize
+\begin{tabular}{lrrrrrrrrr}
+\toprule
+{} &     mean &    std &  min &     5\% &    25\% &    50\% &    75\% &    95\% &  max \\
+\midrule
+Aggravater           &  156.654 &  3.328 &  141 &  151.0 &  154.0 &  157.0 &  159.0 &  162.0 &  170 \\
+CS                   &  156.875 &  3.265 &  144 &  151.0 &  155.0 &  157.0 &  159.0 &  162.0 &  169 \\
+Defector             &  157.324 &  3.262 &  144 &  152.0 &  155.0 &  157.0 &  160.0 &  163.0 &  170 \\
+Grudger              &  155.590 &  3.303 &  143 &  150.0 &  153.0 &  156.0 &  158.0 &  161.0 &  168 \\
+Retaliate 3: 0.05    &  155.382 &  3.306 &  141 &  150.0 &  153.0 &  155.0 &  158.0 &  161.0 &  169 \\
+Retaliate 2: 0.08    &  155.365 &  3.320 &  140 &  150.0 &  153.0 &  155.0 &  158.0 &  161.0 &  169 \\
+MEM2                 &  155.052 &  3.349 &  140 &  149.0 &  153.0 &  155.0 &  157.0 &  160.0 &  169 \\
+HTfT                 &  155.298 &  3.344 &  141 &  150.0 &  153.0 &  155.0 &  158.0 &  161.0 &  168 \\
+Retaliate: 0.1       &  155.370 &  3.314 &  139 &  150.0 &  153.0 &  155.0 &  158.0 &  161.0 &  168 \\
+Spiteful Tit For Tat &  155.030 &  3.326 &  133 &  150.0 &  153.0 &  155.0 &  157.0 &  160.0 &  167 \\
+Punisher             &  153.281 &  3.375 &  140 &  148.0 &  151.0 &  153.0 &  156.0 &  159.0 &  167 \\
+2TfT                 &  152.823 &  3.429 &  138 &  147.0 &  151.0 &  153.0 &  155.0 &  158.0 &  165 \\
+TF3                  &  153.031 &  3.327 &  138 &  148.0 &  151.0 &  153.0 &  155.0 &  158.0 &  166 \\
+Fool Me Once         &  152.817 &  3.344 &  138 &  147.0 &  151.0 &  153.0 &  155.0 &  158.0 &  166 \\
+Predator             &  151.406 &  3.403 &  138 &  146.0 &  149.0 &  151.0 &  154.0 &  157.0 &  165 \\
+\bottomrule
+\end{tabular}
         \label{tbl:noisy_wins_top_winners}
@@
         \centering
+        \includegraphics[width=.8\paperwidth]{noisy_wins_boxplots.pdf}
         \caption{\bf Noisy (5\%) Tournament: number of wins per tournament (ranked by
         median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
-        \includegraphics[width=.8\paperwidth]{./assets/noisy_wins_boxplots.pdf}
+        50000 tournaments).}
         \label{fig:noisy_winplot}
@@
         of top 15 strategies (ranked by median score over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
         \footnotesize
-        \input{./assets/noisy_top_15_wins_summary.tex}
+\begin{tabular}{lrrrrrrrrr}
+\toprule
+{} &     mean &    std &  min &     5\% &    25\% &    50\% &    75\% &    95\% &  max \\
+\midrule
+DBS                              &  102.545 &  3.671 &   87 &   97.0 &  100.0 &  103.0 &  105.0 &  109.0 &  118 \\
+Evolved ANN 5 Noise 05$^{*}$     &   75.026 &  4.226 &   57 &   68.0 &   72.0 &   75.0 &   78.0 &   82.0 &   93 \\
+Evolved FSM 16 Noise 05$^{*}$    &   88.699 &  3.864 &   74 &   82.0 &   86.0 &   89.0 &   91.0 &   95.0 &  104 \\
+Evolved ANN 5$^{*}$              &  137.878 &  4.350 &  118 &  131.0 &  135.0 &  138.0 &  141.0 &  145.0 &  156 \\
+Evolved FSM 4$^{*}$              &   74.250 &  2.694 &   64 &   70.0 &   72.0 &   74.0 &   76.0 &   79.0 &   85 \\
+Evolved HMM 5$^{*}$              &   88.189 &  2.774 &   77 &   84.0 &   86.0 &   88.0 &   90.0 &   93.0 &   99 \\
+Level Punisher                   &   94.263 &  4.789 &   75 &   86.0 &   91.0 &   94.0 &   97.0 &  102.0 &  116 \\
+Omega TFT: 3, 8                  &  131.655 &  4.302 &  112 &  125.0 &  129.0 &  132.0 &  135.0 &  139.0 &  150 \\
+Spiteful Tit For Tat             &  155.030 &  3.326 &  133 &  150.0 &  153.0 &  155.0 &  157.0 &  160.0 &  167 \\
+Evolved FSM 16$^{*}$             &  103.288 &  3.631 &   89 &   97.0 &  101.0 &  103.0 &  106.0 &  109.0 &  118 \\
+PSO Gambler 2\_2\_2 Noise 05$^{*}$ &   90.515 &  4.012 &   75 &   84.0 &   88.0 &   90.0 &   93.0 &   97.0 &  109 \\
+Adaptive                         &  101.898 &  4.899 &   83 &   94.0 &   99.0 &  102.0 &  105.0 &  110.0 &  124 \\
+Evolved ANN$^{*}$                &  138.514 &  3.401 &  125 &  133.0 &  136.0 &  139.0 &  141.0 &  144.0 &  153 \\
+Math Constant Hunter             &   93.010 &  3.254 &   79 &   88.0 &   91.0 &   93.0 &   95.0 &   98.0 &  107 \\
+Gradual                          &  101.899 &  2.870 &   91 &   97.0 &  100.0 &  102.0 &  104.0 &  107.0 &  114 \\
+\bottomrule
+\end{tabular}
         \label{tbl:noisy_wins}
@@
         of top 15 strategies (ranked by median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
         \footnotesize
-        \input{./assets/noisy_top_15_ranks_summary.tex}
+\begin{tabular}{lrrrrrrrrr}
+\toprule
+{} &    mean &    std &  min &      5\% &   25\% &   50\% &   75\% &   95\% &  max \\
+\midrule
+DBS                              &   1.205 &  0.468 &    1 &   1.000 &   1.0 &   1.0 &   1.0 &   2.0 &    3 \\
+Evolved ANN 5 Noise 05$^{*}$     &   2.184 &  0.629 &    1 &   1.000 &   2.0 &   2.0 &   3.0 &   3.0 &    5 \\
+Evolved FSM 16 Noise 05$^{*}$    &   2.626 &  0.618 &    1 &   1.000 &   2.0 &   3.0 &   3.0 &   3.0 &    9 \\
+Evolved ANN 5$^{*}$              &   6.371 &  2.786 &    2 &   4.000 &   4.0 &   5.0 &   8.0 &  12.0 &   31 \\
+Evolved FSM 4$^{*}$              &   7.919 &  3.175 &    3 &   4.000 &   5.0 &   7.0 &  10.0 &  14.0 &   33 \\
+Evolved HMM 5$^{*}$              &   7.996 &  3.110 &    3 &   4.000 &   6.0 &   7.0 &  10.0 &  14.0 &   26 \\
+Level Punisher                   &   8.337 &  3.083 &    3 &   4.000 &   6.0 &   8.0 &  10.0 &  14.0 &   26 \\
+Omega TFT: 3, 8                  &   8.510 &  3.249 &    3 &   4.000 &   6.0 &   8.0 &  11.0 &  14.0 &   32 \\
+Spiteful Tit For Tat             &   9.159 &  3.772 &    3 &   4.000 &   6.0 &   9.0 &  12.0 &  16.0 &   40 \\
+Evolved FSM 16$^{*}$             &  10.218 &  4.099 &    3 &   4.975 &   7.0 &  10.0 &  13.0 &  17.0 &   56 \\
+PSO Gambler 2\_2\_2 Noise 05$^{*}$ &  10.760 &  4.102 &    3 &   5.000 &   8.0 &  10.0 &  13.0 &  18.0 &   47 \\
+Evolved ANN$^{*}$                &  11.346 &  3.252 &    3 &   6.000 &   9.0 &  11.0 &  13.0 &  17.0 &   32 \\
+Adaptive                         &  11.420 &  5.739 &    3 &   4.000 &   7.0 &  11.0 &  14.0 &  21.0 &   63 \\
+Math Constant Hunter             &  14.668 &  3.788 &    3 &   9.000 &  12.0 &  15.0 &  17.0 &  21.0 &   43 \\
+Gradual                          &  15.163 &  3.672 &    4 &  10.000 &  13.0 &  15.0 &  17.0 &  21.0 &   49 \\
+\bottomrule
+\end{tabular}
         \label{tbl:noisy_ranks}
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{./assets/noisy_ranks_boxplots.pdf}
+        \includegraphics[width=.8\paperwidth]{noisy_ranks_boxplots.pdf}
         \caption{\bf Noisy (5\%) Tournament: rank in each tournament (ranked by
         median over
-        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
+        50000 tournaments).}
         \label{fig:noisy_ranks_boxplot}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.pdf}
         \caption{\bf Cooperation rates for DBS (over 10000 standard tournaments).}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.pdf}
         \caption{\bf Cooperation rates for Evolved\_ANN\_5\_Noise\_05 (over 10000 standard tournaments).}
@@
         \centering
-        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.pdf}
         \caption{\bf Cooperation rates for Evolved\_FSM\_16\_Noise\_05 (over 10000 standard tournaments).}
@@
 %
-\bibliographystyle{plos2015}
-\bibliography{bibliography.bib}
 
@@
 
-\bibitem{bib1}
-Conant GC, Wolfe KH.
-\newblock {{T}urning a hobby into a job: how duplicated genes find new
-  functions}.
-\newblock Nat Rev Genet. 2008 Dec;9(12):938--950.
-
-\bibitem{bib2}
-Ohno S.
-\newblock Evolution by gene duplication.
-\newblock London: George Alien \& Unwin Ltd. Berlin, Heidelberg and New York:
-  Springer-Verlag.; 1970.
-
-\bibitem{bib3}
-Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
-\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
-  infection through a transposon insertion followed by a {D}uplication}.
-\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
+\bibitem{Axelrod1984}
+Axelrod RM.
+\newblock The evolution of cooperation.
+\newblock Basic books; 2006.
+
+\bibitem{knight2016open}
+Knight V, Campbell O, Harper M, Langner K, Campbell J, Campbell T, et~al.
+\newblock An Open Framework for the Reproducible Study of the Iterated
+  Prisoner’s Dilemma.
+\newblock Journal of Open Research Software. 2016;4(1).
+
+\bibitem{axelrodproject}
+project developers TA. Axelrod-Python/Axelrod: v2.13.0; 2017.
+\newblock https://doi.org/10.5281/zenodo.801749.
+
+\bibitem{nowak1993strategy}
+Nowak M, Sigmund K.
+\newblock A strategy of win-stay, lose-shift that outperforms tit-for-tat in
+  the Prisoner's Dilemma game.
+\newblock Nature. 1993;364(6432):56.
+
+\bibitem{slany2007some}
+Slany W, Kienreich W.
+\newblock On some winning strategies for the Iterated Prisoner’s Dilemma, or,
+  Mr. Nice Guy and the Cosa Nostra.
+\newblock The Iterated Prisoners' Dilemma: 20 Years on. 2007;4:171.
+
+\bibitem{li2007design}
+Li J.
+\newblock How to design a strategy to win an IPD tournament.
+\newblock The iterated prisoner’s dilemma. 2007;20:89--104.
+
+\bibitem{Stewart2012}
+Stewart AJ, Plotkin JB.
+\newblock Extortion and cooperation in the Prisoner’s Dilemma.
+\newblock Proceedings of the National Academy of Sciences.
+  2012;109(26):10134--10135.
+\newblock doi:{10.1073/pnas.1208087109}.
+
+\bibitem{Axelrod1980a}
+Axelrod R.
+\newblock {Effective Choice in the Prisoner's Dilemma}.
+\newblock Journal of Conflict Resolution. 1980;24(1):3--25.
+
+\bibitem{Bendor1991}
+Bendor J, Kramer RM, Stout S.
+\newblock {When in doubt\dots: Cooperation in a noisy prisoner's dilemma}.
+\newblock Journal of Conflict Resolution. 1991;35(4):691--719.
+\newblock doi:{10.1177/0022002791035004007}.
+
+\bibitem{Axelrod1980b}
+Axelrod R.
+\newblock {More Effective Choice in the Prisoner's Dilemma}.
+\newblock Journal of Conflict Resolution. 1980;24(3):379--403.
+\newblock doi:{10.1177/002200278002400301}.
+
+\bibitem{Stephens2002}
+Stephens DW, McLinn CM, Stevens JR.
+\newblock {Discounting and reciprocity in an Iterated Prisoner's Dilemma.}
+\newblock Science (New York, NY). 2002;298(5601):2216--2218.
+\newblock doi:{10.1126/science.1078498}.
+
+\bibitem{kendall2007iterated}
+Kendall G, Yao X, Chong SY.
+\newblock The iterated prisoners' dilemma: 20 years on. vol.~4.
+\newblock World Scientific; 2007.
+
+\bibitem{ashlock2006training}
+Ashlock D.
+\newblock Training function stacks to play the iterated prisoner's dilemma.
+\newblock In: Computational Intelligence and Games, 2006 IEEE Symposium on.
+  IEEE; 2006. p. 111--118.
+
+\bibitem{Ashlock2015}
+Ashlock D, Brown JA, Hingston P.
+\newblock Multiple Opponent Optimization of Prisoner’s Dilemma Playing
+  Agents.
+\newblock IEEE Transactions on Computational Intelligence and AI in Games.
+  2015;7(1):53--65.
+
+\bibitem{Ashlock2006}
+Ashlock W, Ashlock D.
+\newblock {Changes in Prisoner ' s Dilemma Strategies Over Evolutionary Time
+  With Different Population Sizes}. 2006; p. 1001--1008.
+
+\bibitem{ashlock2014shaped}
+Ashlock W, Ashlock D.
+\newblock Shaped prisoner's dilemma automata.
+\newblock In: Computational Intelligence and Games (CIG), 2014 IEEE Conference
+  on. IEEE; 2014. p. 1--8.
+
+\bibitem{Ashlock2014}
+Ashlock W, Tsang J, Ashlock D.
+\newblock The evolution of exploitation.
+\newblock In: Foundations of Computational Intelligence (FOCI), 2014 IEEE
+  Symposium on. IEEE; 2014. p. 135--142.
+
+\bibitem{barlow2015varying}
+Barlow LA, Ashlock D.
+\newblock Varying decision inputs in Prisoner's Dilemma.
+\newblock In: Computational Intelligence in Bioinformatics and Computational
+  Biology (CIBCB), 2015 IEEE Conference on. IEEE; 2015. p. 1--8.
+
+\bibitem{fogel1993evolving}
+Fogel DB.
+\newblock Evolving behaviors in the iterated prisoner's dilemma.
+\newblock Evolutionary Computation. 1993;1(1):77--97.
+
+\bibitem{marks1989niche}
+Marks RE.
+\newblock Niche strategies: the Prisoner’s Dilemma computer tournaments
+  revisited.
+\newblock In: JOURNAL OF EVOLUTIONARY ECONOMICS. Citeseer; 1989.
+
+\bibitem{sudo2015effects}
+Sudo T, Goto K, Nojima Y, Ishibuchi H.
+\newblock Effects of ensemble action selection with different usage of player's
+  memory resource on the evolution of cooperative strategies for iterated
+  prisoner's dilemma game.
+\newblock In: Evolutionary Computation (CEC), 2015 IEEE Congress on. IEEE;
+  2015. p. 1505--1512.
+
+\bibitem{vassiliades2010multiagent}
+Vassiliades V, Christodoulou C.
+\newblock Multiagent reinforcement learning in the iterated prisoner's dilemma:
+  fast cooperation through evolved payoffs.
+\newblock In: Neural Networks (IJCNN), The 2010 International Joint Conference
+  on. IEEE; 2010. p. 1--8.
+
+\bibitem{Gaudesi2016}
+Gaudesi M, Piccolo E, Squillero G, Tonda A.
+\newblock Exploiting evolutionary modeling to prevail in iterated prisoner’s
+  dilemma tournaments.
+\newblock IEEE Transactions on Computational Intelligence and AI in Games.
+  2016;8(3):288--300.
+
+\bibitem{franken2005particle}
+Franken N, Engelbrecht AP.
+\newblock Particle swarm optimization approaches to coevolve strategies for the
+  iterated prisoner's dilemma.
+\newblock IEEE Transactions on Evolutionary Computation. 2005;9(6):562--579.
+
+\bibitem{Axelrod1980}
+Axelrod R.
+\newblock Effective choice in the prisoner's dilemma.
+\newblock Journal of conflict resolution. 1980;24(1):3--25.
+
+\bibitem{Mathieu2015}
+Mathieu P, Delahaye JP.
+\newblock {New Winning Strategies for the Iterated Prisoner's Dilemma (Extended
+  Abstract)}.
+\newblock 14th International Conference on Autonomous Agents and Multiagent
+  Systems (AAMAS 2015). 2015; p. 1665--1666.
+
+\bibitem{data}
+Knight V, Harper M. {Data for: Reinforcement Learning Produces Dominant
+  Strategies for the Iterated Prisoner's Dilemma}; 2017.
+\newblock https://doi.org/10.5281/zenodo.832287.
+
+\bibitem{Au2006}
+Au TC, Nau D.
+\newblock Accident or intention: that is the question (in the Noisy Iterated
+  Prisoner's Dilemma).
+\newblock In: Proceedings of the fifth international joint conference on
+  Autonomous agents and multiagent systems. ACM; 2006. p. 561--568.
+
+\bibitem{Press2012}
+Press WH, Dyson FJ.
+\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
+  evolutionary opponent.}
+\newblock Proceedings of the National Academy of Sciences of the United States
+  of America. 2012;109(26):10409--13.
+\newblock doi:{10.1073/pnas.1206569109}.
+
+\bibitem{Li2009}
+Li J, Kendall G.
+\newblock {A strategy with novel evolutionary features for the iterated
+  prisoner's dilemma.}
+\newblock Evolutionary Computation. 2009;17(2):257--274.
+\newblock doi:{10.1162/evco.2009.17.2.257}.
+
+\bibitem{Prison1998}
+LIFL. PRISON; 2008.
+\newblock http://www.lifl.fr/IPD/ipd.frame.html.
+
+\bibitem{turing1950computing}
+Turing AM.
+\newblock Computing machinery and intelligence.
+\newblock Mind. 1950;59(236):433--460.
+
+\bibitem{imran2013overview}
+Imran M, Hashim R, Khalid NEA.
+\newblock An overview of particle swarm optimization variants.
+\newblock Procedia Engineering. 2013;53:491--496.
+
+\bibitem{moriarty1999evolutionary}
+Moriarty DE, Schultz AC, Grefenstette JJ.
+\newblock Evolutionary algorithms for reinforcement learning.
+\newblock J Artif Intell Res(JAIR). 1999;11:241--276.
+
+\bibitem{dojo}
+Harper M, Knight V, Jones M, Koutsovoulos G. Axelrod-Python/axelrod-dojo:
+  V0.0.2; 2017.
+\newblock https://doi.org/10.5281/zenodo.832282.
+
+\bibitem{axelrodproject2.2}
+project developers TA. Axelrod-Python/Axelrod: v2.2.0; 2016.
+\newblock https://doi.org/10.5281/zenodo.211828.
+
+\bibitem{ashlock2013impact}
+Ashlock D, Kim EY.
+\newblock The impact of varying resources available to iterated prisoner's
+  dilemma agents.
+\newblock In: Foundations of Computational Intelligence (FOCI), 2013 IEEE
+  Symposium on. IEEE; 2013. p. 60--67.
+
+\bibitem{hunter2007matplotlib}
+Hunter JD.
+\newblock Matplotlib: A 2D graphics environment.
+\newblock Computing In Science \& Engineering. 2007;9(3):90--95.
+
+\bibitem{mckinney2010data}
+McKinney W, et~al.
+\newblock Data structures for statistical computing in python.
+\newblock In: Proceedings of the 9th Python in Science Conference. vol. 445.
+  van der Voort S, Millman J; 2010. p. 51--56.
+
+\bibitem{walt2011numpy}
+Walt Svd, Colbert SC, Varoquaux G.
+\newblock The NumPy array: a structure for efficient numerical computation.
+\newblock Computing in Science \& Engineering. 2011;13(2):22--30.
+
+\bibitem{Li2011}
+Li J, Hingston P, Member S, Kendall G.
+\newblock {Engineering Design of Strategies for Winning Iterated Prisoner ' s
+  Dilemma Competitions}. 2011;3(4):348--360.
+
+\bibitem{Tzafestas2000}
+Tzafestas E.
+\newblock {Toward adaptive cooperative behavior}.
+\newblock From Animals to animals: Proceedings of the 6th International
+  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}.
+  2000;2:334--340.
+
+\bibitem{Mittal2009}
+Mittal S, Deb K.
+\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
+  multiple conflicting objectives}.
+\newblock IEEE Transactions on Evolutionary Computation. 2009;13(3):554--565.
+\newblock doi:{10.1109/TEVC.2008.2009459}.
+
+\bibitem{Hilbe2013}
+Hilbe C, Nowak MA, Traulsen A.
+\newblock Adaptive dynamics of extortion and compliance.
+\newblock PloS one. 2013;8(11):e77886.
+
+\bibitem{Nachbar1992}
+Nachbar JH.
+\newblock Evolution in the finitely repeated prisoner's dilemma.
+\newblock Journal of Economic Behavior \& Organization. 1992;19(3):307--326.
+
+\bibitem{Axelrod1995}
+Wu J, Axelrod R.
+\newblock How to cope with noise in the iterated prisoner's dilemma.
+\newblock Journal of Conflict resolution. 1995;39(1):183--189.
+
+\bibitem{Berg2015}
+van~den Berg P, Weissing FJ.
+\newblock The importance of mechanisms for the evolution of cooperation.
+\newblock In: Proc. R. Soc. B. vol. 282. The Royal Society; 2015. p. 20151382.
+
+\bibitem{Eckhart2015}
+Arnold E. CoopSim v0.9.9 beta 6; 2015.
+\newblock https://github.com/jecki/CoopSim/.
+
+\bibitem{Frean1994}
+Frean MR.
+\newblock The prisoner's dilemma without synchrony.
+\newblock Proceedings of the Royal Society of London B: Biological Sciences.
+  1994;257(1348):75--79.
+
+\bibitem{Ashlock2006b}
+Ashlock W, Ashlock D.
+\newblock Changes in prisoner’s dilemma strategies over evolutionary time
+  with different population sizes.
+\newblock In: Evolutionary Computation, 2006. CEC 2006. IEEE Congress on. IEEE;
+  2006. p. 297--304.
+
+\bibitem{Nowak1993}
+Nowak M, Sigmund K.
+\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
+  the Prisoner's Dilemma game.}
+\newblock Nature. 1993;364(6432):56--58.
+\newblock doi:{10.1038/364056a0}.
+
+\bibitem{Beaufils1997}
+Beaufils B, Delahaye JP, Mathieu P.
+\newblock Our meeting with gradual, a good strategy for the iterated
+  prisoner’s dilemma.
+\newblock In: Proceedings of the Fifth International Workshop on the Synthesis
+  and Simulation of Living Systems; 1997. p. 202--209.
+
+\bibitem{Banks1990}
+Banks JS, Sundaram RK.
+\newblock Repeated games, finite automata, and complexity.
+\newblock Games and Economic Behavior. 1990;2(2):97--117.
+
+\bibitem{Robson1990}
+Robson AJ.
+\newblock Efficiency in evolutionary games: Darwin, Nash and the secret
+  handshake.
+\newblock Journal of theoretical Biology. 1990;144(3):379--396.
+
+\bibitem{PD2017}
+Unknown. www.prisoners-dilemma.com; 2017.
+\newblock http://www.prisoners-dilemma.com/.
+
+\bibitem{Li2014}
+Li J, Kendall G, Member S.
+\newblock {The effect of memory size on the evolutionary stability of
+  strategies in iterated prisoner ' s dilemma}. 2014;X(X):1--8.
+
+\bibitem{Ashlock2008}
+Ashlock D, Kim EY.
+\newblock Fingerprinting: Visualization and automatic analysis of prisoner's
+  dilemma strategies.
+\newblock IEEE Transactions on Evolutionary Computation. 2008;12(5):647--659.
+
+\bibitem{Andre2013}
+Carvalho AL, Rocha HP, Amaral FT, Guimaraes FG.
+\newblock Iterated Prisoner’s Dilemma-An extended analysis. 2013;.
+
+\bibitem{Adami2013}
+Adami C, Hintze A.
+\newblock {Evolutionary instability of zero-determinant strategies demonstrates
+  that winning is not everything.}
+\newblock Nature communications. 2013;4(1):2193.
+\newblock doi:{10.1038/ncomms3193}.
+
+\bibitem{Kraines1989}
+Kraines D, Kraines V.
+\newblock Pavlov and the prisoner's dilemma.
+\newblock Theory and decision. 1989;26(1):47--79.
+
+\bibitem{Kuhn2017}
+Kuhn S.
+\newblock Prisoner's Dilemma.
+\newblock In: Zalta EN, editor. The Stanford Encyclopedia of Philosophy. spring
+  2017 ed. Metaphysics Research Lab, Stanford University; 2017.
 
@@
 \begin{enumerate}
-    \input{./assets/list_of_players.tex}
+\item $\phi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item $\pi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item $e$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item ALLCorALLD - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Adaptive - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
+\item Adaptive Pavlov 2006 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
+\item Adaptive Pavlov 2011 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
+\item Adaptive Tit For Tat: 0.5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Tzafestas2000}
+\item Aggravater - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Alternator - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1984, Mittal2009}
+\item Alternator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Anti Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Hilbe2013}
+\item AntiCycler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Appeaser - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Arrogant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Better and Better - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Bully - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Nachbar1992}
+\item Calculator - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Cautious QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item CollectiveStrategy (\textbf{CS}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2009}
+\item Contrite Tit For Tat (\textbf{CTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1995}
+\item Cooperator - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
+\item Cooperator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Cycler CCCCCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Cycler CCCD - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{axelrodproject}
+\item Cycler CCCDCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Cycler CCD - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
+\item Cycler DC - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Cycler DDC - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
+\item DBS: 0.75, 3, 4, 3, 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Au2006}
+\item Davis: 10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
+\item Defector - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
+\item Defector Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Desperate - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
+\item DoubleResurrection - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{Eckhart2015}
+\item Doubler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Dynamic Two Tits For Tat - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{axelrodproject}
+\item EasyGo - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011, Prison1998}
+\item Eatherley - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
+\item Eventual Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved ANN - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved ANN 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved ANN 5 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16. \cite{axelrodproject}
+\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16. \cite{axelrodproject}
+\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{axelrodproject}
+\item Evolved HMM 5 - \textit{Stochastic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item EvolvedLookerUp1\_1\_1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item EvolvedLookerUp2\_2\_2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Feld: 1.0, 0.5, 200 - \textit{Stochastic} - \textit{Memory depth}: 200. \cite{Axelrod1980}
+\item Firm But Fair - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Frean1994}
+\item Fool Me Forever - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Fool Me Once - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Forgetful Fool Me Once: 0.05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Forgetful Grudger - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Forgiver - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Forgiving Tit For Tat (\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2006b}
+\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{Ashlock2006b}
+\item GTFT: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1.
+\item GTFT: 0.3 - \textit{Stochastic} - \textit{Memory depth}: 1.
+\item GTFT: 0.33 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Gaudesi2016, Nowak1993}
+\item GTFT: 0.7 - \textit{Stochastic} - \textit{Memory depth}: 1.
+\item GTFT: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1.
+\item General Soft Grudger: n=1,d=4,c=2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Gradual - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Beaufils1997}
+\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C') - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Grofman - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
+\item Grudger - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980, Banks1990, Beaufils1997, Berg2015, Li2011}
+\item GrudgerAlternator - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Grumpy: Nice, 10, -10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Handshake - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Robson1990}
+\item Hard Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Mittal2009}
+\item Hard Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Hard Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
+\item Hard Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
+\item Hard Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Hard Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Hard Tit For 2 Tats (\textbf{HTf2T}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Stewart2012}
+\item Hard Tit For Tat (\textbf{HTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{PD2017}
+\item Hesitant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Hopeless - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
+\item Inverse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Inverse Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Axelrod1980, Stewart2012}
+\item Level Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Eckhart2015}
+\item Limited Retaliate 2: 0.08, 15 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Limited Retaliate 3: 0.05, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Limited Retaliate: 0.1, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item MEM2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2014}
+\item Math Constant Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Meta Hunter Aggressive: 7 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Meta Hunter: 6 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Meta Mixer: 173 players - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Naive Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Li2011}
+\item Negation - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{PD2017}
+\item Nice Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Nydegger - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1980}
+\item Omega TFT: 3, 8 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
+\item Once Bitten - \textit{Deterministic} - \textit{Memory depth}: 12. \cite{axelrodproject}
+\item Opposite Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler 1\_1\_1 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler 2\_2\_2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler 2\_2\_2 Noise 05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9. \cite{Ashlock2006b}
+\item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
+\item Prober 2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Prober 3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Prober 4 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2006}
+\item Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2014}
+\item Random Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Random: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 0.
+\item Random: 0.3 - \textit{Stochastic} - \textit{Memory depth}: 0.
+\item Random: 0.5 - \textit{Stochastic} - \textit{Memory depth}: 0. \cite{Axelrod1980, Tzafestas2000}
+\item Random: 0.7 - \textit{Stochastic} - \textit{Memory depth}: 0.
+\item Random: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 0.
+\item Remorseful Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{Li2011}
+\item Resurrection - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{Eckhart2015}
+\item Retaliate 2: 0.08 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Retaliate 3: 0.05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Retaliate: 0.1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Revised Downing: True - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
+\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2008}
+\item Risky QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item SelfSteem - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
+\item ShortMem - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{Andre2013}
+\item Shubik - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
+\item Slow Tit For Two Tats - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{axelrodproject}
+\item Slow Tit For Two Tats 2 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Prison1998}
+\item Sneaky Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Soft Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1984, Mittal2009}
+\item Soft Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Soft Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
+\item Soft Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
+\item Soft Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Soft Grudger - \textit{Deterministic} - \textit{Memory depth}: 6. \cite{Li2011}
+\item Soft Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Prison1998}
+\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2015}
+\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{Ashlock2015}
+\item Spiteful Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Stochastic Cooperator - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Adami2013}
+\item Stochastic WSLS: 0.05 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Suspicious Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Beaufils1997, Hilbe2013}
+\item TF1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item TF2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item TF3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Tester - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
+\item ThueMorse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item ThueMorseInverse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2008}
+\item Tit For 2 Tats (\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
+\item Tit For Tat (\textbf{TfT}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980}
+\item Tricky Cooperator - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Tricky Defector - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Tullock: 11 - \textit{Stochastic} - \textit{Memory depth}: 11. \cite{Axelrod1980}
+\item Two Tits For Tat (\textbf{2TfT}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
+\item VeryBad - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
+\item Willing - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
+\item Win-Shift Lose-Stay: D (\textbf{WShLSt}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Li2011}
+\item Win-Stay Lose-Shift: C (\textbf{WSLS}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Kraines1989, Nowak1993, Stewart2012}
+\item Winner12 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
+\item Winner21 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
+\item Worse and Worse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Worse and Worse 2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Worse and Worse 3 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item ZD-Extort-2 v2: 0.125, 0.5, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
+\item ZD-Extort-2: 0.1111111111111111, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
+\item ZD-Extort-4: 0.23529411764705882, 0.25, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item ZD-GEN-2: 0.125, 0.5, 3 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
+\item ZD-GTFT-2: 0.25, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
+\item ZD-SET-2: 0.25, 0.0, 2 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
 \end{enumerate}

### 2017-10-02 plos/response_to_reviewers.tex
Response to first review and some of second:
- Improve graphics;
- Fix some references;
- Include discussion of PD;
- Include discussion point about the stage game.

\documentclass[a4]{article}

\usepackage{hyperref}

\begin{document}

\section{Comments from editor}

\begin{quote}
	1. Please ensure that your manuscript meets PLOS ONE's style requirements,
	including those for file naming. The PLOS ONE style templates can be found at
	\url{http://www.journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf}
	and
	\url{http://www.journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf}
\end{quote}

We would be happy to change the style but could we be given a bit more guidance
please, the current submission (and revision) has been prepared using the LaTeX
template provided here: \url{http://journals.plos.org/plosone/s/latex}.

\begin{quote}
	2. Thank you for stating the following in the Financial Disclosure section:

	"The author(s) received no specific funding for this work".

	We note that one or more of the authors are employed by a commercial company: "Google Inc"
\end{quote}

% TODO Address this

\begin{quote}
3. Please amend your list of authors on the manuscript to ensure that each
author is linked to an affiliation. Authors’ affiliations should reflect the
institution where the work was done (if authors moved subsequently, you can
also list the new affiliation stating “current affiliation:….” as necessary).
\end{quote}

All authors affiliations have been included. Two of the authors, at the time of
the work being carried out where not affiliated with \textit{any} institution.
We have marked this as \textbf{Not Affiliated} however are open to any
suggestions for a different way of wording this.

\section{Comments from first referee}

\begin{quote}
    1. I did not see the cover letter attached.
\end{quote}

Apologies for this, we refer this comment to the editor, a cover letter was
provided.

\begin{quote}
    2. According to the PLOS One Manuscript Guideline you should not include
    figures in the main manuscript file (each figure must be prepared and
    submitted as an individual file). Also I advice to double check the
    references, for example, \#58, \#15, \#13, \#17 etc.
\end{quote}

We have followed the guidelines and example template provided here,
\url{http://journals.plos.org/plosone/s/latex}. All images were uploaded as
separate files and compiled by the PLOS One. If the editor/typesetter has any
further requirements we would be happy to oblige.

With regards to the references, we have checked them and updated \#15 which was
missing the conference. Thank you for bringing this to our attention.

\begin{quote}
    3. I found this article available in the Internet
    https://arxiv.org/pdf/1707.06307.pdf
\end{quote}

This is our preprint copy of the paper which is not against the copyright
specifications of PLOS. From
\url{http://journals.plos.org/plosone/s/criteria-for-publication}.

\begin{quote}
    PLOS does support authors who wish to share their
    work early through deposition of manuscripts with preprint servers. This
    does not impact consideration of the manuscript at any PLOS journal; we will
    consider manuscripts that have been deposited in preprint servers such as
    bioRxiv or arXiv, or published as a thesis. We will also consider work that
    has been presented at conferences.
\end{quote}

\begin{quote}
    4. In some figures (11, 12, etc) it is hard to see the names of the
    strategies.
\end{quote}

\begin{quote}
    5. The note for Fig 12 is seem not full and clear.
\end{quote}

All figures have been redrawn with bigger font where possible. To avoid poor
readability of names, these have been removed from various figures as the
ordering of the names can be assumed from the other figures.

\begin{quote}
    6. Lines 40-41: you write "we claim that this work contains the best
    performing strategies for the Iterated Prisoner's Dilemma". However, then
    you write "Finally, we note that as the library grows, the top performing
    strategies sometimes shuffle, and are not retrained automatically." (line
    328-329). So, the first statement is sound too strong...
\end{quote}

On reflection we agree and have removed the first sentence.

\begin{quote}
    7. Training methods should be shifted in the Materials and methods.
\end{quote}

This has been done.

\begin{quote}
    8. I did not see the explanation of the PD game and the iterated PD,
    however, it is the general tool in the publication.
\end{quote}

Thank you for pointing this out, an explanation has now been added.

\section{Comments from second referee}

\begin{quote}
Honestly this work less dedicates to the field of evolutionary game from
scientific point of view. One point obviously pointing-out is that their
conclusion of “reinforcement learning produces dominant strategies to win the
Axelrod’s IPD tournament” is no surprising at all. It is because anyone can
agree that the more elaborate learning system, e.g. Structural Neural Network
System with brushing-up mechanism for weights like they did, can be
implemented, there might be emerging some smart and robust strategies gaining
high scores.  But, consequently I think the MS may be acceptable on Plos One
because it devotedly follows the historically important work by Axelrod, in
which quite few people still have been interested. However, the current MS
seems suffering from several crucial problems that must be definitely revised.
\end{quote}

\begin{quote}
1) The way of their description seems so verbose. But, simultaneously, some
descriptions, e.g. explaining models, seem little vague. More clear structure
and plain description should be expected. The MS structure should be rebuilt.
\end{quote}

\begin{quote}
2) Most of visual materials to show their numerical results are obviously mal-functioned because of too small text descriptions, which do not work at all. More careful, friendly to the audience and intrigued expression should be considered.
\end{quote}

These have been addressed with larger font for the names.

\begin{quote}
3) This suggestion comes from science. The dilemma structure of PD they presumed is just one case; where P=0, R=3, S=0, T=5, although I can understand this may result from the previous tournament. A very likely question is what happens if they presume different dilemma strength even in the class of Prisoner’s Dilemma class. One good material to consider what-is-called dilemma strength is;
Wang et al.; Universal scaling for the dilemma strength in evolutionary games, Physics of Life Reviews 14, 1-30, 2015.
Tanimoto \& Sagara; Relationship between dilemma occurrence and the existence of a weakly dominant strategy in a two-player symmetric game, BioSystems 90(1), 105-114, 2007.
Those works suggest that PD games can be featured with combined two different dilemmas; Chicken-type dilemma, theoretically measured by Dg’ and SH-type dilemma evaluated by Dr’. I really love to know whether or not the authors statement or say conclusion by the current work can be robust if they presume different Dg’ and Dr’. At least they should mention this point in the discussion.
\end{quote}

Thank you for the helpful comment and suggested references, a comment about this
has been added to the discussion.

\end{document}

### 2017-10-02 main.tex
Response to first review and some of second:
- Improve graphics;
- Fix some references;
- Include discussion of PD;
- Include discussion point about the stage game.

@@
 evolve IPD strategies in various circumstances
-\cite{ashlock2006training, Ashlock2015, Ashlock2006,
+\cite{ashlock2006training, Ashlock2015, ashlock2006changes,
       ashlock2014shaped, Ashlock2014, barlow2015varying,

### 2017-10-02 plos/main.tex
Response to first review and some of second:
- Improve graphics;
- Fix some references;
- Include discussion of PD;
- Include discussion point about the stage game.

@@
 
-The Iterated Prisoner's Dilemma (IPD) is a common model in game theory,
+The Prisoner's Dilemma (PD) is a two player game
+used to model a variety of strategic interactions. Each player chooses
+between cooperation (C) or defection (D). The payoffs of
+the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
+\end{pmatrix}$, where $T > R > P > S$ and $2R > T + S$. The PD is a one
+round game, but is commonly studied in a manner where the prior outcomes
+matter. This repeated form is called the Iterated Prisoner's
+Dilemma (IPD).
+The IPD is a common model in game theory,
 frequently used  to understand the evolution of cooperative behaviour from complex
@@
 are correctly implemented, tested and documented.
-Moreover, as of the time of writing, we claim that this work contains the best
-performing strategies for the Iterated Prisoner's Dilemma.
 
@@
 
-% Results and Discussion can be combined.
+\subsection*{Training methods}\label{sec:methods}
+
+The trained strategies (denoted by a \(^{*}\) in
+Appendix~\ref{app:list_of_players}) were trained using reinforcement
+learning algorithms. The ideas of reinforcement learning can be attributed to
+the original work of \cite{turing1950computing} in which the notion that
+computers would learn by taking random actions but according to a distribution
+that picked actions with high rewards more often. The two particular algorithms
+used here:
+
+\begin{itemize}
+    \item Particle Swarm Algorithm: \cite{imran2013overview}.
+    \item Evolutionary algorithm: \cite{moriarty1999evolutionary}.
+\end{itemize}
+
+The Particle Swarm Algorithm is implemented using the pyswarm library:
+\url{https://pypi.python.org/pypi/pyswarm}. This algorithm was used only to
+train the Gambler archetype.
+
+All other strategies were trained using evolutionary algorithms. The
+evolutionary algorithms used standard techniques, varying strategies by
+mutation and crossover, and evaluating the performance against each opponent
+for many repetitions. The best performing strategies in each generation are
+persisted, variants created, and objective functions computed again.
+
+The default parameters for this procedure:
+
+\begin{itemize}
+	\item A population size of 40 individuals (kept constant across the
+        generations);
+	\item A mutation rate of 10\%;
+	\item 10 individuals kept from one generation to the next;
+    \item A total of 500 generations.
+\end{itemize}
+
+All implementations of these algorithms are archived at
+\cite{dojo}. This software is (similarly to the Axelrod
+library) available on github
+\url{https://github.com/Axelrod-Python/axelrod-dojo}. There are objective
+functions for:
+
+\begin{itemize}
+ \item total or mean payoff,
+ \item total or mean payoff difference (unused in this work),
+ \item total Moran process wins (fixation probability). This lead to the
+     strategies named TF1, TF2, TF3 listed in
+     Appendix~\ref{app:list_of_players}.
+\end{itemize}
+
+These can be used in noisy or standard environments. These objectives can be
+further modified to suit other purposes. New strategies could be trained with
+variations including spatial structure and probabilistically ending matches.
+
 \section*{Results}
@@
     \begin{pmatrix}
-        (3, 3) & (0, 5)\\
-        (5, 0) & (1, 1)
+        3 & 0\\
+        5 & 1
     \end{pmatrix}
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{standard_scores_boxplots.pdf}
-        \caption{\bf Standard Tournament: Mean score per turn (ranked by median
-        over
-        50000 tournaments).}
+        \includegraphics[width=\paperwidth]{standard_scores_boxplots.pdf}
+        \caption{\bf Standard Tournament: Mean score per turn 
+            (strategies ordered by median score over 50000 tournaments).}
         \label{fig:standard_boxplot}
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{standard_wins_boxplots.pdf}
+        \includegraphics[width=\paperwidth]{standard_wins_boxplots.pdf}
         \caption{\bf Standard Tournament: number of wins per tournament (ranked by
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{standard_ranks_boxplots.pdf}
+        \includegraphics[width=\paperwidth]{standard_ranks_boxplots.pdf}
         \caption{\bf Standard Tournament: rank in each tournament (ranked by
@@
         \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.pdf}
-        \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2 (over 10000
-        repetitions)}
+        \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2
+            (strategies ordered by median score over 10000 tournaments).}
         \label{fig:comparison_cooperation_heatmaps_standard_1}
@@
         \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_HMM_5_array.pdf}
-        \caption{\bf Cooperation rates for Evolved\_HMM\_5 (over 10000)
-        repetitions)}
+        \caption{\bf Cooperation rates for Evolved\_HMM\_5
+            (strategies ordered by median score over 10000 tournaments).}
         \label{fig:comparison_cooperation_heatmaps_standard_2}
@@
         \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_array.pdf}
-        \caption{\bf Cooperation rates for Evolved\_FSM\_16 (over 10000)
-        repetitions)}
+        \caption{\bf Cooperation rates for Evolved\_FSM\_16 
+            (strategies ordered by median score over 10000 tournaments).}
         \label{fig:comparison_cooperation_heatmaps_standard_3}
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{noisy_scores_boxplots.pdf}
-        \caption{\bf Noisy (5\%) Tournament: Mean score per turn (ranked by median
-        over
-        50000 tournaments).}
+        \includegraphics[width=\paperwidth]{noisy_scores_boxplots.pdf}
+        \caption{\bf Noisy (5\%) Tournament: Mean score per turn
+            (strategies ordered by median score over 50000 tournaments).}
+        \label{fig:standard_boxplot}
         \label{fig:noisy_score}
@@
     \centering
-    \includegraphics[width=.8\textwidth]{noisy_scores_heatmap.pdf}
+    \includegraphics[width=\textwidth]{noisy_scores_heatmap.pdf}
     \caption{\bf Noisy (5\%) Tournament: Mean score per turn of row players against
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{noisy_wins_boxplots.pdf}
-        \caption{\bf Noisy (5\%) Tournament: number of wins per tournament (ranked by
-        median over
-        50000 tournaments).}
+        \includegraphics[width=\paperwidth]{noisy_wins_boxplots.pdf}
+        \caption{\bf Noisy (5\%) Tournament: number of wins per tournament
+            (strategies ordered by median score over 50000 tournaments).}
         \label{fig:noisy_winplot}
@@
         \centering
-        \includegraphics[width=.8\paperwidth]{noisy_ranks_boxplots.pdf}
-        \caption{\bf Noisy (5\%) Tournament: rank in each tournament (ranked by
-        median over
-        50000 tournaments).}
+        \includegraphics[width=\paperwidth]{noisy_ranks_boxplots.pdf}
+        \caption{\bf Noisy (5\%) Tournament: rank in each tournament 
+            (strategies ordered by median score over 50000 tournaments).}
         \label{fig:noisy_ranks_boxplot}
@@
         \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.pdf}
-        \caption{\bf Cooperation rates for DBS (over 10000 standard tournaments).}
+        \caption{\bf Cooperation rates for DBS
+            (strategies ordered by median score over 10000 tournaments).}
         \label{fig:comparison_cooperation_heatmaps_noisy_1}
@@
         \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.pdf}
-        \caption{\bf Cooperation rates for Evolved\_ANN\_5\_Noise\_05 (over 10000 standard tournaments).}
+        \caption{\bf Cooperation rates for Evolved\_ANN\_5\_Noise\_05
+            (strategies ordered by median score over 10000 tournaments).}
         \label{fig:comparison_cooperation_heatmaps_noisy_2}
@@
         \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.pdf}
-        \caption{\bf Cooperation rates for Evolved\_FSM\_16\_Noise\_05 (over 10000 standard tournaments).}
+        \caption{\bf Cooperation rates for Evolved\_FSM\_16\_Noise\_05
+            (strategies ordered by median score over 10000 tournaments).}
         \label{fig:comparison_cooperation_heatmaps_noisy_3}
 \end{figure}
-
-\subsection*{Training methods}\label{sec:methods}
-
-The trained strategies (denoted by a \(^{*}\) in
-Appendix~\ref{app:list_of_players}) were trained using reinforcement
-learning algorithms. The ideas of reinforcement learning can be attributed to
-the original work of \cite{turing1950computing} in which the notion that
-computers would learn by taking random actions but according to a distribution
-that picked actions with high rewards more often. The two particular algorithms
-used here:
-
-\begin{itemize}
-    \item Particle Swarm Algorithm: \cite{imran2013overview}.
-    \item Evolutionary algorithm: \cite{moriarty1999evolutionary}.
-\end{itemize}
-
-The Particle Swarm Algorithm is implemented using the pyswarm library:
-\url{https://pypi.python.org/pypi/pyswarm}. This algorithm was used only to
-train the Gambler archetype.
-
-All other strategies were trained using evolutionary algorithms. The
-evolutionary algorithms used standard techniques, varying strategies by
-mutation and crossover, and evaluating the performance against each opponent
-for many repetitions. The best performing strategies in each generation are
-persisted, variants created, and objective functions computed again.
-
-The default parameters for this procedure:
-
-\begin{itemize}
-	\item A population size of 40 individuals (kept constant across the
-        generations);
-	\item A mutation rate of 10\%;
-	\item 10 individuals kept from one generation to the next;
-    \item A total of 500 generations.
-\end{itemize}
-
-All implementations of these algorithms are archived at
-\cite{dojo}. This software is (similarly to the Axelrod
-library) available on github
-\url{https://github.com/Axelrod-Python/axelrod-dojo}. There are objective
-functions for:
-
-\begin{itemize}
- \item total or mean payoff,
- \item total or mean payoff difference (unused in this work),
- \item total Moran process wins (fixation probability). This lead to the
-     strategies named TF1, TF2, TF3 listed in
-     Appendix~\ref{app:list_of_players}.
-\end{itemize}
-
-These can be used in noisy or standard environments. These objectives can be
-further modified to suit other purposes. New strategies could be trained with
-variations including spatial structure and probabilistically ending matches.
 
@@
 
-Finally, we note that as the library grows, the top performing strategies
+We note that as the library grows, the top performing strategies
 sometimes shuffle, and are not retrained automatically. Most of the strategies were
@@
 sufficient -- neural networks with fewer nodes and features and finite state
-machines with fewer states may suffice. See \cite{ashlock2013impact} for
+machines with fewer states may suffice. See~\cite{ashlock2013impact} for
 discussion of resource availability for IPD strategies.
+
+Finally, whilst we have considered the robustness of our claims and results with
+respect to noise it would also be of interest to train strategies for different
+versions of the stage game (also referred to as \textit{dilemma
+strength})~\cite{wang2015universal, tanimoto2007}. Our findings seems to indicate that obtaining
+strong strategies for other games through reinforcement learning would be
+possible.
 
@@
 
+\bibitem{Ashlock2006}
+Ashlock W, Ashlock D.
+\newblock Changes in prisoner’s dilemma strategies over evolutionary time
+  with different population sizes.
+\newblock In: Evolutionary Computation, 2006. CEC 2006. IEEE Congress on. IEEE;
+  2006. p. 297--304.
+
 \bibitem{Ashlock2015}
@@
   2015;7(1):53--65.
-
-\bibitem{Ashlock2006}
-Ashlock W, Ashlock D.
-\newblock {Changes in Prisoner ' s Dilemma Strategies Over Evolutionary Time
-  With Different Population Sizes}. 2006; p. 1001--1008.
 
@@
 
-\bibitem{Ashlock2006b}
-Ashlock W, Ashlock D.
-\newblock Changes in prisoner’s dilemma strategies over evolutionary time
-  with different population sizes.
-\newblock In: Evolutionary Computation, 2006. CEC 2006. IEEE Congress on. IEEE;
-  2006. p. 297--304.
-
 \bibitem{Nowak1993}
@@
   2017 ed. Metaphysics Research Lab, Stanford University; 2017.
+
+\bibitem{wang2015universal}
+Wang Z, Kokubo S, Jusup M, Tanimoto Jun.
+\newblock{Universal scaling for the dilemma strength in evolutionary games}
+\newblock{Physics of life reviews. 2015;(14):1--30.}
+
+\bibitem{tanimoto2007}
+Tanimoto J, Sagara H.
+\newblock {Relationship between dilemma occurrence and the existence of a weakly dominant strategy in a two-player symmetric game.}
+\newblock {BioSystems. 2007 Aug 31;90(1):105--14.}
 

### 2017-10-03 plos/response_to_reviewers.tex
Trim some of the text.
This is in response to the second reviewer whose comment was rather
unhelpful. We should make a point about this to the editor.

@@
 
+We have trimmed various sections of the text and restructured the text to move
+one of the sections to the Methods section. We feel the level of description of
+each model is correct, furthermore it is accompanied by a diagram clearly
+showing an example of each strategy. The results section is clearly written with
+very little prose surrounding what is a standard scientific form for presenting
+results. This is complemented by a verbose discussion section that is inline
+with common scientific texts. Furthermore we note that the other reviewer did
+not find a problem with our description. If the reviewer still feels that this
+is not sufficient we would welcome a more detailed description of the issue that
+persists.
+
 \begin{quote}

### 2017-10-03 plos/main.tex
Trim some of the text.
This is in response to the second reviewer whose comment was rather
unhelpful. We should make a point about this to the editor.

@@
 Dilemma (IPD).
-The IPD is a common model in game theory,
+The IPD is 
 frequently used  to understand the evolution of cooperative behaviour from complex
-dynamics \cite{Axelrod1984}.
+dynamics~\cite{Axelrod1984}.
 
@@
 \url{http://axelrod-tournament.readthedocs.io}. This work presents a detailed
-analysis of a tournament with 176 strategies.
+analysis of tournaments with 176 strategies.
 
@@
 with $n_1 = m_1 = m_2 = 2$ that is \emph{mostly deterministic}, with 52 of the 64
-probabilities being 0 or 1. At one time this strategy outperformed
-EvolvedLookerUp2\_2\_2.
+probabilities being 0 or 1.
 
@@
 a stochastic variant that outputs probabilities rather than exact moves could
-be easily created.
+be created.
 
@@
         \includegraphics[width=.5\textwidth]{FSM16.pdf}
-        \caption{\bf Evolved\_FSM\_16: trained to maximise score in a standard
+        \caption{\bf Evolved\_FSM\_16: trained to maximize score in a standard
         tournament}
@@
         \includegraphics[width=.5\textwidth]{FSM16noise.pdf}
-        \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
+        \caption{\bf Evolved\_FSM\_16\_Noise\_05: trained to maximize score in a
         noisy tournament}
@@
 consensus vote in the case of MetaMajority or the best individual performance
-in the case of MetaWinner. These strategies were among the best in the library
-before the inclusion of those trained by reinforcement learning. The library
-contains strategies containing teams of all the deterministic players, all the
-memory-one players, and some others.
+in the case of MetaWinner. These strategies were among the highest performing in 
+the library before the inclusion of those trained by reinforcement learning.
 
@@
 learning algorithms. The ideas of reinforcement learning can be attributed to
-the original work of \cite{turing1950computing} in which the notion that
+the original work of~\cite{turing1950computing} in which the notion that
 computers would learn by taking random actions but according to a distribution
@@
 stochasticity, the top three strategies almost always rank in the top three. For
-example, the worst that the Evolved Lookerup 2 2 2 ranks in any tournament
+example, the worst that the EvolvedLookerUp\_2\_2\_2 ranks in any tournament
 is 8th.
@@
 
-Noisy tournaments in which there is a 5\% chance that an action is
+Results from noisy tournaments in which there is a 5\% chance that an action is
 flipped are now described. As shown in Table~\ref{tbl:noisy_score} and
@@
 Fig~\ref{fig:comparison_cooperation_heatmaps_noisy_1}-~\ref{fig:comparison_cooperation_heatmaps_noisy_3} shows the rate of
-cooperation in each round for the top three strategies (in the absense of noise)
+cooperation in each round for the top three strategies (in the absence of noise)
 and just as for the top performing strategies in the standard tournament
@@
 strategies (which enforce a payoff difference rather than maximize total payoff).
+
+In opposition to historical tournament results and community folklore,
+our results show that complex strategies can be effective for the
+IPD\@. Of all the human-designed
+strategies in the library, only DBS consistently performs well, and it is
+substantially more complex than traditional tournament winners like TFT, OmegaTFT,
+and zero determinant strategies.
+
 The generic structure of the trained strategies did not appear to be
@@
 
-In opposition to historical tournament results and community folklore,
-our results show that complex strategies can be very effective for the
-IPD\@. Designing complex strategies for the prisoner's dilemma appears to be
-difficult for humans. Of all the human-designed
-strategies in the library, only DBS consistently performs well, and it is
-substantially more complex than traditional tournament winners like TFT, OmegaTFT,
-and zero determinant strategies. Furthermore, dealing with noise is difficult
-for most strategies. Two strategies designed specifically to account for noise,
+Two strategies designed specifically to account for noise,
 DBS and OmegaTFT, perform well and only DBS performs better than the trained
-strategies and \textbf{only} in some noisy contexts. Empirically we find that
+strategies and \textbf{only} in noisy contexts. Empirically we find that
 DBS (with its default parameters) does not win tournaments at 1\% noise.

### 2017-10-11 plos/main.tex
Make required changes.

@@
 % Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{lastpage,fancyhdr}
+\usepackage[draft]{graphicx}
 \usepackage{epstopdf}
@@
     \centering
-    \includegraphics[width=.7\textwidth]{lookerup.pdf}
+    \includegraphics[width=.7\textwidth]{lookerup.eps}
     \caption{\bf Diagrammatic representation of the Looker up Archetype.}
@@
     \centering
-    \includegraphics[width=.7\textwidth]{gambler.pdf}
+    \includegraphics[width=.7\textwidth]{gambler.eps}
     \caption{\bf Diagrammatic representation of the Gambler Archetype.}
@@
     \centering
-    \includegraphics[width=.9\textwidth]{ann.pdf}
+    \includegraphics[width=.9\textwidth]{ann.eps}
     \caption{\bf Diagrammatic representation of the ANN Archetype.}
@@
     \centering
-    \includegraphics[width=\textwidth]{fsm.pdf}
+    \includegraphics[width=\textwidth]{fsm.eps}
     \caption{\bf Diagrammatic representation of the Finite State Machine Archetype.}
@@
     \centering
-        \includegraphics[width=.5\textwidth]{FSM16.pdf}
+        \includegraphics[width=.5\textwidth]{FSM16.eps}
         \caption{\bf Evolved\_FSM\_16: trained to maximize score in a standard
@@
         \centering
-        \includegraphics[width=.5\textwidth]{FSM16noise.pdf}
+        \includegraphics[width=.5\textwidth]{FSM16noise.eps}
         \caption{\bf Evolved\_FSM\_16\_Noise\_05: trained to maximize score in a
@@
     \centering
-    \includegraphics[width=\textwidth]{hmm.pdf}
+    \includegraphics[width=\textwidth]{hmm.eps}
     \caption{\bf Diagrammatic representation of the Hidden Markov Model Archetype.}
@@
         \centering
-        \includegraphics[width=.5\textwidth]{standard_tft_scores.pdf}
+        \includegraphics[width=.5\textwidth]{standard_tft_scores.eps}
         \caption{\bf Scores for Tit for Tat over
@@
         \centering
-        \includegraphics[width=.5\textwidth]{standard_tft_ranks.pdf}
+        \includegraphics[width=.5\textwidth]{standard_tft_ranks.eps}
         \caption{\bf Ranks for Tit for Tat over
@@
         \centering
-        \includegraphics[width=.5\textwidth]{standard_tft_wins.pdf}
+        \includegraphics[width=.5\textwidth]{standard_tft_wins.eps}
         \caption{\bf Wins for Tit for Tat over
@@
         \centering
-        \includegraphics[width=\paperwidth]{standard_scores_boxplots.pdf}
+        \includegraphics[width=\paperwidth]{standard_scores_boxplots.eps}
         \caption{\bf Standard Tournament: Mean score per turn 
@@
     \centering
-    \includegraphics[width=\textwidth]{standard_scores_heatmap.pdf}
+    \includegraphics[width=\textwidth]{standard_scores_heatmap.eps}
     \caption{\bf Standard Tournament: Mean score per turn of row players against
@@
         \centering
-        \includegraphics[width=\paperwidth]{standard_wins_boxplots.pdf}
+        \includegraphics[width=\paperwidth]{standard_wins_boxplots.eps}
         \caption{\bf Standard Tournament: number of wins per tournament (ranked by
@@
         \centering
-        \includegraphics[width=\paperwidth]{standard_ranks_boxplots.pdf}
+        \includegraphics[width=\paperwidth]{standard_ranks_boxplots.eps}
         \caption{\bf Standard Tournament: rank in each tournament (ranked by
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.eps}
         \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_HMM_5_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_HMM_5_array.eps}
         \caption{\bf Cooperation rates for Evolved\_HMM\_5
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_array.eps}
         \caption{\bf Cooperation rates for Evolved\_FSM\_16 
@@
         \centering
-        \includegraphics[width=\paperwidth]{noisy_scores_boxplots.pdf}
+        \includegraphics[width=\paperwidth]{noisy_scores_boxplots.eps}
         \caption{\bf Noisy (5\%) Tournament: Mean score per turn
             (strategies ordered by median score over 50000 tournaments).}
-        \label{fig:standard_boxplot}
         \label{fig:noisy_score}
@@
     \centering
-    \includegraphics[width=\textwidth]{noisy_scores_heatmap.pdf}
+    \includegraphics[width=\textwidth]{noisy_scores_heatmap.eps}
     \caption{\bf Noisy (5\%) Tournament: Mean score per turn of row players against
@@
         \centering
-        \includegraphics[width=\paperwidth]{noisy_wins_boxplots.pdf}
+        \includegraphics[width=\paperwidth]{noisy_wins_boxplots.eps}
         \caption{\bf Noisy (5\%) Tournament: number of wins per tournament
@@
         \centering
-        \includegraphics[width=\paperwidth]{noisy_ranks_boxplots.pdf}
+        \includegraphics[width=\paperwidth]{noisy_ranks_boxplots.eps}
         \caption{\bf Noisy (5\%) Tournament: rank in each tournament 
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.eps}
         \caption{\bf Cooperation rates for DBS
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.eps}
         \caption{\bf Cooperation rates for Evolved\_ANN\_5\_Noise\_05
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.pdf}
+        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.eps}
         \caption{\bf Cooperation rates for Evolved\_FSM\_16\_Noise\_05

### 2017-11-03 plos/main.tex
Make minor adjustments requested by PLOS.

@@
 \usepackage{lastpage,fancyhdr}
-\usepackage[draft]{graphicx}
+\usepackage{graphicx}
 \usepackage{epstopdf}
@@
 Nikoleta E. Glynatsi\textsuperscript{2\ddag},
-Owen Campbell\textsuperscript{3\ddag},
+Owen Campbell\textsuperscript{5\ddag},
 \\
 \bigskip
-\textbf{1} Affiliation Google Inc., Mountain View, CA, USA
+\textbf{1} Google Inc., Mountain View, CA, USA
 \\
-\textbf{2} Affiliation Cardiff University, School of Mathematics, UK
+\textbf{2} Cardiff University, School of Mathematics, UK
 \\
-\textbf{3} Not affiliated
+\textbf{3} Python for biologist (\url{https://pythonforbiologists.com})
 \\
 \textbf{4} INRA, Université Côte d‘Azur, CNRS, ISA, France
+\\
+\textbf{5} Axelrod-Python Project
 \\
@@
     \centering
-    \includegraphics[width=.7\textwidth]{lookerup.eps}
+    %\includegraphics[width=.7\textwidth]{lookerup.eps}
     \caption{\bf Diagrammatic representation of the Looker up Archetype.}
@@
     \centering
-    \includegraphics[width=.7\textwidth]{gambler.eps}
+    %\includegraphics[width=.7\textwidth]{gambler.eps}
     \caption{\bf Diagrammatic representation of the Gambler Archetype.}
@@
     \centering
-    \includegraphics[width=.9\textwidth]{ann.eps}
+    %\includegraphics[width=.9\textwidth]{ann.eps}
     \caption{\bf Diagrammatic representation of the ANN Archetype.}
@@
     \centering
-    \includegraphics[width=\textwidth]{fsm.eps}
+    %\includegraphics[width=\textwidth]{fsm.eps}
     \caption{\bf Diagrammatic representation of the Finite State Machine Archetype.}
@@
     \centering
-        \includegraphics[width=.5\textwidth]{FSM16.eps}
+    %\includegraphics[width=.5\textwidth]{FSM16.eps}
         \caption{\bf Evolved\_FSM\_16: trained to maximize score in a standard
@@
         \centering
-        \includegraphics[width=.5\textwidth]{FSM16noise.eps}
+        %\includegraphics[width=.5\textwidth]{FSM16noise.eps}
         \caption{\bf Evolved\_FSM\_16\_Noise\_05: trained to maximize score in a
@@
     \centering
-    \includegraphics[width=\textwidth]{hmm.eps}
+    %\includegraphics[width=\textwidth]{hmm.eps}
     \caption{\bf Diagrammatic representation of the Hidden Markov Model Archetype.}
@@
         \centering
-        \includegraphics[width=.5\textwidth]{standard_tft_scores.eps}
+        %\includegraphics[width=.5\textwidth]{standard_tft_scores.eps}
         \caption{\bf Scores for Tit for Tat over
@@
         \centering
-        \includegraphics[width=.5\textwidth]{standard_tft_ranks.eps}
+        %\includegraphics[width=.5\textwidth]{standard_tft_ranks.eps}
         \caption{\bf Ranks for Tit for Tat over
@@
         \centering
-        \includegraphics[width=.5\textwidth]{standard_tft_wins.eps}
+        %\includegraphics[width=.5\textwidth]{standard_tft_wins.eps}
         \caption{\bf Wins for Tit for Tat over
@@
         \footnotesize
+        \caption{\bf Standard Tournament: Mean score per turn of top 15 strategies
+            (ranked by median over 50000 tournaments).
+        The leaderboard is dominated by the trained strategies (indicated by a
+        $^{*}$).}
 \begin{tabular}{lrrrrrrrrr}
@@
 \end{tabular}
-        \caption{\bf Standard Tournament: Mean score per turn of top 15 strategies
-            (ranked by median over 50000 tournaments).
-        The leaderboard is dominated by the trained strategies (indicated by a
-        $^{*}$).}
         \label{tbl:standard_score}
@@
 
-\begin{landscape}
-    \begin{figure}[!hbtp]
-        \centering
-        \includegraphics[width=\paperwidth]{standard_scores_boxplots.eps}
+\begin{figure}[!hbtp]
+    \centering
+    %\includegraphics[width=\paperwidth]{standard_scores_boxplots.eps}
     \caption{\bf Standard Tournament: Mean score per turn 
@@
 \end{figure}
-\end{landscape}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{standard_scores_heatmap.eps}
+    %\includegraphics[width=\textwidth]{standard_scores_heatmap.eps}
     \caption{\bf Standard Tournament: Mean score per turn of row players against
@@
         of top 15 strategies (ranked by median wins over
-        50000 tournaments).}
+        50000 tournaments). }
         \label{tbl:standard_wins_top_winners}
@@
 
-\begin{landscape}
-    \begin{figure}[!hbtp]
-        \centering
-        \includegraphics[width=\paperwidth]{standard_wins_boxplots.eps}
+\begin{figure}[!hbtp]
+    \centering
+    %\includegraphics[width=\paperwidth]{standard_wins_boxplots.eps}
     \caption{\bf Standard Tournament: number of wins per tournament (ranked by
@@
         of top 15 strategies (ranked by median score over
-        50000 tournaments).}
+        50000 tournaments)
+        ~$^{*}$ indicates that the strategy was trained.}
         \label{tbl:standard_wins}
@@
         of top 15 strategies (ranked by median over
-        50000 tournaments).}
+        50000 tournaments)
+        ~$^{*}$ indicates that the strategy was trained.}
     \footnotesize
@@
 
-\begin{landscape}
-    \begin{figure}[!hbtp]
-        \centering
-        \includegraphics[width=\paperwidth]{standard_ranks_boxplots.eps}
+\begin{figure}[!hbtp]
+    \centering
+    %\includegraphics[width=\paperwidth]{standard_ranks_boxplots.eps}
     \caption{\bf Standard Tournament: rank in each tournament (ranked by
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.eps}
+        %\includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.eps}
         \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_HMM_5_array.eps}
+        %\includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_HMM_5_array.eps}
         \caption{\bf Cooperation rates for Evolved\_HMM\_5
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_array.eps}
+        %\includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_array.eps}
         \caption{\bf Cooperation rates for Evolved\_FSM\_16 
@@
 
-\begin{landscape}
-    \begin{figure}[!hbtp]
-        \centering
-        \includegraphics[width=\paperwidth]{noisy_scores_boxplots.eps}
+\begin{figure}[!hbtp]
+    \centering
+    %\includegraphics[width=\paperwidth]{noisy_scores_boxplots.eps}
     \caption{\bf Noisy (5\%) Tournament: Mean score per turn
@@
     \centering
-    \includegraphics[width=\textwidth]{noisy_scores_heatmap.eps}
+    %\includegraphics[width=\textwidth]{noisy_scores_heatmap.eps}
     \caption{\bf Noisy (5\%) Tournament: Mean score per turn of row players against
@@
 
-\begin{landscape}
-    \begin{figure}[!hbtp]
-        \centering
-        \includegraphics[width=\paperwidth]{noisy_wins_boxplots.eps}
+\begin{figure}[!hbtp]
+    \centering
+    %\includegraphics[width=\paperwidth]{noisy_wins_boxplots.eps}
     \caption{\bf Noisy (5\%) Tournament: number of wins per tournament
@@
         of top 15 strategies (ranked by median score over
-        50000 tournaments).}
+        50000 tournaments)
+        ~$^{*}$ indicates that the strategy was trained.}
         \footnotesize
@@
         of top 15 strategies (ranked by median over
-        50000 tournaments).}
+        50000 tournaments)
+        ~$^{*}$ indicates that the strategy was trained.}
         \footnotesize
@@
 
-\begin{landscape}
-    \begin{figure}[!hbtp]
-        \centering
-        \includegraphics[width=\paperwidth]{noisy_ranks_boxplots.eps}
+\begin{figure}[!hbtp]
+    \centering
+    %\includegraphics[width=\paperwidth]{noisy_ranks_boxplots.eps}
     \caption{\bf Noisy (5\%) Tournament: rank in each tournament 
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.eps}
+        %\includegraphics[width=.7\textwidth]{cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.eps}
         \caption{\bf Cooperation rates for DBS
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.eps}
+        %\includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.eps}
         \caption{\bf Cooperation rates for Evolved\_ANN\_5\_Noise\_05
@@
         \centering
-        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.eps}
+        %\includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.eps}
         \caption{\bf Cooperation rates for Evolved\_FSM\_16\_Noise\_05
@@
 
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here. See http://journals.plos.org/plosone/s/latex for
-% step-by-step instructions.
-%
-
 \begin{thebibliography}{10}
@@
 
+\bibitem{turing1950computing}
+Turing AM.
+\newblock Computing machinery and intelligence.
+\newblock Mind. 1950;59(236):433--460.
+
+\bibitem{imran2013overview}
+Imran M, Hashim R, Khalid NEA.
+\newblock An overview of particle swarm optimization variants.
+\newblock Procedia Engineering. 2013;53:491--496.
+
+\bibitem{moriarty1999evolutionary}
+Moriarty DE, Schultz AC, Grefenstette JJ.
+\newblock Evolutionary algorithms for reinforcement learning.
+\newblock J Artif Intell Res(JAIR). 1999;11:241--276.
+
+\bibitem{dojo}
+Harper M, Knight V, Jones M, Koutsovoulos G. Axelrod-Python/axelrod-dojo:
+  V0.0.2; 2017.
+\newblock https://doi.org/10.5281/zenodo.832282.
+
 \bibitem{data}
@@
 
-\bibitem{turing1950computing}
-Turing AM.
-\newblock Computing machinery and intelligence.
-\newblock Mind. 1950;59(236):433--460.
-
-\bibitem{imran2013overview}
-Imran M, Hashim R, Khalid NEA.
-\newblock An overview of particle swarm optimization variants.
-\newblock Procedia Engineering. 2013;53:491--496.
-
-\bibitem{moriarty1999evolutionary}
-Moriarty DE, Schultz AC, Grefenstette JJ.
-\newblock Evolutionary algorithms for reinforcement learning.
-\newblock J Artif Intell Res(JAIR). 1999;11:241--276.
-
-\bibitem{dojo}
-Harper M, Knight V, Jones M, Koutsovoulos G. Axelrod-Python/axelrod-dojo:
-  V0.0.2; 2017.
-\newblock https://doi.org/10.5281/zenodo.832282.
-
 \bibitem{axelrodproject2.2}
@@
 
+\bibitem{wang2015universal}
+Wang Z, Kokubo S, Jusup M, Tanimoto Jun.
+\newblock{Universal scaling for the dilemma strength in evolutionary games}
+\newblock{Physics of life reviews. 2015;(14):1--30.}
+
+\bibitem{tanimoto2007}
+Tanimoto J, Sagara H.
+\newblock {Relationship between dilemma occurrence and the existence of a weakly dominant strategy in a two-player symmetric game.}
+\newblock {BioSystems. 2007 Aug 31;90(1):105--14.}
+
 \bibitem{hunter2007matplotlib}
@@
 
-\bibitem{wang2015universal}
-Wang Z, Kokubo S, Jusup M, Tanimoto Jun.
-\newblock{Universal scaling for the dilemma strength in evolutionary games}
-\newblock{Physics of life reviews. 2015;(14):1--30.}
-
-\bibitem{tanimoto2007}
-Tanimoto J, Sagara H.
-\newblock {Relationship between dilemma occurrence and the existence of a weakly dominant strategy in a two-player symmetric game.}
-\newblock {BioSystems. 2007 Aug 31;90(1):105--14.}
-
 \end{thebibliography}
@@
 
-\section{List of players}\label{app:list_of_players}
+\section{Appendix A: List of players}\label{app:list_of_players}
 

### 2017-11-13 plos/main.tex
Make minor final adjustments pointed out by PLOS.
Add affiliations that PLOS are happy with.

@@
 \\
-\textbf{2} Cardiff University, School of Mathematics, UK
+\textbf{2} Cardiff University, School of Mathematics, Cardiff, UK
 \\
-\textbf{3} Python for biologist (\url{https://pythonforbiologists.com})
+\textbf{3} Independent Researcher, Edinburgh, UK
 \\
-\textbf{4} INRA, Université Côte d‘Azur, CNRS, ISA, France
+\textbf{4} INRA, Universit\'{e} C\^{o}te d'Azur, CNRS, ISA, Nice, France
 \\
-\textbf{5} Axelrod-Python Project
+\textbf{5} Independent Researcher, Chester, UK
 \\
@@
 \item Forgiving Tit For Tat (\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2006b}
-\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{Ashlock2006b}
+\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2006}
+\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{Ashlock2006}
 \item GTFT: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1.
@@
 \item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9. \cite{Ashlock2006b}
+\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9. \cite{Ashlock2006}
 \item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
